---
title: "Merging CIMIS Data"
output: html_notebook
---



```{r}
rm(list=ls())

require(stringr)
require(zoo)
require(openair)


na.count<-function(x) sum(is.na(x))
na.mean<-function(x) ifelse(is.nan(mean(x,na.rm=T)),NA,mean(x,na.rm=T))

library(REddyProc)

library(car)
library(stringr)

library(tidyverse)
library(ggpubr)
library(rstatix)
library(broom)
library(psych)

library(lme4)
library(dplyr)
```


# Defining the data I/O directory #

```{r}
## change root.path as needed
root.path<-"C:\\Users\\tfens\\R_REPOS\\Flux_processing\\Concord_R_Code\\Concord_Post_Process\\"
#root.path<-"D:\\Housen\\Flux\\Data-exploring\\02_Concord\\"

combined.path<-paste0(root.path,"01_Data\\03_combined_data\\") ## this is where the combined data lives


path.in_CIMIS<-paste0(root.path,"01_Data\\04_CIMIS_Data\\")
 ver<-"cimis_data" 

# hc: Use this for storing combined file
path.out<-paste0(root.path,"02_output\\04_CIMIS_gapfill\\",sep="")

```



#defining specific files
```{r}
## use follows to specify the versions of the combined file
# file name of the combined_file
cdata.file_combo<-paste0("2023-10-13_master_eddy_met_concord_postfiltering.csv")



## use follows to specify the version of the
file.name_cimis<-paste("hourly_CIMIS.csv")



```


# Read in Combined fulloutput file
# parse variable names and define N/As

```{r}
## read in full output file
eddy_met<-read.csv(paste0(combined.path, cdata.file_combo,sep=""),
              
                header=T,
                na.strings="NA",
                stringsAsFactors=F)
colnames(eddy_met)<-colnames(read.csv(paste(combined.path,cdata.file_combo,sep=""),
                                  
                                   header=T,
                                   na.strings="NA"))



head(eddy_met)
tail(eddy_met)

```


#Read in CIMIS File
```{r}
## read in CIMIS file
cimis_data<-read.csv(paste0(path.in_CIMIS, file.name_cimis,sep=""),
                     header = T,
                     skip = 1)
              
                

colnames(cimis_data)<-colnames(read.csv(paste(path.in_CIMIS,file.name_cimis,sep=""),
                                  
                                   header=T,
                                   na.strings="NA"))



head(cimis_data)
tail(cimis_data)
```

# Parsing time stamp of cimis_data 
#first add zero to the front of the am time values so the strptime can read them
<!-- * then converting it into a POSIXlt vector* -->
<!-- * interpreting date and time into new timestamp column* -->
<!-- ** Then taking that time stamp column and turning each time into a unique number (time.id) so I can join based on that. As it can be really tricky to join/merge based on time stamps alone** -->

<!-- ** Finally ploting time.id to make sure my times translate linearily** -->


```{r}




cimis_data$Hour<-str_pad (as.character(cimis_data$Hour), 4, pad = "0") #adding zero to the front of the am numbers

cimis_data


cimis_data$TIMESTAMP<-strptime(paste(cimis_data$Date,cimis_data$Hour,sep=" "),
                          format="%m/%d/%Y %H%M ",
                          tz = "Etc/GMT-8")
head( cimis_data$TIMESTAMP)

plot(cimis_data$Sol.Rad)


cimis_data$time.id<-cimis_data$TIMESTAMP$year+1900+
  (cimis_data$TIMESTAMP$yday)/366+
  (cimis_data$TIMESTAMP$hour)/366/24+
  (cimis_data$TIMESTAMP$min)/366/24/60

cimis_data$time.id[1:50]
plot(cimis_data$TIMESTAMP,cimis_data$time.id)
which(duplicated(cimis_data$time.id))

head(cimis_data)




```


```{r}
plot(cimis_data$TIMESTAMP, cimis_data$Precip )


plot(cumsum(tapply(cimis_data$Precip,
          (cimis_data$DOY),
            function(x) sum(x,na.rm=T))),
     xaxt='n',
     xlab='Days since June 25,2019',
     ylab=expression(Cumulative~Precipitation~'('~mm~')'),
     main='',
     ylim = c(0,700),
     lty=1,
     col="red",
     lwd=2,
     type="l")
abline(v=365, col="blue")
axis(side=1,at=seq(0,1080,by=30))
```

#dropping time id column and creating a new time id so all the exponents line up for eddy_met data
```{r}
names(eddy_met)[names(eddy_met) == "time.id"] <- "old_time.id"

eddy_met$old_time.id <-NULL

colnames(eddy_met)
```



#For eddy_met master data switching the timestamp back to a timestamp from being a character vector. 
```{r}
head(eddy_met)

names(eddy_met)[names(eddy_met) == "TIMESTAMP"] <- "fake_timestamp"


colnames(eddy_met)

head(eddy_met$fake_timestamp)


eddy_met$TIMESTAMP<-strptime(paste(eddy_met$fake_timestamp),
                          format="%m/%d/%Y %H:%M",
                         tz = "Etc/GMT-8")

head(eddy_met$TIMESTAMP)
tail((eddy_met$TIMESTAMP))


head(eddy_met)

```

#creating a new time.id for eddy_met data
```{r}
eddy_met$time.id<-eddy_met$TIMESTAMP$year+1900+
  (eddy_met$TIMESTAMP$yday)/366+
  (eddy_met$TIMESTAMP$hour)/366/24+
  (eddy_met$TIMESTAMP$min)/366/24/60

eddy_met$time.id[1:50]
plot(eddy_met$TIMESTAMP,eddy_met$time.id)
which(duplicated(eddy_met$time.id))


```






#removing fake timestamp
```{r}
eddy_met$fake_timestamp <-NULL


cimis_data$fake_timestamp <- NULL
colnames(eddy_met)
colnames(cimis_data)

```


#merging cimis and combo data based on time.id
```{r}


cimis_eddy_met<- merge.data.frame(eddy_met,
                         cimis_data[,-which(colnames(cimis_data)=="TIMESTAMP")],
                         by = "time.id",
                         all = TRUE,
                         sort = TRUE)


head(cimis_eddy_met, 50)
tail(cimis_eddy_met, 50)

```

#updating DOY
```{r}
cimis_eddy_met$DOY<-cimis_eddy_met$TIMESTAMP$year+1900+
  (cimis_eddy_met$TIMESTAMP$yday)/366 

tail(cimis_eddy_met$DOY, 50)
```



#filling in missing primary temperature data (hmp) with secondary temperature data (sonic data)

#the intercept and slope need to be updated each time

```{r}
summary(lm(cimis_eddy_met$AirT_Avg~cimis_eddy_met$air_temperature_adj,na.action=na.omit))

#the intercept and slope need to be updated each time

 cimis_eddy_met$AirT_predict<- 1.3268135 + 0.9528243*cimis_eddy_met$air_temperature_adj
 
 cimis_eddy_met$AirT_Avg_GF<-cimis_eddy_met$AirT_Avg
 
 cimis_eddy_met$AirT_Avg_GF[is.na(cimis_eddy_met$AirT_Avg_GF)]<-cimis_eddy_met$AirT_predict[is.na(cimis_eddy_met$AirT_Avg_GF)]

 
 summary(cimis_eddy_met$AirT_predict)
 
 summary(cimis_eddy_met$AirT_Avg_GF)
 
 
 
 plot(cimis_eddy_met$AirT_Avg_GF)
plot(cimis_eddy_met$AirT_predict)
```


#filling in the remaining Temperature NA's with the values from the CIMIS data
```{r}

summary(cimis_data$Air.Temp)
summary(cimis_eddy_met$Air.Temp)

cimis_eddy_met$Air.Temp<-na.approx(cimis_eddy_met$Air.Temp,na.rm=F)
 summary(cimis_eddy_met$Air.Temp)


 cimis_eddy_met$AirT_Avg_GF[is.na(cimis_eddy_met$AirT_Avg_GF)]<-cimis_eddy_met$Air.Temp[is.na(cimis_eddy_met$AirT_Avg_GF)]
 
summary(cimis_eddy_met$AirT_Avg_GF)

plot(cimis_eddy_met$TIMESTAMP, cimis_eddy_met$AirT_Avg_GF)
 
```

#filling in our precipitation data with Cimis data
#Not kosher to gap fill our data with Cimis Data
```{r}
summary(cimis_data$Precip)

# summary(cimis_eddy_met$Precip)
# 
# cimis_eddy_met$Precip<-na.approx(cimis_eddy_met$Precip,na.rm=F)
#  summary(cimis_eddy_met$Precip)
# 
# 
#  cimis_eddy_met$Precip_mm_Tot[is.na(cimis_eddy_met$Precip_mm_Tot)]<-cimis_eddy_met$Precip[is.na(cimis_eddy_met$Precip_mm_Tot)]
#  
# summary(cimis_eddy_met$Precip_mm_Tot)



#####################################################
##ploting and comparing our gap filled to CIMIS t
# plot(cimis_eddy_met$TIMESTAMP, cimis_eddy_met$Precip_mm_Tot)
# 
# plot(cimis_data$Precip)
# 
# plot(cumsum(tapply(cimis_data$Precip,
#           (cimis_data$DOY),
#             function(x) sum(x,na.rm=T))),
#      xaxt='n',
#      xlab='Days since June 25,2019',
#      ylab=expression(Cumulative~Precipitation~'('~mm~')'),
#      main='',
#      ylim = c(0,250),
#      lty=1,
#      col="red",
#      lwd=2,
#      type="l")
# abline(v=365, col="blue")
# axis(side=1,at=seq(0,450,by=30))
# 
# plot(cumsum(tapply(cimis_eddy_met$Precip_mm_Tot,
#           (cimis_eddy_met$DOY),
#             function(x) sum(x,na.rm=T))),
#      xaxt='n',
#      xlab='Days since June 25,2019',
#      ylab=expression(Cumulative~Precipitation~'('~mm~')'),
#      main='',
#      ylim = c(0,500),
#      lty=1,
#      col="red",
#      lwd=2,
#      type="l")
# abline(v=365, col="blue")
# axis(side=1,at=seq(0,450,by=30))


```



```{r}
#hmp rh
plot(cimis_eddy_met$TIMESTAMP, cimis_eddy_met$RH_Avg )

#licor rh
plot(cimis_eddy_met$TIMESTAMP, cimis_eddy_met$RH )

#cimis rh
plot(cimis_eddy_met$TIMESTAMP, cimis_eddy_met$Rel.Hum )



plot(cimis_eddy_met$TIMESTAMP, cimis_eddy_met$PAR_in_mV_Avg)

plot(cimis_eddy_met$TIMESTAMP, cimis_eddy_met$PAR_in_uEm2_Avg )

plot(cimis_eddy_met$TIMESTAMP, cimis_eddy_met$Sol.Rad )


```

#filling in missing Rh avg (hmp) data with secondary sensor (licor) RH data
```{r}
summary(lm(cimis_eddy_met$RH_Avg~cimis_eddy_met$RH,na.action=na.omit))

#neeed to update the intercept and slope each time

 cimis_eddy_met$RH_predict<- 1.172391  + 0.915162*cimis_eddy_met$RH
 
 cimis_eddy_met$RH_Avg_GF<-cimis_eddy_met$RH_Avg
 
 cimis_eddy_met$RH_Avg_GF[is.na(cimis_eddy_met$RH_Avg_GF)]<-cimis_eddy_met$RH_predict[is.na(cimis_eddy_met$RH_Avg_GF)]

 
 summary(cimis_eddy_met$RH_predict)
 
 summary(cimis_eddy_met$RH_Avg_GF)
 
 
 
 plot(cimis_eddy_met$RH_Avg_GF)
plot(cimis_eddy_met$RH_predict)
```

#filling in remaining RH NA's with CIMIS data

```{r}
summary(cimis_data$Rel.Hum)
summary(cimis_eddy_met$Rel.Hum)

cimis_eddy_met$Rel.Hum<-na.approx(cimis_eddy_met$Rel.Hum,na.rm=F)
 summary(cimis_eddy_met$Rel.Hum)


 cimis_eddy_met$RH_Avg_GF[is.na(cimis_eddy_met$RH_Avg_GF)]<-cimis_eddy_met$Rel.Hum[is.na(cimis_eddy_met$RH_Avg_GF)]
 
summary(cimis_eddy_met$RH_Avg_GF)

plot(cimis_eddy_met$TIMESTAMP, cimis_eddy_met$RH_Avg_GF)
```


#Incoming solar radiation
```{r}
#Rg Calculated from tower's PAR sensors
plot(cimis_eddy_met$TIMESTAMP, cimis_eddy_met$Rg)

#CIMIS
plot(cimis_eddy_met$TIMESTAMP, cimis_eddy_met$Sol.Rad)

summary(cimis_data$Sol.Rad)

#filling in half hour data points for CIMIS data
cimis_eddy_met$Sol.Rad<-na.approx(cimis_eddy_met$Sol.Rad,na.rm=F)
 
summary(cimis_eddy_met$Sol.Rad)
 
 summary(cimis_eddy_met$Rg)

 
 #linear model looking at cimis data and our PAR data 
 summary(lm(cimis_eddy_met$Rg ~ cimis_eddy_met$Sol.Rad -1,na.action=na.omit))
 
 #applying this model to CIMIS data  (just applying coeeficient. no intercept)
 #need to update slope/coefficent everytime
cimis_eddy_met$Rg_predict<-cimis_eddy_met$Sol.Rad* 0.8747040
 
  summary(cimis_eddy_met$Rg_predict)
  plot(cimis_eddy_met$Rg_predict)
 
 cimis_eddy_met$Rg_Avg_GF<-cimis_eddy_met$Rg
 
 plot(cimis_eddy_met$Rg_Avg_GF)
 
 #filling in incoming radiation NA's with CIMIS incoming radiation linearly adjusted data
 cimis_eddy_met$Rg_Avg_GF[is.na(cimis_eddy_met$Rg_Avg_GF)]<-cimis_eddy_met$Rg_predict[is.na(cimis_eddy_met$Rg_Avg_GF)]

 
 summary(cimis_eddy_met$Rg_predict)
 
 summary(cimis_eddy_met$Rg_Avg_GF)
 
 
 
 plot(cimis_eddy_met$Rg_Avg_GF)

 
 

```

#combining thermocouple 4 ,9 and 14 data. to get mean soil temperature to 15 cm. gap filling with CIMIS data

```{r}

cimis_eddy_met$Soil_temp_tower_15cm <- apply(cimis_eddy_met[,c('TC_Avg.4.', 'TC_Avg.9.' , 'TC_Avg.14.')], 1, function(x) mean(x))

summary(cimis_eddy_met$Soil_temp_tower_15cm)

plot(cimis_eddy_met$Soil_temp_tower_15cm)
```
#gap filling for the 15cm soil temp with the CIMIS soil temperatures

```{r}
#Soil temp Calculated from tower's thermocouples sensors
plot(cimis_eddy_met$TIMESTAMP, cimis_eddy_met$Soil_temp_tower_15cm)

#CIMIS
plot(cimis_eddy_met$TIMESTAMP, cimis_eddy_met$Soil.Temp)

summary(cimis_eddy_met$Soil.Temp)
summary(cimis_eddy_met$Soil_temp_tower_15cm)

#filling in half hour data points for CIMIS data
cimis_eddy_met$Soil.Temp<-na.approx(cimis_eddy_met$Soil.Temp,na.rm=F)
 
summary(cimis_eddy_met$Soil.Temp)
 
 summary(cimis_eddy_met$Soil_temp_tower_15cm)

 
 #linear model looking at cimis data and our temp data 
 summary(lm(cimis_eddy_met$Soil_temp_tower_15cm ~ cimis_eddy_met$Soil.Temp,na.action=na.omit))
 
 #applying this model to CIMIS data  
cimis_eddy_met$Soil_temp_predict_15cm<-cimis_eddy_met$Soil.Temp* 1.38418  - 1.60962
 
  summary(cimis_eddy_met$Soil_temp_predict_15cm)
  plot(cimis_eddy_met$Soil_temp_predict_15cm)
  
  summary(cimis_eddy_met$Soil_temp_tower_15cm)
 
 cimis_eddy_met$Soil_temp_Avg_GF_15cm<-cimis_eddy_met$Soil_temp_tower_15cm
 
 plot(cimis_eddy_met$Soil_temp_Avg_GF_15cm)
 
 #filling icoming soil temp data with CIMIS templinearly adjusted data
 cimis_eddy_met$Soil_temp_Avg_GF_15cm[is.na(cimis_eddy_met$Soil_temp_Avg_GF_15cm)]<-cimis_eddy_met$Soil_temp_predict_15cm[is.na(cimis_eddy_met$Soil_temp_Avg_GF_15cm)]

 
 summary(cimis_eddy_met$Soil_temp_predict_15cm)
 
 summary(cimis_eddy_met$Soil_temp_Avg_GF_15cm)
 
 
 
 plot(cimis_eddy_met$Soil_temp_Avg_GF_15cm)
 
 plot(cimis_eddy_met$Soil_temp_tower_15cm, cimis_eddy_met$Soil.Temp)

```




```{r}
colnames(cimis_eddy_met)
```

#combining remaining treatment side thermocouples to get mean soil temp data for remaining depths. 

```{r}
#####0cm_treatment#######
cimis_eddy_met$Soil_temp_tower_0cm <- apply(cimis_eddy_met[,c('TC_Avg.1.', 'TC_Avg.6.' , 'TC_Avg.11.')], 1, function(x) mean(x))

summary(cimis_eddy_met$Soil_temp_tower_0cm)


plot(cimis_eddy_met$Soil_temp_tower_0cm)



############5cm_treatment####################
cimis_eddy_met$Soil_temp_tower_5cm <- apply(cimis_eddy_met[,c('TC_Avg.2.', 'TC_Avg.7.' , 'TC_Avg.12.')], 1, function(x) mean(x))

summary(cimis_eddy_met$Soil_temp_tower_5cm)

plot( cimis_eddy_met$TIMESTAMP, cimis_eddy_met$Soil_temp_tower_5cm)



#############10cm_treatment########################
cimis_eddy_met$Soil_temp_tower_10cm <- apply(cimis_eddy_met[,c('TC_Avg.3.', 'TC_Avg.8.' , 'TC_Avg.13.')], 1, function(x) mean(x))

summary(cimis_eddy_met$Soil_temp_tower_10cm)

plot(cimis_eddy_met$Soil_temp_tower_10cm)

###############30cm_treatment######################
cimis_eddy_met$Soil_temp_tower_30cm <- apply(cimis_eddy_met[,c('TC_Avg.5.', 'TC_Avg.10.' , 'TC_Avg.15.')], 1, function(x) mean(x))

summary(cimis_eddy_met$Soil_temp_tower_30cm)

plot(cimis_eddy_met$Soil_temp_tower_30cm)

```

#gap filling  the 10cm soil temps with the 15cm soil temps(combo of tower data and cimisdata)

```{r}
#Soil temp Calculated from tower's thermocouples sensors
plot(cimis_eddy_met$TIMESTAMP, cimis_eddy_met$Soil_temp_tower_10cm)

#CIMIS and tower
plot(cimis_eddy_met$TIMESTAMP, cimis_eddy_met$Soil_temp_Avg_GF_15cm)

summary(cimis_eddy_met$Soil_temp_Avg_GF_15cm)
summary(cimis_eddy_met$Soil_temp_tower_10cm)


 
 #linear model looking at 10 cm gap fill data and 10cm data
 summary(lm(cimis_eddy_met$Soil_temp_tower_10cm ~ cimis_eddy_met$Soil_temp_Avg_GF_15cm,na.action=na.omit))
 
 #applying this model to CIMIS data  
cimis_eddy_met$Soil_temp_predict_10cm<-cimis_eddy_met$Soil.Temp* 1.0611418  -1.0444637
 
  summary(cimis_eddy_met$Soil_temp_predict_10cm)
  plot(cimis_eddy_met$Soil_temp_predict_10cm)
  
  summary(cimis_eddy_met$Soil_temp_tower_10cm)
 
 cimis_eddy_met$Soil_temp_Avg_GF_10cm<-cimis_eddy_met$Soil_temp_tower_10cm
 
 plot(cimis_eddy_met$Soil_temp_Avg_GF_10cm)
 
 #filling icoming soil temp data with CIMIS templinearly adjusted data
 cimis_eddy_met$Soil_temp_Avg_GF_10cm[is.na(cimis_eddy_met$Soil_temp_Avg_GF_10cm)]<-cimis_eddy_met$Soil_temp_predict_10cm[is.na(cimis_eddy_met$Soil_temp_Avg_GF_10cm)]

 
 summary(cimis_eddy_met$Soil_temp_predict_10cm)
 
 summary(cimis_eddy_met$Soil_temp_Avg_GF_10cm)
 
 
 
 plot(cimis_eddy_met$Soil_temp_Avg_GF_10cm)
 
 plot(cimis_eddy_met$Soil_temp_tower_10cm, cimis_eddy_met$Soil_temp_Avg_GF_15cm)

```
#gap filling  the 5cm soil temps with the 15cm soil temps(combo of tower data and cimisdata)

```{r}
#Soil temp Calculated from tower's thermocouples sensors
plot(cimis_eddy_met$TIMESTAMP, cimis_eddy_met$Soil_temp_tower_5cm)

#CIMIS and tower
plot(cimis_eddy_met$TIMESTAMP, cimis_eddy_met$Soil_temp_Avg_GF_15cm)

summary(cimis_eddy_met$Soil_temp_Avg_GF_15cm)
summary(cimis_eddy_met$Soil_temp_tower_5cm)


 
 #linear model looking at 5cm gap fill data and 10cm data
 summary(lm(cimis_eddy_met$Soil_temp_tower_5cm ~ cimis_eddy_met$Soil_temp_Avg_GF_15cm,na.action=na.omit))
 
 #applying this model to CIMIS data  
cimis_eddy_met$Soil_temp_predict_5cm<-cimis_eddy_met$Soil.Temp* 1.120128  -2.080149 
 
  summary(cimis_eddy_met$Soil_temp_predict_5cm)
  plot(cimis_eddy_met$Soil_temp_predict_5cm)
  
  summary(cimis_eddy_met$Soil_temp_tower_5cm)
 
 cimis_eddy_met$Soil_temp_Avg_GF_5cm<-cimis_eddy_met$Soil_temp_tower_5cm
 
 plot(cimis_eddy_met$Soil_temp_Avg_GF_5cm)
 
 #filling icoming soil temp data with CIMIS templinearly adjusted data
 cimis_eddy_met$Soil_temp_Avg_GF_5cm[is.na(cimis_eddy_met$Soil_temp_Avg_GF_5cm)]<-cimis_eddy_met$Soil_temp_predict_5cm[is.na(cimis_eddy_met$Soil_temp_Avg_GF_5cm)]

 
 summary(cimis_eddy_met$Soil_temp_predict_5cm)
 
 summary(cimis_eddy_met$Soil_temp_Avg_GF_5cm)
 
 
 
 plot(cimis_eddy_met$Soil_temp_Avg_GF_5cm)
 
 plot(cimis_eddy_met$Soil_temp_tower_5cm, cimis_eddy_met$Soil_temp_Avg_GF_15cm)

```

#renaming control side thermocouples 
```{r}
####0_cm_control###########

cimis_eddy_met$TC_control_0cm<-cimis_eddy_met$TC_Avg.16._control

summary(cimis_eddy_met$TC_control_0cm)

plot(cimis_eddy_met$TC_control_0cm)

###########5cm_control#########################
cimis_eddy_met$TC_control_5cm<-cimis_eddy_met$TC_Avg.17._control

summary(cimis_eddy_met$TC_control_5cm)

plot(cimis_eddy_met$TC_control_5cm)

###########10cm_control#########################
cimis_eddy_met$TC_control_10cm<-cimis_eddy_met$TC_Avg.18._control

summary(cimis_eddy_met$TC_control_10cm)

plot(cimis_eddy_met$TC_control_10cm)

###########15cm_control#########################
cimis_eddy_met$TC_control_15cm<-cimis_eddy_met$TC_Avg.19._control

summary(cimis_eddy_met$TC_control_15cm)

plot(cimis_eddy_met$TC_control_15cm)


#############30cm_control##########################
cimis_eddy_met$TC_control_30cm<-cimis_eddy_met$TC_Avg.20._control

summary(cimis_eddy_met$TC_control_30cm)

plot(cimis_eddy_met$TC_control_30cm)

```


#linearily expanding control side 0 cm soil temp data from treatment side data
```{r}
#linear model looking at control 0cm data and treatment side temp data 
 summary(lm(cimis_eddy_met$TC_control_0cm ~ cimis_eddy_met$Soil_temp_tower_0cm,na.action=na.omit))
 
 #applying this model to treatment data  
cimis_eddy_met$Soil_temp_predict_0cm_control<-cimis_eddy_met$Soil_temp_tower_0cm* 1.122951  -2.930327  
 
#checking out the predicted control data via summary and plot
summary(cimis_eddy_met$TC_control_0cm)

plot(cimis_eddy_met$TC_control_0cm)

#checking out the predicted control data via summary and plot
summary(cimis_eddy_met$Soil_temp_predict_0cm_control)
  
plot(cimis_eddy_met$Soil_temp_predict_0cm_control)

  
 
 cimis_eddy_met$Soil_temp_control_GF_0cm<-cimis_eddy_met$TC_control_0cm
 
 plot(cimis_eddy_met$Soil_temp_control_GF_0cm)
 
 #filling control soil temp data with treatment linearily adjusted data
 cimis_eddy_met$Soil_temp_control_GF_0cm[is.na(cimis_eddy_met$Soil_temp_control_GF_0cm)]<-cimis_eddy_met$Soil_temp_predict_0cm_control[is.na(cimis_eddy_met$Soil_temp_control_GF_0cm)]

 
 summary(cimis_eddy_met$Soil_temp_predict_0cm_control)
 
 summary(cimis_eddy_met$Soil_temp_control_GF_0cm)
 
 
 
 plot(cimis_eddy_met$Soil_temp_control_GF_0cm)
 
 plot(cimis_eddy_met$Soil_temp_tower_0cm, cimis_eddy_met$TC_control_0cm)
```
#linearily expanding control side 5 cm soil temp data from treatment side data

```{r}
#linear model looking at control 5cm data and treatment side temp data 
 summary(lm(cimis_eddy_met$TC_control_5cm ~ cimis_eddy_met$Soil_temp_tower_5cm,na.action=na.omit))
 
 #applying this model to treatment data  
cimis_eddy_met$Soil_temp_predict_5cm_control<-cimis_eddy_met$Soil_temp_tower_5cm* 1.021544  -0.872515
 
#checking out the predicted control data via summary and plot
summary(cimis_eddy_met$TC_control_5cm)

plot(cimis_eddy_met$TC_control_5cm)

#checking out the predicted control data via summary and plot
summary(cimis_eddy_met$Soil_temp_predict_5cm_control)
  
plot(cimis_eddy_met$Soil_temp_predict_5cm_control)

  
 
 cimis_eddy_met$Soil_temp_control_GF_5cm<-cimis_eddy_met$TC_control_5cm
 
 plot(cimis_eddy_met$Soil_temp_control_GF_5cm)
 
 #filling control soil temp data with treatment linearily adjusted data
 cimis_eddy_met$Soil_temp_control_GF_5cm[is.na(cimis_eddy_met$Soil_temp_control_GF_5cm)]<-cimis_eddy_met$Soil_temp_predict_5cm_control[is.na(cimis_eddy_met$Soil_temp_control_GF_5cm)]

 
 summary(cimis_eddy_met$Soil_temp_predict_5cm_control)
 
 summary(cimis_eddy_met$Soil_temp_control_GF_5cm)
 
 
 
 plot(cimis_eddy_met$Soil_temp_control_GF_5cm)
 
 plot(cimis_eddy_met$Soil_temp_tower_5cm, cimis_eddy_met$TC_control_5cm)
```


#linearily expanding control side 10 cm soil temp data from treatment side data

```{r}
#linear model looking at control 10cm data and treatment side temp data 
 summary(lm(cimis_eddy_met$TC_control_10cm ~ cimis_eddy_met$Soil_temp_tower_10cm,na.action=na.omit))
 
 #applying this model to treatment data  
cimis_eddy_met$Soil_temp_predict_10cm_control<-cimis_eddy_met$Soil_temp_tower_10cm* 0.985878  - 0.236628
 
#checking out the predicted control data via summary and plot
summary(cimis_eddy_met$TC_control_10cm)

plot(cimis_eddy_met$TC_control_10cm)

#checking out the predicted control data via summary and plot
summary(cimis_eddy_met$Soil_temp_predict_10cm_control)
  
plot(cimis_eddy_met$Soil_temp_predict_10cm_control)

  
 
 cimis_eddy_met$Soil_temp_control_GF_10cm<-cimis_eddy_met$TC_control_10cm
 
 plot(cimis_eddy_met$Soil_temp_control_GF_10cm)
 
 #filling control soil temp data with treatment linearily adjusted data
 cimis_eddy_met$Soil_temp_control_GF_10cm[is.na(cimis_eddy_met$Soil_temp_control_GF_10cm)]<-cimis_eddy_met$Soil_temp_predict_10cm_control[is.na(cimis_eddy_met$Soil_temp_control_GF_10cm)]

 
 summary(cimis_eddy_met$Soil_temp_predict_10cm_control)
 
 summary(cimis_eddy_met$Soil_temp_control_GF_10cm)
 
 
 
 plot(cimis_eddy_met$Soil_temp_control_GF_10cm)
 
 plot(cimis_eddy_met$Soil_temp_tower_10cm, cimis_eddy_met$TC_control_10cm)
```

#linearily expanding control side 15 cm soil temp data from treatment side data
```{r}
#linear model looking at control 15cm data and treatment side temp data 
 summary(lm(cimis_eddy_met$TC_control_15cm ~ cimis_eddy_met$Soil_temp_Avg_GF_15cm,na.action=na.omit))
 
 #applying this model to treatment data  
cimis_eddy_met$Soil_temp_predict_15cm_control<-cimis_eddy_met$Soil_temp_Avg_GF_15cm* 0.9942428 - 0.3028919 
 
#checking out the predicted control data via summary and plot
summary(cimis_eddy_met$TC_control_15cm)

plot(cimis_eddy_met$TC_control_15cm)

#checking out the predicted control data via summary and plot
summary(cimis_eddy_met$Soil_temp_predict_15cm_control)
  
plot(cimis_eddy_met$Soil_temp_predict_15cm_control)

  
 
 cimis_eddy_met$Soil_temp_control_GF_15cm<-cimis_eddy_met$TC_control_15cm
 
 plot(cimis_eddy_met$Soil_temp_control_GF_15cm)
 
 #filling control soil temp data with treatment linearily adjusted data
 cimis_eddy_met$Soil_temp_control_GF_15cm[is.na(cimis_eddy_met$Soil_temp_control_GF_15cm)]<-cimis_eddy_met$Soil_temp_predict_15cm_control[is.na(cimis_eddy_met$Soil_temp_control_GF_15cm)]

 
 summary(cimis_eddy_met$Soil_temp_predict_15cm_control)
 
 summary(cimis_eddy_met$Soil_temp_control_GF_15cm)
 
 
 
 plot(cimis_eddy_met$Soil_temp_control_GF_15cm)
 
 plot(cimis_eddy_met$Soil_temp_Avg_GF_15cm, cimis_eddy_met$TC_control_15cm)
```


#linearily expanding control side 30 cm soil temp data from treatment side data
```{r}
#linear model looking at control 30_cm data and treatment side temp data 
 summary(lm(cimis_eddy_met$TC_control_30cm ~ cimis_eddy_met$Soil_temp_tower_30cm,na.action=na.omit))
 
 #applying this model to treatment data  
cimis_eddy_met$Soil_temp_predict_30cm_control<-cimis_eddy_met$Soil_temp_tower_30cm*  0.9916848 -0.2166233
 
#checking out the predicted control data via summary and plot
summary(cimis_eddy_met$TC_control_30cm)

plot(cimis_eddy_met$TC_control_30cm)

#checking out the predicted control data via summary and plot
summary(cimis_eddy_met$Soil_temp_predict_30cm_control)
  
plot(cimis_eddy_met$Soil_temp_predict_30cm_control)

  
 
 cimis_eddy_met$Soil_temp_control_GF_30cm<-cimis_eddy_met$TC_control_30cm
 
 plot(cimis_eddy_met$Soil_temp_control_GF_30cm)
 
 #filling control soil temp data with treatment linearily adjusted data
 cimis_eddy_met$Soil_temp_control_GF_30cm[is.na(cimis_eddy_met$Soil_temp_control_GF_30cm)]<-cimis_eddy_met$Soil_temp_predict_30cm_control[is.na(cimis_eddy_met$Soil_temp_control_GF_30cm)]

 
 summary(cimis_eddy_met$Soil_temp_predict_30cm_control)
 
 summary(cimis_eddy_met$Soil_temp_control_GF_30cm)
 
 
 
 plot(cimis_eddy_met$Soil_temp_control_GF_30cm)
 
 plot(cimis_eddy_met$Soil_temp_tower_30cm, cimis_eddy_met$TC_control_30cm)
```
#linearily expanding VWC 2
```{r}
#linear model looking at control VWC and treatment side VWC data 
 summary(lm(cimis_eddy_met$VWC_2_Avg_Control ~ cimis_eddy_met$VWC_Avg,na.action=na.omit))
 
 #applying this model to treatment data  
cimis_eddy_met$VWC_predict_control<-cimis_eddy_met$VWC_Avg*  1.0215697  +  0.0092021 
 
#checking out the predicted control data via summary and plot
summary(cimis_eddy_met$VWC_2_Avg_Control)

plot(cimis_eddy_met$VWC_2_Avg_Control)

#checking out the predicted control data via summary and plot
summary(cimis_eddy_met$VWC_predict_control)
  
plot(cimis_eddy_met$VWC_predict_control)

  
 
 cimis_eddy_met$VWC_control_GF<-cimis_eddy_met$VWC_2_Avg_Control
 
 plot(cimis_eddy_met$VWC_control_GF)
 
 #filling control soil temp data with treatment linearily adjusted data
 cimis_eddy_met$VWC_control_GF[is.na(cimis_eddy_met$VWC_control_GF)]<-cimis_eddy_met$VWC_predict_control[is.na(cimis_eddy_met$VWC_control_GF)]

 
 summary(cimis_eddy_met$VWC_predict_control)
 
 summary(cimis_eddy_met$VWC_control_GF)
 
 
 
 plot(cimis_eddy_met$VWC_control_GF)
 
 plot(cimis_eddy_met$VWC_Avg, cimis_eddy_met$VWC_2_Avg_Control)
```



#writing CSV of combined file gap filled file. 
```{r}
write.csv(cimis_eddy_met,
          paste(path.out,Sys.Date(),"_eddy_met_cimis_gap_filled.csv",sep=""),
          quote = T,
          row.names = F)


```




#Creating CSV of data needed for Reddy Proc gap filling

```{r}
data.reddy_proc<-data.frame(
                    TIMESTAMP = cimis_eddy_met$TIMESTAMP,
                    H= cimis_eddy_met$H,  ## H
                    LE=cimis_eddy_met$LE,    ## LE
                    h2o_flux = cimis_eddy_met$h2o_flux, #h20flux
                    NEE=cimis_eddy_met$co2_flux ,  ## c02 flux\
                    rH = cimis_eddy_met$RH_Avg_GF, #gapfilled relative humidity
                    Ustar = cimis_eddy_met$u.,   #ustar
                    Tsoil = cimis_eddy_met$Soil_temp_Avg_GF_15cm, #gapfilled soil temperature
                    Tair = cimis_eddy_met$AirT_Avg_GF, #gapfilled air temperature
                    Rg=cimis_eddy_met$Rg_Avg_GF  ## incoming solar radiation)
                     
)



head(data.reddy_proc, 100)


summary(data.reddy_proc)

write.csv(data.reddy_proc,
          paste(path.out,Sys.Date(),"_reddy_proc.csv",sep=""),
          quote = T,
          row.names = F)

# fWriteDataframeToFile(data.reddy_proc,
#                       paste(path.out,Sys.Date(),"_reddy_proc.txt",sep="")
#          )

```
