---
title: "Energy balance closure using heat storage term"
output:
  html_document:
    df_print: paged
---



```{r}
rm(list=ls())

require(stringr)
require(zoo)
require(openair)

na.count<-function(x) sum(is.na(x))
na.mean<-function(x) ifelse(is.nan(mean(x,na.rm=T)),NA,mean(x,na.rm=T))

library(REddyProc)

library(car)
library(stringr)

library(tidyverse)
library(ggpubr)
library(rstatix)
library(broom)
library(psych)

library(lme4)
library(dplyr)

library(lognorm)

SE <- function(x, na.rm=FALSE) {
  if (na.rm) x <- na.omit(x)
  sqrt(var(x)/length(x))
}
```

#Defining the data I/O directory
```{r}
## change root.path as needed
root.path<-"C:\\Users\\tfens\\R_REPOS\\Flux_processing\\Concord_R_Code\\Concord_Post_Process\\"
#root.path<-"D:\\Housen\\Flux\\Data-exploring\\02_Concord_Eden\\"


post_filter.path <-paste0(root.path, "01_data\\07_Gap_Filled_Data\\") #combined post filter file that has precip, etc.
ver<-"combined_data" 



out.path<-paste0(root.path, "02_output\\09_Energy_balance_closure\\")
```

#reading in a specific file

```{r}
## use follows to specify the versions of the combined file
# file name of the combined_file


cdata.file_post_filter <- paste("2023-10-17_eddy_met_cimis_gap_filled.csv")


 
```


#reading in the large post filter Cimis gap-filled data.
```{r}

post_filter <-
  read.csv(
    paste0(post_filter.path, cdata.file_post_filter, sep = ""),
    header = T,
    na.strings = "NA",
    stringsAsFactors = F
  )
colnames(post_filter) <-
  colnames(read.csv(
    paste(post_filter.path, cdata.file_post_filter, sep = ""),
    header = T,
    na.strings = "NA"
  ))

head(post_filter)

tail(post_filter)


```
#fixing time stamp for post filter
```{r}
post_filter$TIMESTAMP <- strptime(paste(post_filter$TIMESTAMP),
                                  format = "%m/%d/%Y %H:%M",
                                  tz = "Etc/GMT-8")

head(post_filter$TIMESTAMP)



```

```{r}
#seeing which rows are duplicated
which(duplicated(post_filter$TIMESTAMP))

#removing duplicated rows
post_filter <-
  post_filter[!duplicated(post_filter$TIMESTAMP),]


#checking that this worked
which(duplicated(post_filter$TIMESTAMP))
```

#Enerygy Balance for the two growing seasons


#creating a gravimeteric water content variable for calculating soil heat storage
```{r}

#gravimetric water content is volumetric/bulk density which is 1.35 grams per cm cubed or 1350 kg per meteris squared. 
#"if you use g/cm3 then VWC = GWC x BD" 
# Robert J. Lascano
# Professor - Soil Physics
# Texas Agricultural Experiment Station
# Texas A&M University - USDA - ARS  

plot(post_filter$TIMESTAMP, post_filter$VWC_Avg)

post_filter$GWC = post_filter$VWC_Avg/1.35 


plot(post_filter$TIMESTAMP, post_filter$GWC)

```

#Soils heat capacity constant (Cs)
#Cs= bulk density (Dry soil heat capacity + GWC*heat capacity of water)
#A value of 840 J kg-1 K-1 for the heat capacity of dry soil is a reasonable value for most mineral soils (Hanks and Ashcroft, 1980).
#heat capacity of water 4181 J kg-1 K-1

```{r}
post_filter$Cs = 1350*(840 + post_filter$GWC*4181 )

plot(post_filter$Cs)

```

#Calculating delta soil temperature at 5 cm
```{r}



# Calculate temperature change for 30-minute intervals (1800 secs)
#0.1 is the depth we at which we are calculating heat storage.  using soil temperature at 5 cm, since we are calculating the heat storage between 0-10 cm. Soil temperature fluctuates even more with a shallow depth. 

post_filter$heat_storage = ((post_filter$Cs*(c(NA, diff(post_filter$Soil_temp_Avg_GF_5cm, lag = 2), NA) / 2) * 0.1)) / 1800  




plot(post_filter$TIMESTAMP, post_filter$heat_storage)





```
#outliersfrom soil heat storage data
```{r}
boxplot(post_filter$heat_storage,
  ylab = "Heat storage",
  main = "Boxplot of soil heat storage"
)   


box_stats_heat_storage <-boxplot.stats(post_filter$heat_storage, coef = 3)$out



sort.int(box_stats_heat_storage) #where we get the below numbers
```


```{r}
#remove soil heat storage outliers
post_filter$heat_storage[ post_filter$heat_storage > 94.80] <-NA

post_filter$heat_storage[ post_filter$heat_storage <  -129.48 ] <-NA

summary(post_filter$heat_storage)

plot(post_filter$heat_storage)
```
#removing soil heat flux outliers
```{r}
#visualizing outliers
post_filter$soil_heat_flux_1_2 = (post_filter$Correct_shf_1+post_filter$Correct_shf_2)/2

boxplot(post_filter$soil_heat_flux_1_2,
  ylab = "soil heat flux",
  main = "Boxplot of soil heat flux"
)   

#identifying outliers
box_stats_soil_heat_flux <-boxplot.stats(post_filter$soil_heat_flux_1_2, coef = 3)$out



sort.int(box_stats_soil_heat_flux)#where we get the below numbers

#removing soil heat flux outliers

post_filter$soil_heat_flux_1_2[ post_filter$soil_heat_flux_1_2 > 91.57] <-NA

post_filter$soil_heat_flux_1_2[ post_filter$soil_heat_flux_1_2 <  -80.95 ] <-NA


summary(post_filter$soil_heat_flux_1_2)

plot(post_filter$soil_heat_flux_1_2)




```


**Energy Balance of non-gapfilled data. Slope of line is energy balance closure. Ideally it should be 1:1 Net radiation - (soil heat flux + soil heat storage)= to Latent heat +sensible heat. **


```{r}
#Plotting SH_f data to see gaps. 
plot(post_filter$TIMESTAMP, post_filter$Correct_shf_1)
plot(post_filter$TIMESTAMP, post_filter$Correct_shf_2)

#Creating E_ng variable NR- (SHF + Soil Heat storage)

post_filter$E_ng = (post_filter$Correct_NR- (post_filter$heat_storage + post_filter$soil_heat_flux_1_2))






#Plotting E_ng variable
summary(post_filter$E_ng )

plot(post_filter$E_ng)


#Creatin LE + H non-gapfilled variable
post_filter$E_le_and_H =(post_filter$LE+post_filter$H)

summary(post_filter$E_le_and_H  )
plot(post_filter$E_le_and_H )


#par(New=TRUE)
#plot(post_filter$E_ng, post_filter$E_le_and_H,
# xlab=expression(Net~Radiation~minus~soil~heat~flux~'('~W~m^{-2}~')'), 
#ylab= expression(Latent~and~Sensible~Heat~'('~W~m^{-2}~')'), 
# main='')


#Energy balance combining first two years. coefficent =   0.757593
Both_years<-lm(post_filter$E_le_and_H[post_filter$TIMESTAMP > as.POSIXct("2019-10-31") & post_filter$TIMESTAMP < as.POSIXct("2021-11-01")]   ~ post_filter$E_ng[post_filter$TIMESTAMP > as.POSIXct("2019-10-31") & post_filter$TIMESTAMP < as.POSIXct("2021-11-01")]-1)

summary(Both_years)

#model coefficient outputs and summary  for both years
write.csv(tidy(Both_years),
          paste(out.path,Sys.Date(),"coefs_both_year.csv",sep=""),
          quote = T,
          row.names = F)

write.csv(glance(Both_years),
          paste(out.path,Sys.Date(),"model_both_year.csv",sep=""),
          quote = T,
          row.names = F)

#Energy balance for first year coeefficent =  0.704206 
first_year<-lm(post_filter$E_le_and_H[post_filter$TIMESTAMP > as.POSIXct("2019-10-31") & post_filter$TIMESTAMP < as.POSIXct("2020-11-01")]   ~ post_filter$E_ng[post_filter$TIMESTAMP > as.POSIXct("2019-10-31") & post_filter$TIMESTAMP < as.POSIXct("2020-11-01")]-1)

summary(first_year)

#model coefficient outputs and summary  for first year
write.csv(tidy(first_year),
          paste(out.path,Sys.Date(),"coefs_first_year.csv",sep=""),
          quote = T,
          row.names = F)

write.csv(glance(first_year),
          paste(out.path,Sys.Date(),"model_first_year.csv",sep=""),
          quote = T,
          row.names = F)


#Energy balance second year coefficient 0.777506
 

second_year <- lm(post_filter$E_le_and_H[post_filter$TIMESTAMP > as.POSIXct("2020-10-31") & post_filter$TIMESTAMP < as.POSIXct("2021-11-01")]   ~ post_filter$E_ng[post_filter$TIMESTAMP > as.POSIXct("2020-10-31") & post_filter$TIMESTAMP < as.POSIXct("2021-11-01")]-1)


summary(second_year)

#model coefficient outputs and summary  for second year
write.csv(tidy(second_year),
          paste(out.path,Sys.Date(),"coefs_second_year.csv",sep=""),
          quote = T,
          row.names = F)

write.csv(glance(second_year),
          paste(out.path,Sys.Date(),"model_second_year.csv",sep=""),
          quote = T,
          row.names = F)

#Plotting energy balance closure

#Energy balance closure without a intercept
# -1 removes the intercept
energy_closure_no_int <- ggplot(data = post_filter[which (post_filter$TIMESTAMP > as.POSIXct("2019-10-31") & post_filter$TIMESTAMP < as.POSIXct("2021-11-01")),], aes(x= E_ng,
                                                   y=E_le_and_H))+
  geom_point()+
   geom_smooth(method = "lm", formula = y ~ x - 1, se = FALSE, color = "red")+
  theme_classic() +
  xlab(expression(Net~Radiation~minus~soil~heat~flux~and~soil~heat~storage~'('~W~m^{-2}~')'))+
  ylab(expression(Latent~and~Sensible~Heat~'('~W~m^{-2}~')'))


energy_closure_no_int

#Generating a png file of the energy balance closure without an intercept
png(units="in", width=10, height=10, res=350,paste0(out.path, Sys.Date(),"Energy_balance_closure_no_int.png"))
energy_closure_no_int
dev.off()


#Plotting the energy balance closure with the intercept. 
energy_closure_int<-  ggplot(data = post_filter[which (post_filter$TIMESTAMP > as.POSIXct("2019-10-31") & post_filter$TIMESTAMP < as.POSIXct("2021-11-01")),], aes(x= E_ng,
                                                   y=E_le_and_H))+
  geom_point()+
   geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "red")+
  theme_classic() +
  xlab(expression(Net~Radiation~minus~soil~heat~flux~and~soil~heat~storage~'('~W~m^{-2}~')'))+
  ylab(expression(Latent~and~Sensible~Heat~'('~W~m^{-2}~')'))


energy_closure_int

#Generating a png file of the energy balance closure with intercept
png(paste0(out.path,Sys.Date(),units="in", width=5, height=5, res=350, "Energy_balance_closure_with_intercept.png"))
energy_closure_int
dev.off()





```