---
title: "Workflow for half-hourly footprints"
author: "Housen Chu"
date: "4/22/2021"
output: github_document
---
This document demonstrates the workflow of half-hourly footprint calculations and footprint-weighted land cover contribution at the Concord flux tower -- [US-CGG](https://ameriflux.lbl.gov/sites/siteinfo/US-CGG). 

20210422 update:

* Constrain the contour to 80%, avoiding the cases that fails to find 90% contour within the footprint domain
* Ensure number of footprint grids > 600 * 600, avoiding problematic contours using coarse pixels


```{r}
rm(list=ls())
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, dev = 'svg')
#workDir <- "D:\\Housen\\Flux\\Data-exploring\\02_Concord_Eden\\flux_site_working\\"
workDir <- "C:\\Users\\tfens\\R_REPOS\\flux_site_working\\"

```

Set working directory as **workDir**, with associated sub-directories as follows: 

* data\ source files of 30 min flux/met files
  + pre-downloaded google maps surrounding selected sites
  + shape files for pre-defined areas
* R\ main workflow and required functions
  + footprint_workflow_v1.Rmd demonstrates the workflow of half-hourly footprint calculations
* output\ include following outputs for each site
  + 4 shape files for all half-hourly footprint contours (50%-80%)
  + 1 geo-tiff (stack) for all half-hourly footprint weights
  + 1 csv file containing basic information for all half-hourly footprints  

```{r include = T}
dataDir <- paste0(workDir, "data\\")
outDir <- paste0(workDir, "output\\")
rDir <- paste0(workDir, "R\\")
```

### Required packages
A list of required packages need to be installed. Note: EBImage is not a CRAN package, and needs to be installed separately. See the corresponding [link](https://bioconductor.org/packages/release/bioc/html/EBImage.html) for details.  

```{r include=T, message = F}
library(ggplot2)
library(ggmap)
library(rgdal)
library(geosphere)
library(zoo)
library(stringr)
library(sp)
library(raster)
library(SpatialEpi)
library(reshape2)
library(REddyProc)
#library(spatialfil)  # required by footprint function
library(EBImage)     # required by footprint function
# source("https://bioconductor.org/biocLite.R")
# biocLite("EBImage")
# if (!requireNamespace("BiocManager", quietly = TRUE))
#   install.packages("BiocManager")
# BiocManager::install("EBImage")

# install.packages("remotes")
# remotes::install_github("nickwing/spatialfil")
```

### Required functions
Assume these functions are stored at the \\R directory

```{r include=T, message = F}
source(file.path(rDir, "math_util.R"))
source(file.path(rDir, "calc_footprint_FFP_climatology_v2.R"))
source(file.path(rDir, "XY_to_latlon2.R"))
source(file.path(rDir, "polar2cart.R"))
source(file.path(rDir, "pbl_height.R"))
source(file.path(rDir, "find_equal_dist.R"))
source(file.path(rDir, "footprint_plot_v6.R"))
source(file.path(rDir, "crop_fpt_climt.R"))
source(file.path(rDir, "ext_radiation_v2.R"))
source(file.path(rDir, "get_extent.R"))
source(file.path(rDir, "data_filtering.R"))
```

### Workflow control parameters 
The following parameters are used to control the workflow, including input, output, data filtering. By default, a csv file with basic information of footprints for each half hour is written out. Additional outputs, like shape files for all half-hourly footprint contours, geo-tiff files for footprint weights, and footprint maps can be written out.  

```{r include=T, echo=T}
# Create a version sub directory
ver <- "20230602"     # for pulling site list
if (!dir.exists(paste(outDir, ver, sep = "")))
  dir.create(paste(outDir, ver, sep = ""))

output.shp <- T            # output shape file for footprint contours
output.tiff <- T           # output geo-tiff file for footprint weight maps
plot.fpt <- T              # output footprint map plots

#########################  Data filtering for footprint climatology runs
zl.u <- NA                 # outer bounds of ZL range  -zl.u< <zl.u
ustr.u <- 1.0              # upper bound of accepted USTAR (m/s)
ustr.l <- 0.1              # lower bound of accepted USTAR (m/s)
wd.u <- 360                # upper bound of accepted WD (degree)
wd.l <- 0                  # lower bound of accepted WD (degree)
lo.u <- NA                 # outer bounds of accepted MO_LENGTH (m), -lo.u< <lo.u, set NA is not used
```

### Site parameter
The following parameters are site-specific, including the file source, site lat/long, sensor & canopy height, footprint model parameters. Both preprocessed file and downloaded google map are located under \\data directory.

```{r include=T, echo=T}
file.ls <- "2022-11-07_eddy_met_cimis_gap_filled.csv"
map.ls <- "Concord_growing_season_basemap.RData" # edenlanding_basemap.RData

case <- "US-CGG"
latitude <- 37.937996
longitude <- -121.976105
utc.offset <- -8         # UTC offset (-8 Pacific standard time)
zm <- 3.67               # EC height(m)
z0 <- 0.05               # roughness length (m), ~0.1 hc
d <- 0                   # zero-plane displacement height (m), ~0.66 hc
footprint.domain <- 600  # target spatial domain for footprint calculation (m), distance from tower
footprint.res <- 2       # target spatial resolution for footprint calculation (m), pixel size
                         # make sure footprint.domain / footprint.res is an integer
                         # also make sure footprint.domain / footprint.res >= 300    
target.mon <- "2020_02"  # target month to run footprints ("YYYY_MM")

## don't modify below
src.res <- "HH"                          # time resolution, HH for half-hourly   
d.hr <- ifelse(src.res == "HH", 48, 24)
hr <- ifelse(d.hr == 48, 30, 60)
target.contour <- seq(50, 80, 10)        # target contour for footprint climatology
crop.contour <- 80                       # target contour for cropping footprint weights
pixel.n <- footprint.domain / footprint.res * 2

```

### Prepare map & shapefile
Get pre-downloaded Google map, load as basemap. Also, get shape files for treatment/control areas.

```{r include = T, echo = T, fig.width = 6, dev = "svg", collapse = TRUE}
## pre-downloaded Google map
load(file = paste0(dataDir, map.ls))

## work on shape files
# polygons
#update to make control area instead of wetland areas
shp.ls1 <- c(
  "compost_app_area_shape_file.shp"
 
)

shp.comb1 <- raster::shapefile(paste0(dataDir, shp.ls1[1]))
shp.comb1 <- sp::spChFIDs(shp.comb1, paste(substr(shp.ls1[1], 1, nchar(shp.ls1)[1] - 4)))



# for (i in 2:length(shp.ls1)) {
#   shp.tmp <- raster::shapefile(paste0(dataDir, shp.ls1[i]))
#   shp.tmp <- sp::spChFIDs(shp.tmp, paste(substr(shp.ls1[i], 1, nchar(shp.ls1)[i] - 4)))
#   shp.comb1 <- rbind(shp.comb1, shp.tmp, makeUniqueIDs = T)
# }

##
sitemap1 <- ggmap::ggmap(concord_tower) +
  geom_polygon(
    aes(x = long,
        y = lat,
        group = id,
        color = as.factor(id)
    ),
    fill = NA,
    size = 0.5,
    data = ggplot2::fortify(shp.comb1),
    na.rm = T
  )+
  geom_point(
    aes(x = longitude, y = latitude),
    fill = "pink",
    color = "red",
    size = 2,
    shape = 21
  ) +
  theme(
    legend.title = element_blank(),
    legend.box.spacing = unit(0.2, "line"),
    legend.direction = "vertical",
    legend.spacing.y = unit(0.4, "line"),
    legend.key.height = unit(0.8, "line"),
    legend.position = c(0.005, 0.800),
    legend.justification = c(0, 0),
    legend.key = element_rect(fill = NA, color = NA),
    legend.background = element_rect(fill = NA, color = NA)
  ) 

print(sitemap1)

```

### Read in Flux/Met data file
Down-select needed variables for footprint calculation. Assume the original file in EddyPro's full output format (see/check below for variable names/units). Combine with potential radiation to differentiate day/night. 

```{r include=T, echo=T}
# read in pre-processed/quality-controlled file
data.org <-
  read.csv(paste0(dataDir, file.ls),
           header = T,
           stringsAsFactors = F)

### prepare data
data.work <-
  data.org[, c(
    "TIMESTAMP",
    "L",                   # Obukhov length m  
    "u.",                  # friction velocity m s-1
    "H",                   # sensible heat flux W m-2
    "air_heat_capacity",   # J1 kg-1 K-1
    "air_density",         # kg m-3
    "sonic_temperature",   # deg C
    "wind_speed",          # m s-1
    "wind_dir",            # deg from N
    "v_var"                # variance of lateral wind velocity m2 s-2
  )]
colnames(data.work) <-
  c("TIMESTAMP",
    "MO_LENGTH",
    "USTAR",
    "H",
    "Cp",
    "rho",
    "Tv",
    "WS",
    "WD",
    "V_SIGMA")

## Unit conversion
data.work$V_SIGMA <- sqrt(data.work$V_SIGMA)
data.work$WT <- data.work$H / data.work$rho / data.work$Cp

head(data.work$TIMESTAMP)

data.work$TIMESTAMP <-
  strptime(data.work$TIMESTAMP, format = "%m/%d/%Y %H:%M", tz = "GMT")

head(data.work$TIMESTAMP)
tail(data.work$TIMESTAMP)
#### bring in potential incoming radiation, for day/night separation
data.work$TIMESTAMP_END <-
  as.character(((data.work$TIMESTAMP$year + 1900) * 10 ^ 8 +
                  (data.work$TIMESTAMP$mon + 1) * 10 ^ 6 +
                  (data.work$TIMESTAMP$mday) * 10 ^ 4 +
                  data.work$TIMESTAMP$hour * 10 ^ 2 +
                  data.work$TIMESTAMP$min
  ))

## calculate potential radiation based on site's location & time zone
SW_IN_POT <- ext_radiation_v2(
  latitude,
  longitude,
  year = c(data.work$TIMESTAMP$year[1]+1900,
           data.work$TIMESTAMP$year[nrow(data.work)]+1900),
  utc.offset = utc.offset,
  res = src.res
)

SW_IN_POT <-
  SW_IN_POT[c(
    which(SW_IN_POT$TIMESTAMP_END == data.work$TIMESTAMP_END[1]):
      which(SW_IN_POT$TIMESTAMP_END == data.work$TIMESTAMP_END[nrow(data.work)])
  ), ]

data.work <- merge.data.frame(data.work,
                              SW_IN_POT,
                              by = "TIMESTAMP_END",
                              all.y = T)
# use potential radiation to diferentiate day/night
data.work$DAYNIGHT <- ifelse(data.work$SW_IN_POT > 0, "DAY", "NIGHT")
data.work[1:3,]

```

### Work on planetary boundary layer height (PBL)
The planetary boundary layer height, required for Kljun 2015 footprint model, was calculated following Kljun et al. (2015), who used the Obukhov length, friction velocity, air temperature, and sensible heat flux in the calculations. As the calculation of PBL is time-dependent, fill the input variables before calculation.

```{r include=T, echo=T}
#### Work on filling the gaps in H, USTAR, Tv, and MO_LENGTH
data.work$DateTime <- data.work$TIMESTAMP
#+++ Initialize new sEddyProc processing class with more columns
EProc1 <- REddyProc::sEddyProc$new(case, data.work, "WT", DTS = d.hr)
EProc1$sFillInit("WT")
data.work$WT_F <- EProc1$sFillMDC(7)$VAR_f

EProc2 <- REddyProc::sEddyProc$new(case, data.work, "USTAR", DTS = d.hr)
EProc2$sFillInit("USTAR")
data.work$USTAR_F <- EProc2$sFillMDC(7)$VAR_f

EProc3 <- REddyProc::sEddyProc$new(case, data.work, "Tv", DTS = d.hr)
EProc3$sFillInit("Tv")
data.work$Tv_F <- EProc3$sFillMDC(7)$VAR_f

data.work$MO_LENGTH_F <-
  (-data.work$USTAR_F ^ 3 * (data.work$Tv_F + 273.15) / 0.4 / 9.81 / (data.work$WT_F))

data.work$zL <- (zm - d) / data.work$MO_LENGTH
data.work$zL_F <- (zm - d) / data.work$MO_LENGTH_F

###### Work on PBL
data.work$PBL <- pbl_height(
  latitude = latitude,
  TIMESTAMP = data.work$TIMESTAMP,
  zL = data.work$zL_F,                 # MO stability parameter (unitless)
  USTAR = data.work$USTAR_F,           # friction velocity (m s-1)
  MO_LENGTH = data.work$MO_LENGTH_F,   # Obukhov length (m)  
  WT = data.work$WT_F,                 # Covariance of vertical wind & temperature   
  Tv = data.work$Tv_F,                 # virtual/sonic temperature (deg C)
  DAYNIGHT = data.work$DAYNIGHT,       # day/night index
  neutral.cri = 0.05,
  hr = hr,
  plot = T,
  outDir = paste0(outDir, "\\", ver, "\\"),
  file.ext = paste(case, sep = "")
)
```

### Data filtering 
This applies further filtering specific for footprint calculation.

```{r include=T, echo=T}
# filtering data by defined thresholds
data.work <- data_filtering(data.work = data.work,
                            ustr.u = ustr.u,
                            ustr.l = ustr.l,
                            wd.u = wd.u,
                            wd.l = wd.l,
                            lo.u = lo.u,
                            zl.u = zl.u)

```

### Create a monthly index
The following workflow executes on selected target month.  

```{r include=T, echo=T}
###### create a index for group processing
data.work$cat1 <-
  paste0(data.work$TIMESTAMP$year + 1900,
         "_",
         stringr::str_pad(data.work$TIMESTAMP$mon + 1, 2, pad = "0"))

# get expected data record number, before filtering
cat.ls.all <- as.data.frame(table(data.work$cat1))

data.work <- data.work[!is.na(data.work$USTAR) &
                         !is.na(data.work$WS) &
                         !is.na(data.work$MO_LENGTH) &
                         !is.na(data.work$PBL) &
                         !is.na(data.work$WD) &
                         !is.na(data.work$V_SIGMA), ]

### create a grouping index, do footprint for each group
cat.ls.work <- as.data.frame(table(data.work$cat1))

## get expected & available data records for each group
cat.ls.all <- merge(
  cat.ls.all,
  cat.ls.work,
  by = "Var1",
  all = T,
  suffixes = c("_org", "_wrk")
)

cat.ls.all
```

### Work on footprint caculation
This section work through each half hour with all needed variables, calculate the footprint (weights & contours), and prepare the results in shape files (contours), geo-tiff (weights), and csv (valid time stamps & basic info) 

```{r include=T, echo=T}
data.work.tmp <- data.work[data.work$cat1 == target.mon, ]

wgt.shp.stack <- list()
fpt.shp.all50 <- list()
fpt.shp.all60 <- list()
fpt.shp.all70 <- list()
fpt.shp.all80 <- list()
fpt_KL15.cvt.all <- data.frame()
valid.fpt.ls <- data.frame()

# loop through each half hour
for (i33 in 1:nrow(data.work.tmp)) {
  
  #### main function for footprint calculation
  # See Kljun, N., P. Calanca, M.W. Rotach, H.P. Schmid, 2015:
  # The simple two-dimensional parameterisation for Flux Footprint Predictions FFP.
  # Geosci. Model Dev. 8, 3695-3713, doi:10.5194/gmd-8-3695-2015, for details.
  
  fpt_KL15 <-
    calc_footprint_FFP_climatology_v2(
      zm = zm - d,                                    # Measurement height above displacement height (i.e. z-d) [m]
      z0 = z0,                                        # Roughness length [m]
      umean = data.work.tmp$WS[i33],                  # wind speed at zm [ms-1]
      h = data.work.tmp$PBL[i33],                     # boundary layer height [m]
      ol = data.work.tmp$MO_LENGTH[i33],              # Obukhov length [m]
      sigmav = data.work.tmp$V_SIGMA[i33],            # standard deviation of lateral velocity fluctuations [ms-1]
      ustar = data.work.tmp$USTAR[i33],               # friction velocity [ms-1]
      wind_dir = data.work.tmp$WD[i33],               # wind direction in degrees (of 360)
      domain = c(-1, 1, -1, 1) * footprint.domain,    # Domain size as an array of [xmin xmax ymin ymax] [m]
      nx = pixel.n,                                   # integer scalars defining the number of grid elements in x and y
      r = target.contour,                             # Percentage of source area for which to provide contours
      smooth_data = 1,                                # Apply convolution filter to smooth footprint climatology if smooth_data=1
      rslayer = 1                                     # Calculate footprint even if zm within roughness sublayer: set rslayer = 1
    )
  
  ### used to clean contour (not sure why, but some sites have NA in the contour)
  ##   drop all points beyond the NA
  for (j1 in 1:length(target.contour)) {
    na.loc1 <- which(is.na(fpt_KL15$xr[[j1]]))
    na.loc2 <- which(is.na(fpt_KL15$yr[[j1]]))
    na.loc <- ifelse(length(na.loc1) > 0 & length(na.loc2) > 0,
                     min(c(na.loc1, na.loc2), na.rm = T),
                     0)
    if (na.loc > 0) {
      fpt_KL15$xr[[j1]] <- fpt_KL15$xr[[j1]][c(1:(na.loc - 1))]
      fpt_KL15$yr[[j1]] <- fpt_KL15$yr[[j1]][c(1:(na.loc - 1))]
    }
  }

  #################################################################################
  ## check if outermost contour enclose the tower as expected
  ## use to double check if footprint climatology calculation fail
  ignore.fpt.KL15 <- ifelse(fpt_KL15$flag_err == 1, T,
                            ifelse(length(fpt_KL15$xr[[length(target.contour)]]) <
                                     length(fpt_KL15$xr[[1]]), T, F)) |
    ifelse(length(fpt_KL15$x_2d) == 1,
           T,
           ifelse(
             sum(fpt_KL15$xr[[length(target.contour)]] > 0, na.rm = T) == 0 |
               sum(fpt_KL15$xr[[length(target.contour)]] < 0, na.rm = T) == 0 |
               sum(fpt_KL15$yr[[length(target.contour)]] > 0, na.rm = T) == 0 |
               sum(fpt_KL15$yr[[length(target.contour)]] < 0, na.rm = T) == 0,
             T,
             F
           ))

  ################################################################################
  ###### parse, store footprint information
  if (!ignore.fpt.KL15) {
    ## Store footprint contours and Convert XY coordinate to Lat/Long
    fpt_KL15.cvt <-
      rbind(
        data.frame(
          lon = XY_to_latlon2(
            lat.center = latitude,
            lon.center = longitude,
            x.ls = fpt_KL15$xr[[1]],
            y.ls = fpt_KL15$yr[[1]]
          )[, 1],
          lat = XY_to_latlon2(
            lat.center = latitude,
            lon.center = longitude,
            x.ls = fpt_KL15$xr[[1]],
            y.ls = fpt_KL15$yr[[1]]
          )[, 2],
          p = target.contour[1] / 100,
          model = 1
        ),
        data.frame(
          lon = XY_to_latlon2(
            lat.center = latitude,
            lon.center = longitude,
            x.ls = fpt_KL15$xr[[2]],
            y.ls = fpt_KL15$yr[[2]]
          )[, 1],
          lat = XY_to_latlon2(
            lat.center = latitude,
            lon.center = longitude,
            x.ls = fpt_KL15$xr[[2]],
            y.ls = fpt_KL15$yr[[2]]
          )[, 2],
          p = target.contour[2] / 100,
          model = 1
        ),
        data.frame(
          lon = XY_to_latlon2(
            lat.center = latitude,
            lon.center = longitude,
            x.ls = fpt_KL15$xr[[3]],
            y.ls = fpt_KL15$yr[[3]]
          )[, 1],
          lat = XY_to_latlon2(
            lat.center = latitude,
            lon.center = longitude,
            x.ls = fpt_KL15$xr[[3]],
            y.ls = fpt_KL15$yr[[3]]
          )[, 2],
          p = target.contour[3] / 100,
          model = 1
        ),
        data.frame(
          lon = XY_to_latlon2(
            lat.center = latitude,
            lon.center = longitude,
            x.ls = fpt_KL15$xr[[4]],
            y.ls = fpt_KL15$yr[[4]]
          )[, 1],
          lat = XY_to_latlon2(
            lat.center = latitude,
            lon.center = longitude,
            x.ls = fpt_KL15$xr[[4]],
            y.ls = fpt_KL15$yr[[4]]
          )[, 2],
          p = target.contour[4] / 100,
          model = 1
        )
      )

    fpt_KL15.cvt <- na.omit(fpt_KL15.cvt)
    fpt_KL15.cvt.all <- rbind.data.frame(fpt_KL15.cvt.all,
                                         fpt_KL15.cvt)

    ### compile shape files for all half-hourly footprint contours
    fpt.shp.all80[[i33]] <-
      sp::Polygons(list(sp::Polygon(coords = cbind(
        c(fpt_KL15.cvt$lon[fpt_KL15.cvt$p == 0.8]),
        c(fpt_KL15.cvt$lat[fpt_KL15.cvt$p ==
                             0.8])
      ))),
      ID = i33)
    fpt.shp.all70[[i33]] <-
      sp::Polygons(list(sp::Polygon(coords = cbind(
        c(fpt_KL15.cvt$lon[fpt_KL15.cvt$p == 0.7]),
        c(fpt_KL15.cvt$lat[fpt_KL15.cvt$p ==
                             0.7])
      ))),
      ID = i33)
    fpt.shp.all60[[i33]] <-
      sp::Polygons(list(sp::Polygon(coords = cbind(
        c(fpt_KL15.cvt$lon[fpt_KL15.cvt$p == 0.6]),
        c(fpt_KL15.cvt$lat[fpt_KL15.cvt$p ==
                             0.6])
      ))),
      ID = i33)
    fpt.shp.all50[[i33]] <-
      sp::Polygons(list(sp::Polygon(coords = cbind(
        c(fpt_KL15.cvt$lon[fpt_KL15.cvt$p == 0.5]),
        c(fpt_KL15.cvt$lat[fpt_KL15.cvt$p ==
                             0.5])
      ))),
      ID = i33)

    ################################################################
    #### work on footprint weight function output
    ## crop footprint weight to crop.contour, normalize to 100% within the crop.contour
    crop.weight <-
      crop_fpt_climt(
        x = seq(fpt_KL15$x_2d[1], fpt_KL15$x_2d[(pixel.n + 1) * (pixel.n + 1)], length.out = (pixel.n + 1)),
        y = seq(fpt_KL15$y_2d[1], fpt_KL15$y_2d[(pixel.n + 1) * (pixel.n + 1)], length.out = (pixel.n + 1)),
        z = fpt_KL15$fclim_2d,
        crop.bound <-
          cbind(fpt_KL15$xr[[which(target.contour == crop.contour)]],
                fpt_KL15$yr[[which(target.contour == crop.contour)]]),
        trim.beyond.bound = F
      )
    crop.weight$weight[is.na(crop.weight$weight)] <- 0

    fpt_weight <- data.frame(
      lon = XY_to_latlon2(
        lat.center = latitude,
        lon.center = longitude,
        x.ls = crop.weight$x,
        y.ls = crop.weight$y
      )[, 1],
      lat = XY_to_latlon2(
        lat.center = latitude,
        lon.center = longitude,
        x.ls = crop.weight$x,
        y.ls = crop.weight$y
      )[, 2],
      weight = crop.weight$weight,
      model = 1
    )

    wgt.shp <- raster::rasterFromXYZ(fpt_weight[, c(1, 2, 3)],
                                     crs = CRS("+proj=longlat +datum=WGS84"))

    wgt.shp.stack[[i33]] <- wgt.shp

    ## basic information for each valid footprint, also calculate the footprint-weighted land cover percentages
    valid.fpt.ls <- rbind.data.frame(
      valid.fpt.ls,
      cbind(
        data.work.tmp[i33,
                      c("TIMESTAMP", "DAYNIGHT", "cat1", "WD", "zL", "USTAR")],
        fetch_max = (
          fpt_KL15$fetch_max$X_max ^ 2 + fpt_KL15$fetch_max$Y_max ^ 2) ^ 0.5,
        fetch_crop_contour = get_extent(
          x.ls = fpt_KL15$xr[[length(target.contour)]],
          y.ls = fpt_KL15$yr[[length(target.contour)]],
          scal.coeff = 1)[1],
        ## handling footprint-weighted land cover percentages
        fpt_weight_control = NA,
        fpt_weight_treatment = raster::cellStats(raster::crop(wgt.shp,
                                                              shp.comb1[1,],
                                                              snap = "in"),
                                                 function(i, ...)
                                                   sum(i, na.rm = T))#,
        # fpt_weight_wetland1 = raster::cellStats(raster::crop(wgt.shp,
        #                                                      shp.comb1[2,],
        #                                                      snap = "in"),
        #                                         function(i, ...)
        #                                           sum(i, na.rm = T)),
        # fpt_weight_wetland2 = raster::cellStats(raster::crop(wgt.shp,
        #                                                      shp.comb1[3,],
        #                                                      snap = "in"),
        #                                         function(i, ...)
        #                                           sum(i, na.rm = T))
      )
    )
  }
}

## calculate control area as residual of all other land types
    valid.fpt.ls$fpt_weight_control <-
      1 - valid.fpt.ls$fpt_weight_treatment 

    valid.fpt.ls$fpt_weight_control <-
      ifelse(valid.fpt.ls$fpt_weight_control < 0,
             0,
             valid.fpt.ls$fpt_weight_control)

```

### Prepare outputs
Three types of files are output: 1) 5 shape files for all half-hourly footprint contours (50%-80%), 2) 1 geo-tiff (stack) for all half-hourly footprint weights, 3) a csv file containing basic information for all half-hourly footprints. 

```{r include=T, echo=T}
#### compile a raster stack with all 30-min footprint weight maps
if(output.tiff){
  
  wgt.shp.stack <-
    wgt.shp.stack[which(lapply(wgt.shp.stack, length) > 0)]
  wgt.shp.stack <- raster::stack(wgt.shp.stack)
  
  ## output footprint weight raster stacks
  raster::writeRaster(
    wgt.shp.stack,
    paste0(outDir, ver, "\\", case, "_", target.mon, "_fpt_weight.tif"),
    format = "GTiff",
    overwrite = TRUE
  )
  
}

#### compile shape files for all 30-min footprint contours, separated by percentages
fpt.shp.all80 <-
  fpt.shp.all80[which(lapply(fpt.shp.all80, length) > 0)]
fpt.shp.all80 <-
  sp::SpatialPolygons(fpt.shp.all80, proj4string = CRS("+proj=longlat +datum=WGS84"))
fpt.shp.all70 <-
  fpt.shp.all70[which(lapply(fpt.shp.all70, length) > 0)]
fpt.shp.all70 <-
  sp::SpatialPolygons(fpt.shp.all70, proj4string = CRS("+proj=longlat +datum=WGS84"))
fpt.shp.all60 <-
  fpt.shp.all60[which(lapply(fpt.shp.all60, length) > 0)]
fpt.shp.all60 <-
  sp::SpatialPolygons(fpt.shp.all60, proj4string = CRS("+proj=longlat +datum=WGS84"))
fpt.shp.all50 <-
  fpt.shp.all50[which(lapply(fpt.shp.all50, length) > 0)]
fpt.shp.all50 <-
  sp::SpatialPolygons(fpt.shp.all50, proj4string = CRS("+proj=longlat +datum=WGS84"))
#fpt.shp.all<-clgeo_Clean(fpt.shp.all)

## convert into spatial polygon data frame for output
df <- data.frame(ID = character(), stringsAsFactors = FALSE)
for (i in fpt.shp.all80@polygons) {
  df <- rbind(df, data.frame(ID = i@ID, stringsAsFactors = FALSE))
}
row.names(df) <- df$ID

fpt.shp.all80.df <- sp::SpatialPolygonsDataFrame(fpt.shp.all80, data = df)
fpt.shp.all70.df <- sp::SpatialPolygonsDataFrame(fpt.shp.all70, data = df)
fpt.shp.all60.df <- sp::SpatialPolygonsDataFrame(fpt.shp.all60, data = df)
fpt.shp.all50.df <- sp::SpatialPolygonsDataFrame(fpt.shp.all50, data = df)

# if(output.shp){
#   ### remove any pre-existing shape files before writing new ones
#   if (dir.exists(paste(outDir, ver, "\\", case, "_", target.mon, "_80per_contour", sep =
#                        ""))) {
#     unlink(paste0(outDir, ver, "\\", case, "_", target.mon, "_80per_contour"),
#            recursive = TRUE
#     )
#   }
#   if (dir.exists(paste(outDir, ver, "\\", case, "_", target.mon, "_70per_contour", sep =
#                        ""))) {
#     unlink(paste0(outDir, ver, "\\", case, "_", target.mon, "_70per_contour"),
#            recursive = TRUE
#     )
#   }
#   if (dir.exists(paste(outDir, ver, "\\", case, "_", target.mon, "_60per_contour", sep =
#                        ""))) {
#     unlink(paste0(outDir, ver, "\\", case, "_", target.mon, "_60per_contour"),
#            recursive = TRUE
#     )
#   }
#   if (dir.exists(paste(outDir, ver, "\\", case, "_", target.mon, "_50per_contour", sep =
#                        ""))) {
#     unlink(paste0(outDir, ver, "\\", case, "_", target.mon, "_50per_contour"),
#            recursive = TRUE
#     )
#   }
#   
#   ## prepare outputs shape files
#   rgdal::writeOGR(
#     fpt.shp.all80.df,
#     paste0(outDir, ver, "\\", case, "_", target.mon, "_80per_contour"),
#     layer = c("fpt_climatology"),
#     driver = "ESRI Shapefile"
#   )
#   ## prepare outputs shape files
#   rgdal::writeOGR(
#     fpt.shp.all70.df,
#     paste0(outDir, ver, "\\", case, "_", target.mon, "_70per_contour"),
#     layer = c("fpt_climatology"),
#     driver = "ESRI Shapefile"
#   )
#   ## prepare outputs shape files
#   rgdal::writeOGR(
#     fpt.shp.all60.df,
#     paste0(outDir, ver, "\\", case, "_", target.mon, "_60per_contour"),
#     layer = c("fpt_climatology"),
#     driver = "ESRI Shapefile"
#   )
#   ## prepare outputs shape files
#   rgdal::writeOGR(
#     fpt.shp.all50.df,
#     paste0(outDir, ver, "\\", case, "_", target.mon, "_50per_contour"),
#     layer = c("fpt_climatology"),
#     driver = "ESRI Shapefile"
#   )
#   
# }

## output a list of all valid footprints, with selected info
write.csv(
  valid.fpt.ls,
  paste0(outDir, ver, "\\", case, "_", target.mon, "_fpt_valid_list.csv"),
  row.names = F
)

## get a list of outputs
list.files(paste0(outDir, ver, "\\"))[grep(case, list.files(paste0(outDir, ver, "\\")))]

```

### Prepare footprint map plots
Two footprint maps are generated: 1) a map with all half-hourly footprints, 2) a map with 3 selected representative half-hourly footprints. Use select.example to define examples.

```{r include=TRUE, echo=T, fig.width = 7, warning = FALSE, dev = "svg"}

if (plot.fpt) {
  #### plot all footprint contours on a Google map
  suppressMessages((
    fpt.map1 <- footprint_plot_v6(
      fpt.shp.comb = fpt.shp.all80.df,                                  ## footprint contours shape files
      shp.comb1 = shp.comb1,                                            ## control/treatment areas shape files
      #shp.comb2 = shp.comb2,
      longitude = longitude,                                            ## tower location
      latitude = latitude,                                              ## tower location
      basemap = concord_tower,                                                ## background map  
      dist.target = 300,                                   ## target extent (m) for output map
      map.comment = paste0(case, " ", target.mon, " 80% footprint"),    ## short comment used in map title
      map.comment.short = paste0(case, "_", target.mon, "_footprint"),  ## short comment used in map file name
      path.out = paste0(outDir, "\\", ver, "\\")                        ## output directory  
    )
  ))
  
  #### plot selected 30-min footprints on a Google map
  ## create a index for selecting footprints
  select.example <-
    c(
      which(valid.fpt.ls$WD > 160 & valid.fpt.ls$WD < 209)[1],
      #which(valid.fpt.ls$WD > 260 & valid.fpt.ls$WD < 290)[2],
      which(valid.fpt.ls$WD > 350 | valid.fpt.ls$WD < 45)[2]
    )
  
  print(valid.fpt.ls$TIMESTAMP[select.example])
  print(valid.fpt.ls$WD[select.example])
  
  fpt.shp.all.df.example <- rbind(
    fpt.shp.all50.df[select.example, ],
    fpt.shp.all60.df[select.example, ],
    fpt.shp.all70.df[select.example, ],
    fpt.shp.all80.df[select.example, ]
  )
  
  suppressMessages((
    fpt.map2 <- footprint_plot_v6(
      fpt.shp.comb = fpt.shp.all.df.example,
      shp.comb1 = shp.comb1,
      longitude = longitude,
      latitude = latitude,
      basemap = concord_tower,
      dist.target = 300,
      map.comment = "Selected examples",
      map.comment.short = paste0(case, "_", target.mon, "_example_footprint"),
      path.out = paste0(outDir, "\\", ver, "\\")
    )
  ))
  
  plot(fpt.map1)
  plot(fpt.map2)
  
}
```

