---
title: "Pulling out the treatment side data post compost application"
output:
  html_document:
    df_print: paged
---



```{r echo=FALSE}
rm(list=ls())

require(stringr)
require(zoo)
require(openair)
library(bigleaf)


na.count<-function(x) sum(is.na(x))
na.mean<-function(x) ifelse(is.nan(mean(x,na.rm=T)),NA,mean(x,na.rm=T))

library(REddyProc)

library(car)
library(stringr)

library(tidyverse)
library(ggpubr)
library(rstatix)
library(broom)
library(psych)

library(lme4)
library(dplyr)

library(lognorm)

SE <- function(x, na.rm=FALSE) {
  if (na.rm) x <- na.omit(x)
  sqrt(var(x)/length(x))
}
```

#Defining the data I/O directory
```{r}
## change root.path as needed
root.path<-"C:\\Users\\Tommy\\flux\\Data-exploring\\02_Concord\\"
# root.path<-"D:\\Housen\\Flux\\Data-exploring\\02_Concord_Eden\\"

cimis_gap_fill.path<-paste0(root.path,"06_CIMIS_gap_fill\\") ## this is where the gapfilled MET data lives

foot_print.path <- paste0(root.path, "08_fp_lc\\")
ver_2<- "master_fp_lc"

out.path<-paste0(root.path, "12_treat_control_data\\")

GAM.path<-paste0(root.path,"14_GAM_ready_Data\\") # this is tower data for the GAM model lives
```

#reading in a specific file

```{r}
## use follows to specify the versions of the combined file
# file name of the combined_file
cdata.file_gap_fill<-paste0("2021-09-13_eddy_met_cimis_gap_filled.csv")

cdata.file_fp_lc <- paste("Master_fp_lc.csv")
 
```


# Read in gap filled fulloutput file
# parse variable names and define N/As

```{r}
## read in full output file of gap filled data
MET_gap_filled <-
  read.csv(
    paste0(cimis_gap_fill.path, cdata.file_gap_fill, sep = ""),
    header = T,
    na.strings = "NA",
    stringsAsFactors = F
  )

```

#read in footprint land cover file

```{r}
fp_lc_master <-
  read.csv(
    paste0(foot_print.path , cdata.file_fp_lc, sep = ""),
    header = T,
    na.strings = "NA",
    stringsAsFactors = F
  )

```

#adding back timestamp gap filled

```{r}
MET_gap_filled$TIMESTAMP <- strptime(paste(MET_gap_filled$TIMESTAMP),
                                 format = "%m/%d/%Y %H:%M",
                                 tz = "UTC")

```



#fixing time stamp for footprint landcover
```{r}
fp_lc_master$TIMESTAMP <- strptime(paste(fp_lc_master$TIMESTAMP),
                                   format = "%m/%d/%Y %H:%M",
                                   tz = "UTC")

```


#addding time.id gap filled
```{r}
MET_gap_filled$time.id <- MET_gap_filled$TIMESTAMP$year + 1900 +
  (MET_gap_filled$TIMESTAMP$yday) / 366 +
  (MET_gap_filled$TIMESTAMP$hour) / 366 / 24 +
  (MET_gap_filled$TIMESTAMP$min) / 366 / 24 / 60

plot(MET_gap_filled$TIMESTAMP, MET_gap_filled$time.id)



```



#adding timeid for footprint_landcover

```{r}
fp_lc_master$time.id <- fp_lc_master$TIMESTAMP$year + 1900 +
  (fp_lc_master$TIMESTAMP$yday) / 366 +
  (fp_lc_master$TIMESTAMP$hour) / 366 / 24 +
  (fp_lc_master$TIMESTAMP$min) / 366 / 24 / 60

plot(fp_lc_master$TIMESTAMP, fp_lc_master$time.id)


```


#Creating DOY
```{r}
MET_gap_filled$DOY <- MET_gap_filled$TIMESTAMP$year + 1900 +
  (MET_gap_filled$TIMESTAMP$yday) / 366

######################################
fp_lc_master$DOY <- fp_lc_master$TIMESTAMP$year + 1900 +
  (fp_lc_master$TIMESTAMP$yday) / 366


```

#merging gap filled and post filter data based on time id
```{r}
MET_Gap_LC <- merge.data.frame(
  MET_gap_filled,
  fp_lc_master[, -which(colnames(fp_lc_master) == "TIMESTAMP")],
  by = "time.id",
  all.x  = TRUE,
  sort = TRUE
)

```

#creating DOY for gap fill post filter

```{r}
MET_Gap_LC$DOY <- 
  MET_Gap_LC$TIMESTAMP$year + 1900 +
  (MET_Gap_LC$TIMESTAMP$yday) / 366

```
#creating vpd column
```{r}
MET_Gap_LC$VPD <-
  rH.to.VPD(
    MET_Gap_LC$RH_Avg_GF / 100,
    MET_Gap_LC$AirT_Avg_GF,
    Esat.formula = c("Sonntag_1990", "Alduchov_1996",
                     "Allen_1998"),
    constants = bigleaf.constants()
  )

```

#quick plot of VPD to double check
```{r}
plot(MET_Gap_LC$TIMESTAMP, MET_Gap_LC$VPD)
```


# Sorting into pre-compost and post compost application treatment and control areas
1. based on footprint weight if available
2. based on wind direction (excluding west & east wind sectors where the 
   boundary of control and treatment sides)

```{r}
# buffer sector for excluding winds coming from the boundaries of treatment & control
buffer.wd <- 45
east.bound <- 100
west.bound <- 255

#Sorting the treatment area into the pre and post compost application for analysis
MET_Gap_LC$treat_pre_post_cmpst_filt <-
  rep("exclude", nrow(MET_Gap_LC))

MET_Gap_LC$treat_pre_post_cmpst_filt[which(
  ((!is.na(MET_Gap_LC$fpt_weight_treatment) &
      MET_Gap_LC$fpt_weight_treatment >= 0.7) | 
     (!is.na(MET_Gap_LC$wind_dir) & 
        MET_Gap_LC$wind_dir >= east.bound + 0.5 * buffer.wd & 
        MET_Gap_LC$wind_dir <= west.bound - 0.5 * buffer.wd)) &
    MET_Gap_LC$TIMESTAMP > as.POSIXct("2020-10-16")
)] <- "treatment_post_compost"

#######################################################

MET_Gap_LC$treat_pre_post_cmpst_filt[which(
  ((!is.na(MET_Gap_LC$fpt_weight_treatment) &
      MET_Gap_LC$fpt_weight_treatment >= 0.7) | 
     (!is.na(MET_Gap_LC$wind_dir) & 
        MET_Gap_LC$wind_dir >= east.bound + 0.5 * buffer.wd & 
        MET_Gap_LC$wind_dir <= west.bound - 0.5 * buffer.wd)) &
    MET_Gap_LC$TIMESTAMP < as.POSIXct("2020-10-16")
)] <- "treatment_pre_compost"

######################################################

MET_Gap_LC$treat_pre_post_cmpst_filt[which(
  ((!is.na(MET_Gap_LC$fpt_weight_treatment) &
      MET_Gap_LC$fpt_weight_treatment < 0.3) | 
     (!is.na(MET_Gap_LC$wind_dir) & 
        (MET_Gap_LC$wind_dir <= east.bound - 0.5 * buffer.wd | 
           MET_Gap_LC$wind_dir >= west.bound + 0.5 * buffer.wd))) &
    MET_Gap_LC$TIMESTAMP > as.POSIXct("2020-10-16")
)] <- "control_post_compost"

####################################################

MET_Gap_LC$treat_pre_post_cmpst_filt[which(
  ((!is.na(MET_Gap_LC$fpt_weight_treatment) &
      MET_Gap_LC$fpt_weight_treatment < 0.3) | 
     (!is.na(MET_Gap_LC$wind_dir) & 
        (MET_Gap_LC$wind_dir <= east.bound - 0.5 * buffer.wd | 
           MET_Gap_LC$wind_dir >= west.bound + 0.5 * buffer.wd))) &
    MET_Gap_LC$TIMESTAMP < as.POSIXct("2020-10-16")
)] <- "control_pre_compost"


table(MET_Gap_LC$treat_pre_post_cmpst_filt)

```

#Sorting out treatment and control data data post compost application for readyproc

```{r}

data.GAM_treat_post_compost<-data.frame(
                    TIMESTAMP = MET_Gap_LC$TIMESTAMP,
                    H = MET_Gap_LC$H,  ## H
                    LE = MET_Gap_LC$LE,    ## LE
                    h2o_flux = MET_Gap_LC$h2o_flux, #h20flux
                    NEE = MET_Gap_LC$co2_flux ,  ## c02 flux\
                    rH = MET_Gap_LC$RH_Avg_GF, #gapfilled relative humidity
                    Ustar = MET_Gap_LC$u.,   #ustar
                    Tsoil_0cm = MET_Gap_LC$Soil_temp_control_GF_0cm, #gapfilled soil temperature
                    Tsoil_5cm = MET_Gap_LC$Soil_temp_control_GF_5cm,
                    Tsoil_10cm = MET_Gap_LC$Soil_temp_control_GF_10cm,
                    Tsoil_15cm = MET_Gap_LC$Soil_temp_control_GF_15cm,
                    Tsoil_30cm = MET_Gap_LC$Soil_temp_control_GF_30cm,
                    Tair = MET_Gap_LC$AirT_Avg_GF, #gapfilled air temperature
                    VWC = MET_Gap_LC$VWC_Avg,
                    Rg = MET_Gap_LC$Rg_Avg_GF,  ## incoming solar radiation
                    precip = MET_Gap_LC$Precip_mm_Tot,
                    VPD = MET_Gap_LC$VPD,
                    treatment = MET_Gap_LC$treat_pre_post_cmpst_filt
                     
)

data.GAM_treat_post_compost <-
  data.GAM_treat_post_compost[!is.na(data.GAM_treat_post_compost$TIMESTAMP), ]

write.csv(
  data.GAM_treat_post_compost,
  paste0(GAM.path, Sys.Date(), "_all_GAM_data.csv"),
  quote = T,
  row.names = F
)



```

