---
title: "Pulling out the treatment side data post compost application"
output:
  html_document:
    df_print: paged
---



```{r echo=FALSE}
rm(list=ls())

require(stringr)
require(zoo)
require(openair)
library(bigleaf)


na.count<-function(x) sum(is.na(x))
na.mean<-function(x) ifelse(is.nan(mean(x,na.rm=T)),NA,mean(x,na.rm=T))

library(REddyProc)

library(car)
library(stringr)

library(tidyverse)
library(ggpubr)
library(rstatix)
library(broom)
library(psych)

library(lme4)
library(dplyr)

library(lognorm)

SE <- function(x, na.rm=FALSE) {
  if (na.rm) x <- na.omit(x)
  sqrt(var(x)/length(x))
}
```

#Defining the data I/O directory
```{r}
## change root.path as needed
#root.path<-"C:\\Users\\Tommy\\flux\\Data-exploring\\02_Concord\\"
root.path<-"D:\\Housen\\Flux\\Data-exploring\\02_Concord_Eden\\"

cimis_gap_fill.path<-paste0(root.path,"06_CIMIS_gap_fill\\") ## this is where the gapfilled MET data lives

foot_print.path <- paste0(root.path, "08_fp_lc\\")
ver_2<- "master_fp_lc"

out.path<-paste0(root.path, "12_treat_control_data\\")
```

#reading in a specific file

```{r}
## use follows to specify the versions of the combined file
# file name of the combined_file
cdata.file_gap_fill<-paste0("2021-09-13_eddy_met_cimis_gap_filled.csv")

cdata.file_fp_lc <- paste("Master_fp_lc.csv")
 
```


# Read in gap filled fulloutput file
# parse variable names and define N/As

```{r}
## read in full output file of gap filled data
MET_gap_filled <-
  read.csv(
    paste0(cimis_gap_fill.path, cdata.file_gap_fill, sep = ""),
    header = T,
    na.strings = "NA",
    stringsAsFactors = F
  )

```

#read in footprint land cover file

```{r}
fp_lc_master <-
  read.csv(
    paste0(foot_print.path , cdata.file_fp_lc, sep = ""),
    header = T,
    na.strings = "NA",
    stringsAsFactors = F
  )

```

#adding back timestamp gap filled

```{r}
MET_gap_filled$TIMESTAMP <- strptime(paste(MET_gap_filled$TIMESTAMP),
                                 format = "%Y-%m-%d %H:%M:%S",
                                 tz = "UTC")

```



#fixing time stamp for footprint landcover
```{r}
fp_lc_master$TIMESTAMP <- strptime(paste(fp_lc_master$TIMESTAMP),
                                   format = "%m/%d/%Y %H:%M",
                                   tz = "UTC")

```


#addding time.id gap filled
```{r}
MET_gap_filled$time.id <- MET_gap_filled$TIMESTAMP$year + 1900 +
  (MET_gap_filled$TIMESTAMP$yday) / 366 +
  (MET_gap_filled$TIMESTAMP$hour) / 366 / 24 +
  (MET_gap_filled$TIMESTAMP$min) / 366 / 24 / 60

plot(MET_gap_filled$TIMESTAMP, MET_gap_filled$time.id)

```



#adding timeid for footprint_landcover

```{r}
fp_lc_master$time.id <- fp_lc_master$TIMESTAMP$year + 1900 +
  (fp_lc_master$TIMESTAMP$yday) / 366 +
  (fp_lc_master$TIMESTAMP$hour) / 366 / 24 +
  (fp_lc_master$TIMESTAMP$min) / 366 / 24 / 60

plot(fp_lc_master$TIMESTAMP, fp_lc_master$time.id)


```


#Creating DOY
```{r}
MET_gap_filled$DOY <- MET_gap_filled$TIMESTAMP$year + 1900 +
  (MET_gap_filled$TIMESTAMP$yday) / 366

######################################
fp_lc_master$DOY <- fp_lc_master$TIMESTAMP$year + 1900 +
  (fp_lc_master$TIMESTAMP$yday) / 366


```

#merging gap filled and post filter data based on time id
```{r}
MET_Gap_LC <- merge.data.frame(
  MET_gap_filled,
  fp_lc_master[, -which(colnames(fp_lc_master) == "TIMESTAMP")],
  by = "time.id",
  all.x  = TRUE,
  sort = TRUE
)

```

#creating DOY for gap fill post filter

```{r}
MET_Gap_LC$DOY <- 
  MET_Gap_LC$TIMESTAMP$year + 1900 +
  (MET_Gap_LC$TIMESTAMP$yday) / 366

```
#creating vpd column
```{r}
MET_Gap_LC$VPD <-
  rH.to.VPD(
    MET_Gap_LC$RH_Avg_GF / 100,
    MET_Gap_LC$AirT_Avg_GF,
    Esat.formula = c("Sonntag_1990", "Alduchov_1996",
                     "Allen_1998"),
    constants = bigleaf.constants()
  )

```

#Sorting into pre-compost and post compost application treatment area

```{r}

#Sorting the treatment area into the pre and post compost application for analysis
MET_Gap_LC $treat_pre_post_cmpst_filt<-rep("exclude",nrow(MET_Gap_LC))

MET_Gap_LC$treat_pre_post_cmpst_filt[which(!is.na(MET_Gap_LC$fpt_weight_treatment)&
                                 MET_Gap_LC$fpt_weight_treatment>=0.7&
                 MET_Gap_LC$TIMESTAMP> as.POSIXct("2020-10-16")         
                 )        
                 ]<-"treatment_post_compost" 

#######################################################

MET_Gap_LC$treat_pre_post_cmpst_filt[which(!is.na(MET_Gap_LC$fpt_weight_treatment)&
                                 MET_Gap_LC$fpt_weight_treatment>= 0.7 &
                 MET_Gap_LC$TIMESTAMP < as.POSIXct("2020-10-16")         
                 )        
                 
                                 ]<-"treatment_pre_compost" 

######################################################

MET_Gap_LC$treat_pre_post_cmpst_filt[which(!is.na(MET_Gap_LC$fpt_weight_treatment)&
                                 MET_Gap_LC$fpt_weight_treatment <0.3&
                 MET_Gap_LC$TIMESTAMP> as.POSIXct("2020-10-16")         
                 )        
                 ]<-"control_post_compost"

####################################################

MET_Gap_LC$treat_pre_post_cmpst_filt[which(!is.na(MET_Gap_LC$fpt_weight_treatment)&
                                 MET_Gap_LC$fpt_weight_treatment < 0.3 &
                 MET_Gap_LC$TIMESTAMP < as.POSIXct("2020-10-16")         
                 )        
                 
                                 ]<-"control_pre_compost" 


table(MET_Gap_LC$treat_pre_post_cmpst_filt)

```



```{r}
#colnames(MET_Gap_LC)
```


```{r}
write.csv(MET_Gap_LC,
          paste(out.path,Sys.Date(),"_MET_GAP_LC.csv",sep=""),
          quote = T,
          row.names = F)
```
#Sorting out treatment data post compost application for readyproc

```{r}
data.reddy_proc_treat_post_compost<-data.frame(
                    TIMESTAMP = MET_Gap_LC$TIMESTAMP,
                    H= MET_Gap_LC$H,  ## H
                    LE=MET_Gap_LC$LE,    ## LE
                    h2o_flux = MET_Gap_LC$h2o_flux, #h20flux
                    NEE=MET_Gap_LC$co2_flux ,  ## c02 flux\
                    rH = MET_Gap_LC$RH_Avg_GF, #gapfilled relative humidity
                    Ustar = MET_Gap_LC$u.,   #ustar
                    Tsoil = MET_Gap_LC$Soil_temp_Avg_GF_15cm, #gapfilled soil temperature
                    Tair = MET_Gap_LC$AirT_Avg_GF, #gapfilled air temperature
                    Rg=MET_Gap_LC$Rg_Avg_GF,  ## incoming solar radiation
                    treatment = MET_Gap_LC$treat_pre_post_cmpst_filt
                     
)



head(data.reddy_proc_treat_post_compost, 100)


summary(data.reddy_proc_treat_post_compost)

# write.csv(data.reddy_proc_treat,
#           paste(out.path,Sys.Date(),"_compost_treat_reddy_proc.csv",sep=""),
#           quote = T,
#           row.names = F)
```



#Turning NEE, LE. H20 flux values that are not treatment post compost to NA's for ready proc gapfilling
```{r}
#Making all NEE values NA that are not treatment_post_compost
data.reddy_proc_treat_post_compost$NEE[(data.reddy_proc_treat_post_compost $treatment != "treatment_post_compost")] <- NA

#Making all H values NA that are not treatment post compost
data.reddy_proc_treat_post_compost$H[(data.reddy_proc_treat_post_compost $treatment != "treatment_post_compost")] <- NA


#Making all LE values NA that are not treatment post compost
data.reddy_proc_treat_post_compost$LE[(data.reddy_proc_treat_post_compost $treatment != "treatment_post_compost")] <- NA

#Making all H20 flux values NA that are not treatment post compost
data.reddy_proc_treat_post_compost$h2o_flux[(data.reddy_proc_treat_post_compost $treatment != "treatment_post_compost")] <- NA



tail(data.reddy_proc_treat_post_compost, 50
     )


```


#preparing treatment side data post compost application for GAM gap_filling
```{r}
data.GAM_treat_post_compost<-data.frame(
                    TIMESTAMP = MET_Gap_LC$TIMESTAMP,
                    H= MET_Gap_LC$H,  ## H
                    LE=MET_Gap_LC$LE,    ## LE
                    h2o_flux = MET_Gap_LC$h2o_flux, #h20flux
                    NEE=MET_Gap_LC$co2_flux ,  ## c02 flux\
                    rH = MET_Gap_LC$RH_Avg_GF, #gapfilled relative humidity
                    Ustar = MET_Gap_LC$u.,   #ustar
                    Tsoil_0cm = MET_Gap_LC$Soil_temp_control_GF_0cm, #gapfilled soil temperature
                    Tsoil_5cm = MET_Gap_LC$Soil_temp_control_GF_5cm,
                    Tsoil_10cm = MET_Gap_LC$Soil_temp_control_GF_10cm,
                    Tsoil_15cm = MET_Gap_LC$Soil_temp_control_GF_15cm,
                    Tsoil_30cm = MET_Gap_LC$Soil_temp_control_GF_30cm,
                    Tair = MET_Gap_LC$AirT_Avg_GF, #gapfilled air temperature
                    VWC = MET_Gap_LC$VWC_Avg,
                    Rg=MET_Gap_LC$Rg_Avg_GF,  ## incoming solar radiation
                    precip =MET_Gap_LC$Precip_mm_Tot,
                    VPD= MET_Gap_LC$VPD,
                    treatment = MET_Gap_LC$treat_pre_post_cmpst_filt
                     
)



head(data.GAM_treat_post_compost, 100)


summary(data.GAM_treat_post_compost)

```


#Turning NEE, LE. H20 flux values that are not treatment post compost to NA's for GAM gapfilling
```{r}
#Making all NEE values NA that are not treatment_post_compost
data.GAM_treat_post_compost$NEE[(data.GAM_treat_post_compost $treatment != "treatment_post_compost")] <- NA

#Making all H values NA that are not treatment post compost
data.GAM_treat_post_compost$H[(data.GAM_treat_post_compost $treatment != "treatment_post_compost")] <- NA


#Making all LE values NA that are not treatment post compost
data.GAM_treat_post_compost$LE[(data.GAM_treat_post_compost $treatment != "treatment_post_compost")] <- NA

#Making all H20 flux values NA that are not treatment post compost
data.GAM_treat_post_compost$h2o_flux[(data.GAM_treat_post_compost $treatment != "treatment_post_compost")] <- NA



tail(data.GAM_treat_post_compost, 50
     )


```

#All of the data formatted for simplicity. maybe use for GAM
```{r}
data_GAM<-data.frame(
                    TIMESTAMP = MET_Gap_LC$TIMESTAMP,
                    H= MET_Gap_LC$H,  ## H
                    LE=MET_Gap_LC$LE,    ## LE
                    h2o_flux = MET_Gap_LC$h2o_flux, #h20flux
                    NEE=MET_Gap_LC$co2_flux ,  ## c02 flux\
                    rH = MET_Gap_LC$RH_Avg_GF, #gapfilled relative humidity
                    Ustar = MET_Gap_LC$u.,   #ustar
                    Tsoil_0cm = MET_Gap_LC$Soil_temp_control_GF_0cm, #gapfilled soil temperature
                    Tsoil_5cm = MET_Gap_LC$Soil_temp_control_GF_5cm,
                    Tsoil_10cm = MET_Gap_LC$Soil_temp_control_GF_10cm,
                    Tsoil_15cm = MET_Gap_LC$Soil_temp_control_GF_15cm,
                    Tsoil_30cm = MET_Gap_LC$Soil_temp_control_GF_30cm,
                    Tair = MET_Gap_LC$AirT_Avg_GF, #gapfilled air temperature
                    VWC_Control_GF = MET_Gap_LC$VWC_control_GF,
                    Rg=MET_Gap_LC$Rg_Avg_GF,  ## incoming solar radiation
                    precip =MET_Gap_LC$Precip_mm_Tot,
                    VPD= MET_Gap_LC$VPD,
                    treatment = MET_Gap_LC$treat_pre_post_cmpst_filt
                     
)



head(data_GAM, 100)


summary(data_GAM)
```



#Formating pre compost application data
```{r}
data_GAM_pre_compost<-data.frame(
                    TIMESTAMP = MET_Gap_LC$TIMESTAMP,
                    H= MET_Gap_LC$H,  ## H
                    LE=MET_Gap_LC$LE,    ## LE
                    h2o_flux = MET_Gap_LC$h2o_flux, #h20flux
                    NEE=MET_Gap_LC$co2_flux ,  ## c02 flux\
                    rH = MET_Gap_LC$RH_Avg_GF, #gapfilled relative humidity
                    Ustar = MET_Gap_LC$u.,   #ustar
                    Tsoil_0cm = MET_Gap_LC$Soil_temp_control_GF_0cm, #gapfilled soil temperature
                    Tsoil_5cm = MET_Gap_LC$Soil_temp_control_GF_5cm,
                    Tsoil_10cm = MET_Gap_LC$Soil_temp_control_GF_10cm,
                    Tsoil_15cm = MET_Gap_LC$Soil_temp_control_GF_15cm,
                    Tsoil_30cm = MET_Gap_LC$Soil_temp_control_GF_30cm,
                    Tair = MET_Gap_LC$AirT_Avg_GF, #gapfilled air temperature
                    VWC_Control_GF = MET_Gap_LC$VWC_control_GF,
                    Rg=MET_Gap_LC$Rg_Avg_GF,  ## incoming solar radiation
                    precip =MET_Gap_LC$Precip_mm_Tot,
                    VPD= MET_Gap_LC$VPD,
                    treatment = MET_Gap_LC$treat_pre_post_cmpst_filt
                     
)



head(data_GAM_pre_compost, 100)


summary(data_GAM_pre_compost)

```



#Turning NEE, LE. H20 flux values that are not Control pre or post compost, or treatment pre compost to NA's for attempt at ready proc gapfilling
```{r}
#Making all NEE values NA that are not control pre or post compost. 


data_GAM_pre_compost$NEE[(data_GAM_pre_compost $treatment == "treatment_post_compost")] <- NA

data_GAM_pre_compost$NEE[(data_GAM_pre_compost $treatment == "exclude")] <- NA


#Making H values NA

data_GAM_pre_compost$H[(data_GAM_pre_compost $treatment == "treatment_post_compost")] <- NA

data_GAM_pre_compost$H[(data_GAM_pre_compost $treatment == "exclude")] <- NA



#Making all LE values NA that are not control pre or post compost


data_GAM_pre_compost$LE[(data_GAM_pre_compost $treatment == "treatment_post_compost")] <- NA

data_GAM_pre_compost$LE[(data_GAM_pre_compost $treatment == "exclude")] <- NA



#Making all H20 flux values NA that are not control pre or post compost


data_GAM_pre_compost$h2o_flux[(data_GAM_pre_compost $treatment == "treatment_post_compost")] <- NA

data_GAM_pre_compost$h2o_flux[(data_GAM_pre_compost $treatment == "exclude")] <- NA




tail(data_GAM_pre_compost, 50
     )


```

#Formatting post compost application data control data
```{r}
data_GAM_Control_post_compost<-data.frame(
                    TIMESTAMP = MET_Gap_LC$TIMESTAMP,
                    H= MET_Gap_LC$H,  ## H
                    LE=MET_Gap_LC$LE,    ## LE
                    h2o_flux = MET_Gap_LC$h2o_flux, #h20flux
                    NEE=MET_Gap_LC$co2_flux ,  ## c02 flux\
                    rH = MET_Gap_LC$RH_Avg_GF, #gapfilled relative humidity
                    Ustar = MET_Gap_LC$u.,   #ustar
                    Tsoil_0cm = MET_Gap_LC$Soil_temp_control_GF_0cm, #gapfilled soil temperature
                    Tsoil_5cm = MET_Gap_LC$Soil_temp_control_GF_5cm,
                    Tsoil_10cm = MET_Gap_LC$Soil_temp_control_GF_10cm,
                    Tsoil_15cm = MET_Gap_LC$Soil_temp_control_GF_15cm,
                    Tsoil_30cm = MET_Gap_LC$Soil_temp_control_GF_30cm,
                    Tair = MET_Gap_LC$AirT_Avg_GF, #gapfilled air temperature
                    VWC_Control_GF = MET_Gap_LC$VWC_control_GF,
                    Rg=MET_Gap_LC$Rg_Avg_GF,  ## incoming solar radiation
                    precip =MET_Gap_LC$Precip_mm_Tot,
                    VPD= MET_Gap_LC$VPD,
                    treatment = MET_Gap_LC$treat_pre_post_cmpst_filt
                     
)



head(data_GAM_Control_post_compost, 100)


summary(data_GAM_Control_post_compost)
```



#Making Data that is only post compost application control side with which to test the GAM model against. 
```{r}
#Making all NEE values NA that are not control_post_compost
data_GAM_Control_post_compost$NEE[(data_GAM_Control_post_compost $treatment != "control_post_compost")] <- NA

#Making all H values NA that are not control_post_compost
data_GAM_Control_post_compost$H[(data_GAM_Control_post_compost $treatment != "control_post_compost")] <- NA


#Making all LE values NA that are not control_post_compost
data_GAM_Control_post_compost$LE[(data_GAM_Control_post_compost $treatment != "control_post_compost")] <- NA

#Making all H20 flux values NA that are not control_post_compost
data_GAM_Control_post_compost$h2o_flux[(data_GAM_Control_post_compost $treatment != "control_post_compost")] <- NA



tail(data_GAM_Control_post_compost, 50
     )
```

#writing CSV of treatment side data to be gap_filled in ready proc
```{r}
write.csv(data.reddy_proc_treat_post_compost,
          paste(out.path,Sys.Date(),"_post_compost_treat_reddy_proc.csv",sep=""),
          quote = T,
          row.names = F)
```

#writing CSV of treatment side data to be gap_filled by GAM
```{r}
write.csv(data.GAM_treat_post_compost,
          paste(out.path,Sys.Date(),"_post_compost_treat_GAM.csv",sep=""),
          quote = T,
          row.names = F)
```


#writing CSV of Data for GAM model fluxes before compost application 
```{r}

write.csv(data_GAM_pre_compost,
          paste(out.path,Sys.Date(),"_pre_compost_GAM_data.csv",sep=""),
          quote = T,
          row.names = F)

```


#writing CSV of control side data post compost application with which to test the GAM model against. 
```{r}
write.csv(data_GAM_Control_post_compost,
          paste(out.path,Sys.Date(),"_control_post_compost_GAM_data.csv",sep=""),
          quote = T,
          row.names = F)

```

```{r}

write.csv(data_GAM,
          paste(out.path,Sys.Date(),"_all_data_gam.csv",sep=""),
          quote = T,
          row.names = F)

```

```{r}
#ANCOVA and Daytime NEE all year Comparison treatment and control area
# NEE_by_fp_LC_all_year<- glmer( ~ Rg_f
#                      + treat_pre_post_cmpst_filt +(1|treat_pre_post_cmpst_filt),
#                   data = MET_Gap_LC[MET_Gap_LC$PotRad_U50 >0 &
#                                  MET_Gap_LC$treat_pre_post_cmpst_filt!="exclude",])
# 
# summary(NEE_by_fp_LC_all_year)
# Anova(NEE_by_fp_LC_all_year)
# shapiro.test(resid(NEE_by_fp_LC_all_year))

```
