---
title: "Bootstrap GAM"
output: html_document
---
```{r}
require(dplyr)
require(mgcv)
library(mgcv)
library(ggplot2)
library(ISLR)
library(mgcv)
library(boot)
require(matrixStats)
```

#load mud co2 data 

```{r}

root.path<-"D:\\SanDiskSecureAccess\\EdenLanding\\EL_chamber_data\\GAM_bootstrap\\DATA\\"


file1<-paste0("mud")

mud<-read.csv(paste(root.path,file1,".csv",sep=""),
                header=F,
                skip=1,
                na.strings="NAN",
                stringsAsFactors=F)

colnames(mud)<-colnames(read.csv(paste(root.path,file1,".csv",sep=""),                                                                 na.strings="NaN"))

```

## Mud CO2
  you choose number of times to be run (line 49)
  choose sample size (line 55)
  creates n number of gams (line 56)
  makes the predictions on each gam (ine 58)
  unlists and transposes the predictions (lines 61 and 62)
  puts all in one df (lines 65 and 70)
  find the mean and the 95% CI for each point  (lines 73 to 87)
  puts the mean, upper, and lower CI into one dataframe called mean_df (lines 90-92)

```{r}
#if an error says vector length not the same you may have a column with too many NaN's


n<-1:500 ##enter number of times to be run here 

master_mud_pred = list()

for (x in n) 
  {
    mud_co2_sample<-sample_n(mud,100)    ####choose sample size #####################
        gam <- gam(F_CO2_umol~s(elevation,k=5)+s(LE)+s(PAR)+s(TS_5cm),data = mud_co2_sample, method = "REML")
        #assign(paste("gam_mud_co2",x,sep="_"),gam)         #this is if we want to see each gam and its info separately in the environment on the right 
    pred_mud_co2<-predict(gam,mud,type="link",se.fit=TRUE,terms=NULL,
        exclude=NULL,block.size=NULL,newdata.guaranteed=FALSE,
        na.action=na.pass,unconditional=FALSE,iterms.type=NULL)
    mud_co2_pred<- data.frame(matrix(unlist(pred_mud_co2), nrow=length(pred_mud_co2), byrow=TRUE))
        mud_co2_pred<- as.data.frame(t(mud_co2_pred))
        mud_co2_pred = subset(mud_co2_pred, select = -c(V2))
        # mud_co2_pred$x <- x  use this if we want to know which run is which. 
        master_mud_pred[[x]] <- mud_co2_pred
        #assign(paste("mud_co2_pred",x,sep="_"),mud_co2_pred)  ##this is if we want to see each prediction separately (has standard error)
}

#put all the predicted data together 
master_mud_co2 = do.call(cbind, master_mud_pred)

#find the mean 
mean<-rowMeans(master_mud_co2, na.rm=TRUE)
mean_df<- as.data.frame(mean)  #make it a data frame to plot

#find the standard deviation 
master_mud_co2_matrix<-data.matrix(master_mud_co2, rownames.force = NA)  #to be able to find row stdev, have to convert to numerix matrix
stdev<-rowSds(master_mud_co2_matrix, na.rm=TRUE)
stdev_df<- as.data.frame(stdev) #make it a data frame to plot

#find upper lim of CI
upperlim=mean_df$mean+1.960*stdev_df$stdev/sqrt(length(n)) #zvalue for 95% CI= 1.960
upperlim_df<- as.data.frame(upperlim)

#find lower lim of CI
lowerlim=mean_df$mean-1.960*stdev_df$stdev/sqrt(length(n)) #zvalue for 95% CI= 1.960
lowerlim_df<- as.data.frame(lowerlim)

#put needed values in a dataframe 
mean_df$lowerCI=lowerlim_df$lowerlim
mean_df$upperCI=upperlim_df$upperlim
mean_df$begin_time=mud$begin_time
  
  
```

#plots 
Two plots, but they are the same. Just different colors

```{r}
#plots
plot(mud$begin_time,
      upperlim_df$upperlim, lty = 'dashed', col = 'red')
lines(mud$begin_time,
      lowerlim_df$lowerlim, lty = 'dashed', col = 'red')
lines(mud$begin_time,
     mean_df$mean,
     col="black")
 legend(900, 15,
         legend = c("95% CI","mean"),
           pch = 16,
         col = c( "red", "black"),
         bty = "n")



plot(mud$begin_time,
       upperlim_df$upperlim,
       col="green")
     # pch = 16,)
lines(mud$begin_time,
      upperlim_df$upperlim,
       col="green")

points(mud$begin_time,
       lowerlim_df$lowerlim,
       col="blue")
     # pch = 16,)
lines(mud$begin_time,
      lowerlim_df$lowerlim,
      col="blue")
points(mud$begin_time,
     mean_df$mean,
     col="red")
      #pch = 16,)
lines(mud$begin_time
      ,mean_df$mean,
     col="red")
  legend(900, 10,
         legend = c("upper 95% CI","lower 95% CI","mean"),
           pch = 16,
         col = c( "green", "blue","red"),
         bty = "n")
  
```

##save predictions

```{r}
#save dataframe
out.path<-"D:\\SanDiskSecureAccess\\EdenLanding\\EL_chamber_data\\GAM_bootstrap\\DATA\\predicted_data_CI\\"
write.csv(mean_df,
          paste(out.path,"mud_co2.csv",sep=""),
          quote = T,
          row.names = F)
```
