---
title: "Bootstrap treatment side GAM Concord"
output: html_document
---
```{r}
require(dplyr)
require(mgcv)
library(mgcv)
library(ggplot2)
library(ISLR)
library(mgcv)
library(boot)
require(matrixStats)
library(REddyProc)

library(bigleaf)
```

#load tower and eosense data

#Defining the data I/O directory
```{r}
## change root.path as needed
root.path<-"C:\\Users\\Tommy\\flux\\Data-exploring\\02_Concord\\"
#root.path<-"D:\\Housen\\Flux\\Data-exploring\\02_Concord_Eden\\"

GAM.path<-paste0(root.path,"14_GAM_ready_Data\\") # this is tower data for the GAM model lives



 


out.path<-paste0(root.path, "15_GAM_predict_data\\")
```

#reading in a specific file

```{r}
## use follows to specify the versions of the combined file
# file name of the combined_file
cdata.GAM_treat_post_compost<-paste0("2021-09-14_post_compost_treat_GAM.csv")





 
```


#Tower data for the GAM model

```{r}
## read in full output file of gap filled data
GAM_treat_post_compost <-
  read.csv(
    paste0(GAM.path, cdata.GAM_treat_post_compost, sep = ""),
    header = T,
    na.strings = "NA",
    stringsAsFactors = F
  )
colnames(GAM_treat_post_compost) <-
  colnames(read.csv(
    paste(GAM.path, cdata.GAM_treat_post_compost, sep = ""),
    header = T,
    na.strings = "NA"
  ))

head(GAM_treat_post_compost)

tail(GAM_treat_post_compost)

```




#adding POSIXT format back to GAM_treat_post_compost_data
```{r}


GAM_treat_post_compost$TIMESTAMP <- strptime(paste(GAM_treat_post_compost$TIMESTAMP),
                                 format = "%m/%d/%Y %H:%M",
                                 tz = "Etc/GMT-8")


GAM_treat_post_compost$TIMESTAMP[500:560]

head(GAM_treat_post_compost)

plot( GAM_treat_post_compost$TIMESTAMP, GAM_treat_post_compost$NEE)
```

```{r}
GAM_treat_post_compost$time.id <- GAM_treat_post_compost$TIMESTAMP$year + 1900 +
  (GAM_treat_post_compost$TIMESTAMP$yday) / 366 +
  (GAM_treat_post_compost$TIMESTAMP$hour) / 366 / 24 +
  (GAM_treat_post_compost$TIMESTAMP$min) / 366 / 24 / 60

GAM_treat_post_compost$time.id[1:50]
plot(GAM_treat_post_compost$TIMESTAMP, GAM_treat_post_compost$time.id)

```









#plotting in blue NEE from Tower 
```{r}


plot(GAM_treat_post_compost$TIMESTAMP, GAM_treat_post_compost$NEE, 
     ylim = c(-20,20),
     col= "blue")



```
```{r}
boxplot(GAM_treat_post_compost$NEE,
  ylab = "NEE",
  main = "Boxplot of tower NEE"
)   


box_stats_treat <-boxplot.stats(GAM_treat_post_compost$NEE)$out



sort.int(box_stats_treat)
```
```{r}
#from overall data removing any points greater than 6.405
GAM_treat_post_compost$NEE[ GAM_treat_post_compost$NEE > 6.601] <-NA

GAM_treat_post_compost$NEE[ GAM_treat_post_compost$NEE < -6.723 ] <-NA

summary(GAM_treat_post_compost$NEE)
```



## treatment side CO2
  you choose number of times to be run (line 49)
  choose sample size (line 55)
  creates n number of gams (line 56)
  makes the predictions on each gam (ine 58)
  unlists and transposes the predictions (lines 61 and 62)
  puts all in one df (lines 65 and 70)
  find the mean and the 95% CI for each point  (lines 73 to 87)
  puts the mean, upper, and lower CI into one dataframe called mean_df (lines 90-92)

```{r}
#if an error says vector length not the same you may have a column with too many NaN's

n <- 1:30 ##enter number of times to be run here 

## use data.frame since you only have 1 fixed-length vector each time
master_treatment_pred = data.frame(NULL)

# create progress bar
pb <- txtProgressBar(min = 0, max = max(n), style = 3)
for (x in n)
{
  ## use this to track time for each major steps (could be comment out)
  time.ini <- Sys.time()
  
  #### the following part deal with re-sampling (bootstrapping)
  ## use the original data
  if(x == 1){
  treatment_co2_sample <- GAM_treat_post_compost
    
  }else{
  ## re-sample data for n-1 times, with the same sample size, but with repeats 
  treatment_co2_sample <-
    sample_n(GAM_treat_post_compost, size = nrow(GAM_treat_post_compost), replace = T)    
    
  }
  # return time (could comment out)
  print(Sys.time() - time.ini)
  
  ## avoid using names that is designated in R, e.g., gam     
  nee.gam <-
    gam(
      NEE ~ s(VWC, precip, k = 30) + s(Rg, Tair, VPD, k = 30) ,
      data = treatment_co2_sample,
      method = "REML"
    )
  # return time (could comment out)
  print(Sys.time() - time.ini)
  
  #this is if we want to see each gam and its info separately in the environment on the right
  pred_treatment_co2 <-
    predict(
      nee.gam,
      GAM_treat_post_compost,
      type = "link",
      se.fit = FALSE,
      terms = NULL,
      exclude = NULL,
      block.size = NULL,
      newdata.guaranteed = FALSE,
      na.action = na.pass,
      unconditional = FALSE,
      iterms.type = NULL
    )
  # return time (could comment out)
  print(Sys.time() - time.ini)
  
  treat_co2_pred <-
    data.frame(matrix(
      unlist(pred_treatment_co2),
      nrow = length(pred_treatment_co2),
      byrow = TRUE
    ))
  #treat_co2_pred <- as.data.frame(t(treat_co2_pred))
  #treat_co2_pred = subset(treat_co2_pred, select = -c(V2))
  # treat_co2_pred$x <- x  use this if we want to know which run is which.
  if(x == 1){
    master_treatment_pred <- treat_co2_pred
  }else{
    master_treatment_pred <- cbind.data.frame(master_treatment_pred,
                                            treat_co2_pred)   
  }
  
  #assign(paste("treat_co2_pred",x,sep="_"),treat_co2_pred)  ##this is if we want to see each prediction separately (has standard error)
  
  # return time (could comment out)
  print(Sys.time() - time.ini)
  
  # update progress bar
  Sys.sleep(0.1)
  setTxtProgressBar(pb, x)
}

#put all the predicted data together 
#master_control_co2 = do.call(cbind, master_treatment_pred)

#find the mean 
GAM_treat_post_compost$pred_GAM_NEE <- rowMeans(master_treatment_pred, na.rm = TRUE)
#mean<-rowMeans(master_control_co2, na.rm=TRUE)
#mean_df<- as.data.frame(mean)  #make it a data frame to plot

#find the standard deviation 
#master_control_co2_matrix<-data.matrix(master_control_co2, rownames.force = NA)  #to be able to find row stdev, have to convert to numerix matrix
GAM_treat_post_compost$NEE_pred_stdev <- apply(master_treatment_pred, 1, sd, na.rm = TRUE)
#stdev<-rowSds(master_control_co2_matrix, na.rm=TRUE)
#stdev_df<- as.data.frame(stdev) #make it a data frame to plot

#find upper lim of CI
#upperlim=mean_df$mean+1.960*stdev_df$stdev/sqrt(length(n)) #zvalue for 95% CI= 1.960
#upperlim_df<- as.data.frame(upperlim)
GAM_treat_post_compost$upperCI <- apply(master_treatment_pred, 1, quantile, probs = 0.975, na.rm = TRUE)

#find lower lim of CI
#lowerlim=mean_df$mean-1.960*stdev_df$stdev/sqrt(length(n)) #zvalue for 95% CI= 1.960
#lowerlim_df<- as.data.frame(lowerlim)
GAM_treat_post_compost$lowerCI <- apply(master_treatment_pred, 1, quantile, probs = 0.025, na.rm = TRUE)

#put needed values in a dataframe 
#mean_df$lowerCI=lowerlim_df$lowerlim
#mean_df$upperCI=upperlim_df$upperlim
#mean_df$TIMESTAMP=GAM_treat_post_compost$TIMESTAMP
  
  
```

#plots 
Two plots, but they are the same. Just different colors

```{r}
#plots
plot(GAM_treat_post_compost$TIMESTAMP,
      GAM_treat_post_compost$upperCI, lty = 'dashed', col = 'red',  ylim = c(-60,20))
lines(GAM_treat_post_compost$TIMESTAMP,
      GAM_treat_post_compost$lowerCI, lty = 'dashed', col = 'red',   ylim = c(-60,20))
lines(GAM_treat_post_compost$TIMESTAMP,
     GAM_treat_post_compost$pred_GAM_NEE,
     col="black",   ylim = c(-60,20))
 legend(x= "topleft",
         legend = c("95% CI","mean"),
           pch = 16,
         col = c( "red", "black"),
         bty = "n")


# 
# plot(GAM_treat_post_compost$TIMESTAMP,
#        upperlim_df$upperlim,
#        col="green",
#      ylim = c(-60,20))
#      # pch = 16,)
# lines(GAM_treat_post_compost$TIMESTAMP,
#       upperlim_df$upperlim,
#        col="green",
#       ylim = c(-60,20))
# 
# points(GAM_treat_post_compost$TIMESTAMP,
#        lowerlim_df$lowerlim,
#        col="blue",)
#      # pch = 16,
# ylim = c(-60,20)
# lines(GAM_treat_post_compost$TIMESTAMP,
#       lowerlim_df$lowerlim,
#       col="blue",
#       ylim = c(-60,20))
# points(GAM_treat_post_compost$TIMESTAMP,
#      mean_df$mean,
#      col="red",
#       #pch = 16,)
# ylim = c(-60,20))
# lines(GAM_treat_post_compost$TIMESTAMP
#       ,mean_df$mean,
#      col="red",
#      ylim = c(-60,20))
#   legend(
#          legend = c("upper 95% CI","lower 95% CI","mean"),
#            pch = 16,
#          col = c( "green", "blue","red"),
#          bty = "n")
  
```

```{r}
  #creating a new NEE column with the modeled treatment side data
GAM_treat_post_compost $GAM_treat_GF_GAM <- (GAM_treat_post_compost$NEE * 1)


summary(GAM_treat_post_compost $GAM_treat_GF_GAM)



#making any NA values measured by the tower the treatment gapfilled values.
GAM_treat_post_compost$GAM_treat_GF_GAM[is.na(GAM_treat_post_compost$GAM_treat_GF_GAM)] <-
  GAM_treat_post_compost$pred_GAM_NEE[is.na(GAM_treat_post_compost$GAM_treat_GF_GAM)]


summary(GAM_treat_post_compost $GAM_treat_GF_GAM)

plot(GAM_treat_post_compost$GAM_treat_GF_GAM)

```

```{r}
boxplot(GAM_treat_post_compost$GAM_treat_GF_GAM,
  ylab = "NEE",
  main = "Boxplot of tower NEE"
)   


box_stats_GF_treat <-boxplot.stats(GAM_treat_post_compost$GAM_treat_GF_GAM)$out

min(box_stats_GF_treat)

sort.int(box_stats_GF_treat)
```


#cleaning up last outliers
```{r}
#from overall data removing any points greater than originally identified outliers


GAM_treat_post_compost$GAM_treat_GF_GAM[ GAM_treat_post_compost$GAM_treat_GF_GAM < -8.978 ] <-NA

summary(GAM_treat_post_compost$GAM_treat_GF_GAM)
```


```{r}
#plotting
plot(GAM_treat_post_compost$TIMESTAMP,GAM_treat_post_compost$GAM_treat_GF_GAM,
     ylim = c(-20,50),
     col= 'red')

par(new=TRUE)
plot(GAM_treat_post_compost$TIMESTAMP, GAM_treat_post_compost$NEE,
     ylim = c(-20,50))

plot(GAM_treat_post_compost$TIMESTAMP, GAM_treat_post_compost$pred_GAM_NEE)

with(GAM_treat_post_compost, boxplot(GAM_treat_post_compost$GAM_treat_GF_GAM~treatment, ylim =c (-40,40)
                          ))
#comparing NEE data to gap filled data
summary(GAM_treat_post_compost$NEE)
summary(GAM_treat_post_compost $GAM_treat_GF_GAM)




```

#removing outliers No longer neccesary
```{r}
#some  outliers. Removing any values greater or smaller than Max and min original NEE values recorded on the control side.

#from overall data removing any points greater than 22.936
# GAM_treat_post_compost$GAM_treat_GF_GAM[ GAM_treat_post_compost$GAM_treat_GF_GAM > 15.007] <-NA
# 
# GAM_treat_post_compost$GAM_treat_GF_GAM[ GAM_treat_post_compost$GAM_treat_GF_GAM < -34.211  ] <-NA





##########removing upper bound outliers#########




#from the data post compost application removing any data points greater than 15.07 and less than -34.211. The max and min values recorded by the tower during that time
# GAM_treat_post_compost$upperCI[ GAM_treat_post_compost$upperCI > 15.007   ] <-NA
# 
# GAM_treat_post_compost$upperCI[ GAM_treat_post_compost$upperCI < -34.211  ] <-NA


###############removing lower bound outliers############



#from the data post compost application removing any data points greater than 15.07 and less than -34.211. The max and min values recorded by the tower during that time
# GAM_treat_post_compost$lowerCI[ GAM_treat_post_compost$lowerCI > 15.007   ] <-NA
# 
# GAM_treat_post_compost$lowerCI[ GAM_treat_post_compost$lowerCI < -34.211  ] <-NA


#comparing orginal NEE data to GF with GAM again
summary(GAM_treat_post_compost $GAM_treat_GF_GAM)
summary(GAM_treat_post_compost$NEE)

#comparing post compost application
summary(GAM_treat_post_compost $GAM_treat_GF_GAM)
summary(GAM_treat_post_compost$NEE)


#plotting overall data
plot(GAM_treat_post_compost$GAM_treat_GF_GAM ,
     ylim=c (-60,20),
     col ="red")
par(new= TRUE)
plot(GAM_treat_post_compost$NEE,
     ylim=c (-60,20),
     col ="blue")

#plotting data post compost application
plot(GAM_treat_post_compost$TIMESTAMP[GAM_treat_post_compost $ TIMESTAMP >as.POSIXct("2020-10-16")],GAM_treat_post_compost$GAM_treat_GF_GAM [GAM_treat_post_compost $ TIMESTAMP >as.POSIXct("2020-10-16")],
     ylim=c (-20,20),
     ylab = "NEE",
     xlab ="2020-2021",
     main = "Treatment Side tower data (blue) and GF GAM Data (red)",
     col ="red")
par(new= TRUE)
plot(GAM_treat_post_compost$TIMESTAMP[GAM_treat_post_compost $ TIMESTAMP >as.POSIXct("2020-10-16")],GAM_treat_post_compost$NEE[GAM_treat_post_compost $ TIMESTAMP >as.POSIXct("2020-10-16")],
     ylim=c (-20,20),
     ylab = "",
     xlab = "",
     col ="blue")
```


```{r}
#plots
plot(GAM_treat_post_compost$TIMESTAMP,
      GAM_treat_post_compost$upperCI, lty = 'dashed', col = 'red',  ylim = c(-60,20))
lines(GAM_treat_post_compost$TIMESTAMP,
      GAM_treat_post_compost$lowerCI, lty = 'dashed', col = 'red',   ylim = c(-60,20))
lines(GAM_treat_post_compost$TIMESTAMP,
     GAM_treat_post_compost$GAM_treat_GF_GAM,
     col="black",   ylim = c(-60,20))
 legend(x= "topleft",
         legend = c("95% CI","mean"),
           pch = 16,
         col = c( "red", "black"),
         bty = "n")
```

```{r}
#seeing which rows are duplicated
which(duplicated(GAM_treat_post_compost$TIMESTAMP))

#removing duplicated rows
GAM_treat_post_compost<-GAM_treat_post_compost[!duplicated(GAM_treat_post_compost$TIMESTAMP), ]

#checking that this worked

 which(duplicated(GAM_treat_post_compost$TIMESTAMP))
 
 #removing any rows with NA in time.id column
 GAM_treat_post_compost <- GAM_treat_post_compost[ !(GAM_treat_post_compost$time.id %in% c(NA)), ]
 
#removing any rows with NA in TIMESTAMP column 
  GAM_treat_post_compost <- GAM_treat_post_compost[ !(GAM_treat_post_compost$TIMESTAMP %in% c(NA)), ]
  
 which(duplicated(GAM_treat_post_compost$TIMESTAMP))
 
 summary(GAM_treat_post_compost $GAM_treat_GF_GAM[GAM_treat_post_compost $ TIMESTAMP >as.POSIXct("2020-10-16")])
 
 GAM_treat_post_compost
 





```


##save predictions

```{r}
#save dataframe

write.csv(GAM_treat_post_compost,
          paste(out.path,Sys.Date(),"_Boot_strap_Treatment_side_gap_filled_via_GAM.csv",sep=""),
          quote = T,
          row.names = F)
```
