---
title: "Bootstrap GAM Concord"
output: html_document
---
```{r}
require(dplyr)
require(mgcv)
library(mgcv)
library(ggplot2)
library(ISLR)
library(mgcv)
library(boot)
require(matrixStats)
```

#load tower and eosense data

#Defining the data I/O directory
```{r}
## change root.path as needed
root.path<-"C:\\Users\\Tommy\\flux\\Data-exploring\\02_Concord\\"
#root.path<-"D:\\Housen\\Flux\\Data-exploring\\02_Concord_Eden\\"

GAM.path<-paste0(root.path,"14_GAM_ready_Data\\") # this is tower data for the GAM model lives

eosense.path<- paste0(root.path,"14_GAM_ready_Data\\")#this is were the data for the eosense data for the GAM model lives

 


out.path<-paste0(root.path, "15_GAM_predict_data\\")
```

#reading in a specific file

```{r}
## use follows to specify the versions of the combined file
# file name of the combined_file
cdata.GAM_pre_compost<-paste0("2021-07-15_pre_compost_GAM_data.csv")



cdata.eo_sense <- paste("eo_sense_20210601.csv")

# cdata.GAM_test <- paste("2021-07-13_control_post_compost_GAM_data.csv")
 
```


#Tower data for the GAM model

```{r}
## read in full output file of gap filled data
GAM_pre_compost <-
  read.csv(
    paste0(GAM.path, cdata.GAM_pre_compost, sep = ""),
    header = T,
    na.strings = "NA",
    stringsAsFactors = F
  )
colnames(GAM_pre_compost) <-
  colnames(read.csv(
    paste(GAM.path, cdata.GAM_pre_compost, sep = ""),
    header = T,
    na.strings = "NA"
  ))

head(GAM_pre_compost)

tail(GAM_pre_compost)

```

#Read in eosense data for the GAm model

```{r}
## read in eo_sensee_data
eosense.data <-
  read.csv(
    paste0(eosense.path, cdata.eo_sense, sep = ""),
    header = T,
    na.strings = "NA",
    stringsAsFactors = F
  )
colnames(eosense.data) <-
  colnames(read.csv(
    paste(GAM.path, cdata.eo_sense, sep = ""),
    header = T,
    na.strings = "NA"
  ))

head(eosense.data)

tail(eosense.data)


```



#adding POSIXT format back to Gam_pre_compost_data
```{r}


GAM_pre_compost$TIMESTAMP <- strptime(paste(GAM_pre_compost$TIMESTAMP),
                                 format = "%m/%d/%Y %H:%M",
                                 tz = "Etc/GMT-8")


GAM_pre_compost$TIMESTAMP[500:560]

head(GAM_pre_compost)

plot( GAM_pre_compost$TIMESTAMP, GAM_pre_compost$NEE)
```

```{r}
GAM_pre_compost$time.id <- GAM_pre_compost$TIMESTAMP$year + 1900 +
  (GAM_pre_compost$TIMESTAMP$yday) / 366 +
  (GAM_pre_compost$TIMESTAMP$hour) / 366 / 24 +
  (GAM_pre_compost$TIMESTAMP$min) / 366 / 24 / 60

GAM_pre_compost$time.id[1:50]
plot(GAM_pre_compost$TIMESTAMP, GAM_pre_compost$time.id)
# which(duplicated(GAM_pre_compost$time.id))



# which(duplicated(GAM_pre_compost$TIMESTAMP))
# 
# 
# 
# which(duplicated(GAM_pre_compost$time.id))

# GAM_pre_compost %>% distinct(time.id, .keep_all = TRUE)
# 
# GAM_pre_compost[!duplicated(GAM_pre_compost$TIMESTAMP), ]

```



#creating timestamp for eosense data
```{r}

eosense.data$Year<-eosense.data$Year +2000


eosense.data


#combining month day year into a date column. 
eosense.data$Date<-paste(eosense.data$Month,eosense.data$Day, eosense.data$Year,sep="/")

head( eosense.data$Date, 50)

eosense.data

#creating a timestamp based on 
eosense.data$TIMESTAMP<-strptime(paste(eosense.data$Date,eosense.data$Time,sep=" "),
                          format="%m/%d/%Y %H:%M ",
                          tz = "Etc/GMT-8")


eosense.data

eosense.data$TIMESTAMP[1:50]

plot(eosense.data$TIMESTAMP, eosense.data$Flux)

```

```{r}
#creating time id for eosense data
eosense.data$time.id<-eosense.data$TIMESTAMP$year+1900+
  (eosense.data$TIMESTAMP$yday)/366+
  (eosense.data$TIMESTAMP$hour)/366/24+
  (eosense.data$TIMESTAMP$min)/366/24/60

eosense.data$time.id[1:50]
plot(eosense.data$TIMESTAMP,eosense.data$time.id)

which(duplicated(eosense.data$time.id))

eosense.data %>% distinct(time.id, .keep_all = TRUE)

head(eosense.data)
```


#creating full time stamp without gaps for for merging data
```{r}

# create a full timestamp, 30 mins
full.time<-data.frame(TIMESTAMP=
                        seq.POSIXt(min(min(GAM_pre_compost$TIMESTAMP),min(eosense.data$TIMESTAMP)),
                                   max(max(GAM_pre_compost$TIMESTAMP),max(eosense.data$TIMESTAMP)),
                                   units = "seconds", by = 1800),
                      stringsAsFactors=F)

full.time$TIMESTAMP<-strptime(full.time$TIMESTAMP,
                              format ="%Y-%m-%d %H:%M:%S",
                              tz = "Etc/GMT-8")

full.time$time.id <-full.time$TIMESTAMP$year+1900+
  (full.time$TIMESTAMP$yday)/366+
  (full.time$TIMESTAMP$hour)/366/24+
  (full.time$TIMESTAMP$min)/366/24/60 

print(paste("Starting timestamp:",full.time$TIMESTAMP[1]))
print(paste("Ending timestamp:",full.time$TIMESTAMP[nrow(full.time)]))

head(full.time)

which(duplicated(full.time$time.id))

```

#merging tower and eosense data
```{r}
tower_eo_sense.data<- merge.data.frame(full.time,
                         GAM_pre_compost[,-which(colnames(GAM_pre_compost)=="TIMESTAMP")],
                         by = "time.id",
                         all = TRUE,
                         sort = TRUE) 
#all=true what ever appears in each file is show in the file data file. sort tries to sort each data frame by merging. in this case probably doesnot matter. timestamp

tower_eo_sense.data<- merge.data.frame(tower_eo_sense.data,
                         eosense.data[,-which(colnames(eosense.data)=="TIMESTAMP")],
                         by = "time.id",
                         all = TRUE,
                         sort = TRUE) 

head(tower_eo_sense.data, 50)
tail(tower_eo_sense.data, 50)

tower_eo_sense.data
```









#plotting in blue NEE from Tower and red, flux from chamber
```{r}
plot(tower_eo_sense.data$TIMESTAMP, tower_eo_sense.data$Flux, 
     ylim = c(-20,20),
     col= "red")

par(new= TRUE)

plot(tower_eo_sense.data$TIMESTAMP, tower_eo_sense.data$NEE, 
     ylim = c(-20,20),
     col= "blue")



```



## control side CO2
  you choose number of times to be run (line 49)
  choose sample size (line 55)
  creates n number of gams (line 56)
  makes the predictions on each gam (ine 58)
  unlists and transposes the predictions (lines 61 and 62)
  puts all in one df (lines 65 and 70)
  find the mean and the 95% CI for each point  (lines 73 to 87)
  puts the mean, upper, and lower CI into one dataframe called mean_df (lines 90-92)

```{r}
#if an error says vector length not the same you may have a column with too many NaN's


n<-1:500 ##enter number of times to be run here 

master_control_pred = list()

for (x in n) 
  {
    control_co2_sample<-sample_n(tower_eo_sense.data,100)    ####choose sample size #####################
        gam <- gam(NEE ~s(Flux,k=12) + s(VWC_Control_GF, precip, k=30) + s( Rg, Tair,VPD, k=30) ,data = tower_eo_sense.data, method = "REML")
        #assign(paste("gam_mud_co2",x,sep="_"),gam)         #this is if we want to see each gam and its info separately in the environment on the right 
    pred_control_co2<-predict(gam,tower_eo_sense.data,type="link",se.fit=TRUE,terms=NULL,
        exclude=NULL,block.size=NULL,newdata.guaranteed=FALSE,
        na.action=na.pass,unconditional=FALSE,iterms.type=NULL)
    control_co2_pred<- data.frame(matrix(unlist(pred_control_co2), nrow=length(pred_control_co2), byrow=TRUE))
        control_co2_pred<- as.data.frame(t(control_co2_pred))
        control_co2_pred = subset(control_co2_pred, select = -c(V2))
        # control_co2_pred$x <- x  use this if we want to know which run is which. 
        master_control_pred[[x]] <- control_co2_pred
        #assign(paste("control_co2_pred",x,sep="_"),control_co2_pred)  ##this is if we want to see each prediction separately (has standard error)
}

#put all the predicted data together 
master_control_co2 = do.call(cbind, master_control_pred)

#find the mean 
mean<-rowMeans(master_control_co2, na.rm=TRUE)
mean_df<- as.data.frame(mean)  #make it a data frame to plot

#find the standard deviation 
master_control_co2_matrix<-data.matrix(master_control_co2, rownames.force = NA)  #to be able to find row stdev, have to convert to numerix matrix
stdev<-rowSds(master_control_co2_matrix, na.rm=TRUE)
stdev_df<- as.data.frame(stdev) #make it a data frame to plot

#find upper lim of CI
upperlim=mean_df$mean+1.960*stdev_df$stdev/sqrt(length(n)) #zvalue for 95% CI= 1.960
upperlim_df<- as.data.frame(upperlim)

#find lower lim of CI
lowerlim=mean_df$mean-1.960*stdev_df$stdev/sqrt(length(n)) #zvalue for 95% CI= 1.960
lowerlim_df<- as.data.frame(lowerlim)

#put needed values in a dataframe 
mean_df$lowerCI=lowerlim_df$lowerlim
mean_df$upperCI=upperlim_df$upperlim
mean_df$TIMESTAMP=tower_eo_sense.data $TIMESTAMP
  
  
```

#add those values to the original data from
```{r}
tower_eo_sense.data$pred_GAM_NEE=mean_df$mean
tower_eo_sense.data$lowerCI=lowerlim_df$lowerlim
tower_eo_sense.data$upperCI=upperlim_df$upperlim
```

#plots 
Two plots, but they are the same. Just different colors

```{r}
#plots
plot(tower_eo_sense.data$TIMESTAMP,
      tower_eo_sense.data$upperCI, lty = 'dashed', col = 'red',  ylim = c(-60,20))
lines(tower_eo_sense.data$TIMESTAMP,
      tower_eo_sense.data$lowerCI, lty = 'dashed', col = 'red',   ylim = c(-60,20))
lines(tower_eo_sense.data$TIMESTAMP,
     tower_eo_sense.data$pred_GAM_NEE,
     col="black",   ylim = c(-60,20))
 legend(x= "topleft",
         legend = c("95% CI","mean"),
           pch = 16,
         col = c( "red", "black"),
         bty = "n")


# 
# plot(tower_eo_sense.data$TIMESTAMP,
#        upperlim_df$upperlim,
#        col="green",
#      ylim = c(-60,20))
#      # pch = 16,)
# lines(tower_eo_sense.data$TIMESTAMP,
#       upperlim_df$upperlim,
#        col="green",
#       ylim = c(-60,20))
# 
# points(tower_eo_sense.data$TIMESTAMP,
#        lowerlim_df$lowerlim,
#        col="blue",)
#      # pch = 16,
# ylim = c(-60,20)
# lines(tower_eo_sense.data$TIMESTAMP,
#       lowerlim_df$lowerlim,
#       col="blue",
#       ylim = c(-60,20))
# points(tower_eo_sense.data$TIMESTAMP,
#      mean_df$mean,
#      col="red",
#       #pch = 16,)
# ylim = c(-60,20))
# lines(tower_eo_sense.data$TIMESTAMP
#       ,mean_df$mean,
#      col="red",
#      ylim = c(-60,20))
#   legend(
#          legend = c("upper 95% CI","lower 95% CI","mean"),
#            pch = 16,
#          col = c( "green", "blue","red"),
#          bty = "n")
  
```

```{r}
  #creating a new NEE column with the modeled control side data
tower_eo_sense.data $NEE_control_GF_GAM <- (tower_eo_sense.data$NEE * 1)


summary(tower_eo_sense.data $NEE_control_GF_GAM)



#making any NA values measured by the tower the chamber gapfilled values.
tower_eo_sense.data$NEE_control_GF_GAM[is.na(tower_eo_sense.data$NEE_control_GF_GAM)] <-
  tower_eo_sense.data$pred_GAM_NEE[is.na(tower_eo_sense.data$NEE_control_GF_GAM)]


summary(tower_eo_sense.data $NEE_control_GF_GAM)

plot(tower_eo_sense.data$NEE_control_GF_GAM)

```
```{r}
#plotting
plot(tower_eo_sense.data$TIMESTAMP,tower_eo_sense.data$NEE_control_GF_GAM,
     ylim = c(-20,50),
     col= 'red')

par(new=TRUE)
plot(tower_eo_sense.data$TIMESTAMP, tower_eo_sense.data$NEE,
     ylim = c(-20,50))

plot(tower_eo_sense.data$TIMESTAMP, tower_eo_sense.data$pred_GAM_NEE)

with(tower_eo_sense.data, boxplot(tower_eo_sense.data$NEE_control_GF_GAM~treatment, ylim =c (-40,40)
                          ))
#comparing NEE data to chamber filled data
summary(tower_eo_sense.data$NEE)
summary(tower_eo_sense.data $NEE_control_GF_GAM)


summary(tower_eo_sense.data$NEE[tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16")])
summary(tower_eo_sense.data $NEE_control_GF_GAM[tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16")])

```

#removing outliers
```{r}
#some  outliers. Removing any values greater or smaller than Max and min original NEE values recorded on the control side.

#from overall data removing any points greater than 22.936
tower_eo_sense.data$NEE_control_GF_GAM[ tower_eo_sense.data$NEE_control_GF_GAM > 22.936] <-NA


#from the data post compost application removing any data points greater than 15.07 and less than -34.211. The max and min values recorded by the tower during that time
tower_eo_sense.data$NEE_control_GF_GAM[ tower_eo_sense.data$NEE_control_GF_GAM > 15.007 & tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16")  ] <-NA

tower_eo_sense.data$NEE_control_GF_GAM[ tower_eo_sense.data$NEE_control_GF_GAM < -34.211 & tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16") ] <-NA


##########removing upper bound outliers#########


#from overall data removing any points greater than 22.936
tower_eo_sense.data$upperCI[ tower_eo_sense.data$upperCI > 22.936] <-NA


#from the data post compost application removing any data points greater than 15.07 and less than -34.211. The max and min values recorded by the tower during that time
tower_eo_sense.data$upperCI[ tower_eo_sense.data$upperCI > 15.007 & tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16")  ] <-NA

tower_eo_sense.data$upperCI[ tower_eo_sense.data$upperCI < -34.211 & tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16") ] <-NA


###############removing lower bound outliers############
#from overall data removing any points greater than 22.936
tower_eo_sense.data$lowerCI[ tower_eo_sense.data$lowerCI > 22.936] <-NA


#from the data post compost application removing any data points greater than 15.07 and less than -34.211. The max and min values recorded by the tower during that time
tower_eo_sense.data$lowerCI[ tower_eo_sense.data$lowerCI > 15.007 & tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16")  ] <-NA

tower_eo_sense.data$lowerCI[ tower_eo_sense.data$lowerCI < -34.211 & tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16") ] <-NA


#comparing orginal NEE data to GF with chambers again
summary(tower_eo_sense.data $NEE_control_GF_GAM)
summary(tower_eo_sense.data$NEE)

#comparing post compost application
summary(tower_eo_sense.data $NEE_control_GF_GAM[tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16")])
summary(tower_eo_sense.data$NEE[tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16")])


#plotting overall data
plot(tower_eo_sense.data$NEE_control_GF_GAM ,
     ylim=c (-60,20),
     col ="red")
par(new= TRUE)
plot(tower_eo_sense.data$NEE,
     ylim=c (-60,20),
     col ="blue")

#plotting data post compost application
plot(tower_eo_sense.data$TIMESTAMP[tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16")],tower_eo_sense.data$NEE_control_GF_GAM [tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16")],
     ylim=c (-60,20),
     ylab = "NEE",
     xlab ="2020-2021",
     main = "Control Side tower data (blue) and GF GAM Data (red)",
     col ="red")
par(new= TRUE)
plot(tower_eo_sense.data$TIMESTAMP[tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16")],tower_eo_sense.data$NEE[tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16")],
     ylim=c (-60,20),
     ylab = "",
     xlab = "",
     col ="blue")
```


```{r}
#plots
plot(tower_eo_sense.data$TIMESTAMP,
      tower_eo_sense.data$upperCI, lty = 'dashed', col = 'red',  ylim = c(-60,20))
lines(tower_eo_sense.data$TIMESTAMP,
      tower_eo_sense.data$lowerCI, lty = 'dashed', col = 'red',   ylim = c(-60,20))
lines(tower_eo_sense.data$TIMESTAMP,
     tower_eo_sense.data$NEE_control_GF_GAM,
     col="black",   ylim = c(-60,20))
 legend(x= "topleft",
         legend = c("95% CI","mean"),
           pch = 16,
         col = c( "red", "black"),
         bty = "n")
```

```{r}
#seeing which rows are duplicated
which(duplicated(tower_eo_sense.data$TIMESTAMP))

#removing duplicated rows
tower_eo_sense.data<-tower_eo_sense.data[!duplicated(tower_eo_sense.data$TIMESTAMP), ]

#checking that this worked

 which(duplicated(tower_eo_sense.data$TIMESTAMP))
 
 #removing any rows with NA in time.id column
 tower_eo_sense.data <- tower_eo_sense.data[ !(tower_eo_sense.data$time.id %in% c(NA)), ]
 
#removing any rows with NA in TIMESTAMP column 
  tower_eo_sense.data <- tower_eo_sense.data[ !(tower_eo_sense.data$TIMESTAMP %in% c(NA)), ]
 
 tower_eo_sense.data
 





```


##save predictions

```{r}
#save dataframe

write.csv(tower_eo_sense.data,
          paste(out.path,Sys.Date(),"_Boot_strap_Control_side_gap_filled_via_GAM.csv",sep=""),
          quote = T,
          row.names = F)
```
