---
title: "GAM_concord"
output: html_document
---
#https://noamross.github.io/gams-in-r-course/chapter1 
```


```

## R Markdown

```{r}

require(stringr)
require(mgcv)
library(lme4)

library(ggplot2)
library(cowplot)
library(tidyverse)
library(ggpubr)


require(zoo)
require(openair)

na.count<-function(x) sum(is.na(x))
na.mean<-function(x) ifelse(is.nan(mean(x,na.rm=T)),NA,mean(x,na.rm=T))

library(REddyProc)

library(car)
library(stringr)

library(tidyverse)
library(ggpubr)
library(rstatix)
library(broom)
library(psych)

library(lme4)
library(dplyr)




```



#Defining the data I/O directory
```{r}
## change root.path as needed
root.path<-"C:\\Users\\Tommy\\flux\\Data-exploring\\02_Concord\\"
#root.path<-"D:\\Housen\\Flux\\Data-exploring\\02_Concord_Eden\\"

GAM.path<-paste0(root.path,"14_GAM_ready_Data\\") # this is tower data for the GAM model lives

eosense.path<- paste0(root.path,"14_GAM_ready_Data\\")#this is were the data for the eosense data for the GAM model lives

GAM_test.path<-paste0(root.path, "14_GAM_ready_Data\\") #this is where the tower data control side post compost lives to test the model against. 


out.path<-paste0(root.path, "15_GAM_predict_data\\")
```

#reading in a specific file

```{r}
## use follows to specify the versions of the combined file
# file name of the combined_file
cdata.GAM_pre_compost<-paste0("2021-07-15_pre_compost_GAM_data.csv")



cdata.eo_sense <- paste("eo_sense_20210601.csv")

# cdata.GAM_test <- paste("2021-07-13_control_post_compost_GAM_data.csv")
 
```


#Tower data for the GAM model

```{r}
## read in full output file of gap filled data
GAM_pre_compost <-
  read.csv(
    paste0(GAM.path, cdata.GAM_pre_compost, sep = ""),
    header = T,
    na.strings = "NA",
    stringsAsFactors = F
  )
colnames(GAM_pre_compost) <-
  colnames(read.csv(
    paste(GAM.path, cdata.GAM_pre_compost, sep = ""),
    header = T,
    na.strings = "NA"
  ))

head(GAM_pre_compost)

tail(GAM_pre_compost)

```

#Read in eosense data for the GAm model

```{r}
## read in eo_sensee_data
eosense.data <-
  read.csv(
    paste0(eosense.path, cdata.eo_sense, sep = ""),
    header = T,
    na.strings = "NA",
    stringsAsFactors = F
  )
colnames(eosense.data) <-
  colnames(read.csv(
    paste(GAM.path, cdata.eo_sense, sep = ""),
    header = T,
    na.strings = "NA"
  ))

head(eosense.data)

tail(eosense.data)


```


#Post compost control side data to test GAM model against
```{r}

## read in Data to test the GAM model
# GAM_test.data <-
#   read.csv(
#     paste0(GAM_test.path, cdata.GAM_test, sep = ""),
#     header = T,
#     na.strings = "NA",
#     stringsAsFactors = F
#   )
# colnames(GAM_test.data) <-
#   colnames(read.csv(
#     paste(GAM.path, cdata.GAM_test, sep = ""),
#     header = T,
#     na.strings = "NA"
#   ))
# 
# head(GAM_test.data)
# 
# tail(GAM_test.data)

```

#Adding back POSIXT format timestamp to post compost control side data
```{r}

# GAM_test.data$TIMESTAMP <- strptime(paste(GAM_test.data$TIMESTAMP),
#                                  format = "%m/%d/%Y %H:%M",
#                                  tz = "Etc/GMT-8")
# 
# 
# GAM_test.data$TIMESTAMP[500:560]
# 
# head(GAM_test.data)
# 
# plot( GAM_test.data$TIMESTAMP, GAM_test.data$NEE)
```



#adding POSIXT format back to Gam_pre_compost_data
```{r}


GAM_pre_compost$TIMESTAMP <- strptime(paste(GAM_pre_compost$TIMESTAMP),
                                 format = "%m/%d/%Y %H:%M",
                                 tz = "Etc/GMT-8")


GAM_pre_compost$TIMESTAMP[500:560]

head(GAM_pre_compost)

plot( GAM_pre_compost$TIMESTAMP, GAM_pre_compost$NEE)
```

```{r}
GAM_pre_compost$time.id <- GAM_pre_compost$TIMESTAMP$year + 1900 +
  (GAM_pre_compost$TIMESTAMP$yday) / 366 +
  (GAM_pre_compost$TIMESTAMP$hour) / 366 / 24 +
  (GAM_pre_compost$TIMESTAMP$min) / 366 / 24 / 60

GAM_pre_compost$time.id[1:50]
plot(GAM_pre_compost$TIMESTAMP, GAM_pre_compost$time.id)
# which(duplicated(GAM_pre_compost$time.id))



# which(duplicated(GAM_pre_compost$TIMESTAMP))
# 
# 
# 
# which(duplicated(GAM_pre_compost$time.id))

# GAM_pre_compost %>% distinct(time.id, .keep_all = TRUE)
# 
# GAM_pre_compost[!duplicated(GAM_pre_compost$TIMESTAMP), ]

```



#creating timestamp for eosense data
```{r}

eosense.data$Year<-eosense.data$Year +2000


eosense.data


#combining month day year into a date column. 
eosense.data$Date<-paste(eosense.data$Month,eosense.data$Day, eosense.data$Year,sep="/")

head( eosense.data$Date, 50)

eosense.data

#creating a timestamp based on 
eosense.data$TIMESTAMP<-strptime(paste(eosense.data$Date,eosense.data$Time,sep=" "),
                          format="%m/%d/%Y %H:%M ",
                          tz = "Etc/GMT-8")


eosense.data

eosense.data$TIMESTAMP[1:50]

plot(eosense.data$TIMESTAMP, eosense.data$Flux)

```

```{r}
#creating time id for eosense data
eosense.data$time.id<-eosense.data$TIMESTAMP$year+1900+
  (eosense.data$TIMESTAMP$yday)/366+
  (eosense.data$TIMESTAMP$hour)/366/24+
  (eosense.data$TIMESTAMP$min)/366/24/60

eosense.data$time.id[1:50]
plot(eosense.data$TIMESTAMP,eosense.data$time.id)

which(duplicated(eosense.data$time.id))

eosense.data %>% distinct(time.id, .keep_all = TRUE)

head(eosense.data)
```


#creating full time stamp without gaps for for merging data
```{r}

# create a full timestamp, 30 mins
full.time<-data.frame(TIMESTAMP=
                        seq.POSIXt(min(min(GAM_pre_compost$TIMESTAMP),min(eosense.data$TIMESTAMP)),
                                   max(max(GAM_pre_compost$TIMESTAMP),max(eosense.data$TIMESTAMP)),
                                   units = "seconds", by = 1800),
                      stringsAsFactors=F)

full.time$TIMESTAMP<-strptime(full.time$TIMESTAMP,
                              format ="%Y-%m-%d %H:%M:%S",
                              tz = "Etc/GMT-8")

full.time$time.id <-full.time$TIMESTAMP$year+1900+
  (full.time$TIMESTAMP$yday)/366+
  (full.time$TIMESTAMP$hour)/366/24+
  (full.time$TIMESTAMP$min)/366/24/60 

print(paste("Starting timestamp:",full.time$TIMESTAMP[1]))
print(paste("Ending timestamp:",full.time$TIMESTAMP[nrow(full.time)]))

head(full.time)

which(duplicated(full.time$time.id))

```

#merging tower and eosense data
```{r}
tower_eo_sense.data<- merge.data.frame(full.time,
                         GAM_pre_compost[,-which(colnames(GAM_pre_compost)=="TIMESTAMP")],
                         by = "time.id",
                         all = TRUE,
                         sort = TRUE) 
#all=true what ever appears in each file is show in the file data file. sort tries to sort each data frame by merging. in this case probably doesnot matter. timestamp

tower_eo_sense.data<- merge.data.frame(tower_eo_sense.data,
                         eosense.data[,-which(colnames(eosense.data)=="TIMESTAMP")],
                         by = "time.id",
                         all = TRUE,
                         sort = TRUE) 

head(tower_eo_sense.data, 50)
tail(tower_eo_sense.data, 50)

tower_eo_sense.data
```









#plotting in blue NEE from Tower and red, flux from chamber
```{r}
plot(tower_eo_sense.data$TIMESTAMP, tower_eo_sense.data$Flux, 
     ylim = c(-20,20),
     col= "red")

par(new= TRUE)

plot(tower_eo_sense.data$TIMESTAMP, tower_eo_sense.data$NEE, 
     ylim = c(-20,20),
     col= "blue")



```


## Plots and linear regression for co2 chamber fluxes

```{r}

##for co2 chamber fluxes 
ggplot(data = tower_eo_sense.data, aes(x = Year, y = Flux)) +
  geom_point(color = "black") +
  theme_bw()

ggplot(data = tower_eo_sense.data, aes(x = Month, y = Flux)) +
  geom_point(color = "black") +
  theme_bw()



ggplot(data = tower_eo_sense.data, aes(x = Tsoil_0cm, y = Flux)) +
  geom_point(color = "black") +
  theme_bw()

ggplot(data = tower_eo_sense.data, aes(x = Tsoil_5cm, y = Flux)) +
  geom_point(color = "black") +
  theme_bw()

ggplot(data = tower_eo_sense.data, aes(x = Tsoil_10cm, y = Flux)) +
  geom_point(color = "black") +
  theme_bw()

ggplot(data = tower_eo_sense.data, aes(x = Tsoil_15cm, y = Flux)) +
  geom_point(color = "black") +
  theme_bw()

ggplot(data = tower_eo_sense.data, aes(x = Tsoil_30cm, y = Flux)) +
  geom_point(color = "black") +
  theme_bw()

ggplot(data = tower_eo_sense.data, aes(x =VWC_Control_GF, y = Flux)) +
  geom_point(color = "black") +
  theme_bw()

ggplot(data = tower_eo_sense.data, aes(x = Tair, y = Flux)) +
  geom_point(color = "black") +
  theme_bw()

ggplot(data = tower_eo_sense.data, aes(x = rH, y = Flux)) +
  geom_point(color = "black") +
  theme_bw()




ggplot(data = tower_eo_sense.data, aes(x = precip, y = Flux)) +
  geom_point(color = "black") +
  theme_bw()

ggplot(data = tower_eo_sense.data, aes(x = VPD, y = NEE)) +
  geom_point(color = "black") +
  theme_bw()

```






#gam for Tower NEE


```{r}

#colnames(tower_eo_sense.data)

gam_tower_NEE <- gam(NEE ~s(Flux,k=12) + s(VWC_Control_GF, precip, k=30) + s( Rg, Tair,VPD, k=30) ,data = tower_eo_sense.data, method = "REML")
 # gam_tower_NEE <- gam(NEE[(tower_eo_sense.data $treatment != "treatment_post_compost")&(tower_eo_sense.data $treatment != "exclude")] ~s(Flux[(tower_eo_sense.data $treatment != "treatment_post_compost")&(tower_eo_sense.data $treatment != "exclude")],k=4) + s(precip[(tower_eo_sense.data $treatment != "treatment_post_compost")&(tower_eo_sense.data $treatment != "exclude")],VWC_Control_GF[(tower_eo_sense.data $treatment != "treatment_post_compost")&(tower_eo_sense.data $treatment != "exclude")], k=8) + s(Rg[(tower_eo_sense.data $treatment != "treatment_post_compost")&(tower_eo_sense.data $treatment != "exclude")], k=8)+s(VPD[(tower_eo_sense.data $treatment != "treatment_post_compost")&(tower_eo_sense.data $treatment != "exclude")], k=8)   ,data = tower_eo_sense.data, method = "REML")




#plotting residuals
plot(gam_tower_NEE, residuals = TRUE)

plot(gam_tower_NEE, residuals = TRUE, pch = 1, cex = 1)


# Plot the weight effect
plot(gam_tower_NEE, select = 4, shade = TRUE, shade.col = "hotpink")

# Make another plot adding the intercept value and uncertainty
plot(gam_tower_NEE, select = 4, shade = TRUE, shade.col = "hotpink", 
     shift = coef(gam_tower_NEE)[1], seWithMean = TRUE)

#plotting concurvity
concurvity(gam_tower_NEE, full = TRUE)

concurvity(gam_tower_NEE, full = FALSE)




gam.check(gam_tower_NEE)
summary(gam_tower_NEE)
logLik(gam_tower_NEE)

AIC(gam_tower_NEE)

```


#Predicting NEE values with GAM
```{r}

#created weird outliers use GAM predict
pred<-predict.gam(gam_tower_NEE,tower_eo_sense.data,type="link",se.fit=TRUE,terms=NULL,
        exclude=NULL,block.size=NULL,newdata.guaranteed=FALSE,
        na.action=na.pass,unconditional=FALSE,iterms.type=NULL)

#V1 in output is the predicted value of your gam
#V2 is the associated standard error



plot(pred$fit)
plot(pred$se.fit)

#put list into a dataframe
GAM_NEE_predictions <- data.frame(matrix(unlist(pred), nrow=length(pred), byrow=TRUE))

#transpose so that the data is in columns not rows 
GAM_NEE_predictions<- as.data.frame(t(GAM_NEE_predictions))

#rename variables to something meaningful in the new data frame
GAM_NEE_predictions$pred_GAM_NEE=GAM_NEE_predictions$V1
GAM_NEE_predictions$pred_GAM_SE=GAM_NEE_predictions$V2

# or add to original data frame
tower_eo_sense.data$pred_GAM_NEE=GAM_NEE_predictions$V1
tower_eo_sense.data$pred_GAM_SE=GAM_NEE_predictions$V2



```
#slight variation to code above. produces same results
```{r}
# pred_1 <- predict.gam(gam_tower_NEE,tower_eo_sense.data)
# 
# 
# 
# pred_1_data_frame<- data.frame(matrix(unlist(pred_1), nrow=length(pred_1), byrow=TRUE))
# 
# plot(pred_1_data_frame$matrix.unlist.pred_1...nrow...length.pred_1...byrow...TRUE.)
# 
# tower_eo_sense.data$pred_GAM_NEE=GAM_NEE_predictions$v1

```


```{r}
#creating a new NEE column with the modeled control side data
tower_eo_sense.data $NEE_control_GF_GAM <- (tower_eo_sense.data$NEE * 1)


summary(tower_eo_sense.data $NEE_control_GF_GAM)



#making any NA values measured by the tower the chamber gapfilled values.
tower_eo_sense.data$NEE_control_GF_GAM[is.na(tower_eo_sense.data$NEE_control_GF_GAM)] <-
  tower_eo_sense.data$pred_GAM_NEE[is.na(tower_eo_sense.data$NEE_control_GF_GAM)]





#plotting
plot(tower_eo_sense.data$TIMESTAMP,tower_eo_sense.data$NEE_control_GF_GAM,
     ylim = c(-20,50),
     col= 'red')

par(new=TRUE)
plot(tower_eo_sense.data$TIMESTAMP, tower_eo_sense.data$NEE,
     ylim = c(-20,50))

plot(tower_eo_sense.data$TIMESTAMP, tower_eo_sense.data$pred_GAM_NEE)

with(tower_eo_sense.data, boxplot(tower_eo_sense.data$NEE_control_GF_GAM~treatment, ylim =c (-40,40)
                          ))
#comparing NEE data to chamber filled data
summary(tower_eo_sense.data$NEE)
summary(tower_eo_sense.data $NEE_control_GF_GAM)


summary(tower_eo_sense.data$NEE[tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16")])
summary(tower_eo_sense.data $NEE_control_GF_GAM[tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16")])


#some  outliers. Removing any values greater or smaller than Max and min original NEE values recorded on the control side.

#from overall data removing any points greater than 22.936
tower_eo_sense.data$NEE_control_GF_GAM[ tower_eo_sense.data$NEE_control_GF_GAM > 22.936] <-NA


#from the data post compost application removing any data points greater than 15.07 and less than -34.211. The max and min values recorded by the tower during that time
tower_eo_sense.data$NEE_control_GF_GAM[ tower_eo_sense.data$NEE_control_GF_GAM > 15.007 & tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16")  ] <-NA

tower_eo_sense.data$NEE_control_GF_GAM[ tower_eo_sense.data$NEE_control_GF_GAM < -34.211 & tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16") ] <-NA

#comparing orginal NEE data to GF with chambers again
summary(tower_eo_sense.data $NEE_control_GF_GAM)
summary(tower_eo_sense.data$NEE)

#comparing post compost application
summary(tower_eo_sense.data $NEE_control_GF_GAM[tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16")])
summary(tower_eo_sense.data$NEE[tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16")])


#plotting overall data
plot(tower_eo_sense.data$NEE_control_GF_GAM ,
     ylim=c (-60,20),
     col ="red")
par(new= TRUE)
plot(tower_eo_sense.data$NEE,
     ylim=c (-60,20),
     col ="blue")

#plotting data post compost application
plot(tower_eo_sense.data$TIMESTAMP[tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16")],tower_eo_sense.data$NEE_control_GF_GAM [tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16")],
     ylim=c (-60,20),
     ylab = "NEE",
     xlab ="2020-2021",
     main = "Control Side tower data (blue) and GF GAM Data (red)",
     col ="red")
par(new= TRUE)
plot(tower_eo_sense.data$TIMESTAMP[tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16")],tower_eo_sense.data$NEE[tower_eo_sense.data $ TIMESTAMP >as.POSIXct("2020-10-16")],
     ylim=c (-60,20),
     ylab = "",
     xlab = "",
     col ="blue")

```

#Final check for duplicate rows. Some remove them
```{r}


#seeing which rows are duplicated
which(duplicated(tower_eo_sense.data$TIMESTAMP))

#removing duplicated rows
tower_eo_sense.data<-tower_eo_sense.data[!duplicated(tower_eo_sense.data$TIMESTAMP), ]

#checking that this worked

 which(duplicated(tower_eo_sense.data$TIMESTAMP))
 
 #removing any rows with NA in time.id column
 tower_eo_sense.data <- tower_eo_sense.data[ !(tower_eo_sense.data$time.id %in% c(NA)), ]
 
#removing any rows with NA in TIMESTAMP column 
  tower_eo_sense.data <- tower_eo_sense.data[ !(tower_eo_sense.data$TIMESTAMP %in% c(NA)), ]
 
 tower_eo_sense.data
 



#also need to remove rows with duplicate time stamps


```



#wrting a CSV of the data with the gap filled values
```{r}
write.csv(tower_eo_sense.data,
          paste(out.path,Sys.Date(),"_Control_side_gap_filled_via_GAM.csv",sep=""),
          quote = T,
          row.names = F)
```





























