---
title: "GAM_other_sites"
output: html_document
---
#https://noamross.github.io/gams-in-r-course/chapter1 
```{r, include=FALSE}

install.packages("lme4")

install.packages("ggplot2")

install.packages("cowplot")


```

## R Markdown

```{r}

require(mgcv)
library(lme4)
library(ggplot2)
library(cowplot)
library(tidyverse)
library(ggpubr)


root.path<-"D:\\SanDiskSecureAccess\\EdenLanding\\EL_chamber_data\\GAM\\other_sites\\"

cdata.file1<-paste0("Weston_et_al_2014_4_GAM_2")


wes<-read.csv(paste(root.path,cdata.file1,".csv",sep=""),
                header=F,
                skip=1,
                na.strings="NA",
                stringsAsFactors=F)


colnames(wes)<-colnames(read.csv(paste(root.path,cdata.file1,".csv",sep=""),                                                                 na.strings="NaN"))



```

## Plots and linear regression for co2 chamber fluxes

```{r}

##for co2 chamber fluxes 
ggplot(data = wes, aes(x = sample_year, y = co2_flux)) +
  geom_point(color = "black") +
  theme_bw()

ggplot(data = wes, aes(x = sample_month, y = co2_flux)) +
  geom_point(color = "black") +
  theme_bw()

ggplot(data = wes, aes(x = sample_day, y = co2_flux)) +
  geom_point(color = "black") +
  theme_bw()

ggplot(data = wes, aes(x = conductivity, y = co2_flux)) +
  geom_point(color = "black") +
  theme_bw()


ggplot(data = wes, aes(x =biomass_above, y = co2_flux)) +
  geom_point(color = "black") +
  theme_bw()

ggplot(data = wes, aes(x = ppt, y = co2_flux)) +
  geom_point(color = "black") +
  theme_bw()

ggplot(data = wes, aes(x = tmean..degrees.C., y = co2_flux)) +
  geom_point(color = "black") +
  theme_bw()


ggplot(data = wes, aes(x = tmax..degrees.C., y = co2_flux)) +
  geom_point(color = "black") +
  theme_bw()


ggplot(data = wes, aes(x = vpdmax..hPa., y = co2_flux)) +
  geom_point(color = "black") +
  theme_bw()

### for CO2, ppt and biomass had the strongest relationships 
linear_model<- lm(co2_flux~ sample_month, data = wes)
summary(linear_model)
plot(linear_model)

linear_model<- lm(co2_flux~ sample_year, data = wes)
summary(linear_model)
plot(linear_model)

linear_model<- lm(co2_flux~ sample_day, data = wes)
summary(linear_model)
plot(linear_model)

linear_model<- lm(co2_flux~ conductivity, data = wes)
summary(linear_model)
plot(linear_model)

linear_model<- lm(co2_flux~ biomass_above, data = wes)
summary(linear_model)
plot(linear_model)

linear_model<- lm(co2_flux~ ppt, data = wes)
summary(linear_model)
plot(linear_model)

linear_model<- lm(co2_flux~ tmean..degrees.C., data = wes)
summary(linear_model)
plot(linear_model)

linear_model<- lm(co2_flux~ tmax..degrees.C., data = wes)
summary(linear_model)
plot(linear_model)

linear_model<- lm(co2_flux~ vpdmax..hPa., data = wes)
summary(linear_model)
plot(linear_model)


ch4_flux
co2_flux

sample_year
sample_month
sample_day
chamber_id

conductivity
biomass_above
ppt..m.
tmean..degrees.C.
tmax..degrees.C.
vpdmax..hPa.

wes$ppt=wes$ppt..mm.



```


##plots and linear regressions for ch4 fluxes 


```{r}

ggplot(data = wes, aes(x = sample_year, y = ch4_flux)) +
  geom_point(color = "black") +
  theme_bw()

ggplot(data = wes, aes(x = sample_month, y = ch4_flux )) +
  geom_point(color = "black") +
  theme_bw()

ggplot(data = wes, aes(x = sample_day, y = ch4_flux)) +
  geom_point(color = "black") +
  theme_bw()

ggplot(data = wes, aes(x = conductivity, y = ch4_flux)) +
  geom_point(color = "black") +
  theme_bw()


ggplot(data = wes, aes(x =biomass_above, y = ch4_flux)) +
  geom_point(color = "black") +
  theme_bw()

ggplot(data = wes, aes(x = ppt, y = ch4_flux)) +
  geom_point(color = "black") +
  theme_bw()

ggplot(data = wes, aes(x = tmean..degrees.C., y = ch4_flux)) +
  geom_point(color = "black") +
  theme_bw()


ggplot(data = wes, aes(x = tmax..degrees.C., y = ch4_flux)) +
  geom_point(color = "black") +
  theme_bw()


ggplot(data = wes, aes(x = vpdmax..hPa., y = ch4_flux)) +
  geom_point(color = "black") +
  theme_bw()

### for ch4 tmean, tmax, and vpd had strongest relationships 
linear_model<- lm(ch4_flux~ sample_month, data = wes)
summary(linear_model)
plot(linear_model)

linear_model<- lm(ch4_flux~ sample_year, data = wes)
summary(linear_model)
plot(linear_model)

linear_model<- lm(ch4_flux~ sample_day, data = wes)
summary(linear_model)
plot(linear_model)

linear_model<- lm(ch4_flux~ conductivity, data = wes)
summary(linear_model)
plot(linear_model)

linear_model<- lm(ch4_flux~ biomass_above, data = wes)
summary(linear_model)
plot(linear_model)

linear_model<- lm(ch4_flux~ ppt, data = wes)
summary(linear_model)
plot(linear_model)

linear_model<- lm(ch4_flux~ tmean..degrees.C., data = wes)
summary(linear_model)
plot(linear_model)

linear_model<- lm(ch4_flux~ tmax..degrees.C., data = wes)
summary(linear_model)
plot(linear_model)

linear_model<- lm(ch4_flux~ vpdmax..hPa., data = wes)
summary(linear_model)
plot(linear_model)



plot(wes$p.biomass)



```

# fill variables with gaps from linear relationships 

```{r}
#predict conductivity from ppt  *** this is precipitation 
linear_model<- lm(conductivity~ ppt, data = wes)
summary(linear_model)
plot(linear_model)

wes$p.conductivity <- predict.lm(linear_model, wes)

##predict biomass from TA
linear_model<- lm(biomass~ tmean+sample_month, data = wes)
summary(linear_model)
plot(linear_model)
##predict biomass from something else? 
#ppt 0.01 *** 
#tmean 0.27 ***
#tmax 0.239 ***
#vpd 0.2 
#sample day 0.057 ***
#sample month 10.3  ***
#sample year 0.018  *** 
#sample year and sample month  
# sample year, month and day 
linear_model<- lm(biomass~ tmean, data = wes)
summary(linear_model)
plot(linear_model)

wes$p.biomass<- predict.lm(linear_model, wes)

##predict cond from something else? 
#ppt 7.6% *** 
#tmean 2.7% * 
#tmax 3.6% ** 
#vpd 0.07% 
#sample day 8.4% ***
#sample month 55.5% 2e-16 ***
#sample year 52.5%  2e-16 *** 
#sample year and sample month 66.57% *** 
# sample year, month and day 70% *** 
linear_model<- lm(cond~ sample_day+sample_month+sample_year , data = wes)
summary(linear_model)

#plot(linear_model)
wes$p.cond<- predict.lm(linear_model, wes)
plot(wes$p.cond)

#remove ch4 outliers - did in matlab 


```

#gam for ch4 chamber fluxes
ch4_flux
co2_flux

sample_year
sample_month
sample_day
chamber_id

conductivity
biomass_above
ppt..m.
tmean..degrees.C.
tmax..degrees.C.
vpdmax..hPa.

wes$ppt=wes$ppt..mm.
wes$tmean=wes$tmean..degrees.C.
wes$tmax=wes$tmax..degrees.C.
wes$vpd=wes$vpdmax..hPa.

```{r}
wes$ppt=wes$ppt

gam_ch4 <- gam(ch4_flux~s(tmean,k=5)+s(vpd,k=5)+s(sample_day,k=5)+s(cond,k=5)+s(biomass,k=5)+s(collar_aligned_co2_1,k=5),data = wes, method = "REML")


plot(gam_ch4)

gam.check(gam_ch4)
summary(gam_ch4)
logLik(gam_ch4)

```
## gam for co2 chamber fluxes (without light treatment)


ch4_flux
co2_flux

sample_year
sample_month
sample_day
chamber_id

conductivity
biomass_above
ppt..m.
tmean..degrees.C.
tmax..degrees.C.
vpdmax..hPa.

wes$ppt=wes$ppt..mm.
wes$tmean=wes$tmean..degrees.C.
wes$tmax=wes$tmax..degrees.C.
wes$vpd=wes$vpdmax..hPa.
```{r}

gam_co2_0 <- gam(collar_aligned_co2_0~s(ppt,k=5)+s(biomass,k=5)+s(sample_day,k=5)+s(vpd,k=5)+s(ch4_flux,k=5)+s(p.cond,k=3),data = wes, method = "REML") 

gam.check(gam_co2_0)

summary(gam_co2_0)
logLik(gam_co2_0)

```
#regression for co2 
```{r}
##predict biomass from TA
linear_model<- lm(biomass~ tmean, data = wes)
summary(linear_model)
plot(linear_model)

wes$p.biomass<- predict.lm(linear_model, wes)
```




## gam for co2 chamber fluxes (with light treatment)


ch4_flux
co2_flux

sample_year
sample_month
sample_day
chamber_id

conductivity
biomass_above
ppt..m.
tmean..degrees.C.
tmax..degrees.C.
vpdmax..hPa.

wes$ppt=wes$ppt..mm.
wes$tmean=wes$tmean..degrees.C.
wes$tmax=wes$tmax..degrees.C.
wes$vpd=wes$vpdmax..hPa.

```{r}
#gam_co2_1<-gam(co2_flux_1~s(ppt,k=5)+s(biomass,k=5)+s(sample_day,k=5)+s(vpd,k=5)+s(tmean,k=5)+s(sample_year,k=3)+s(sample_month,k=5)+s(ch4_flux,k=5),data = wes, method = "REML") 

gam_co2_1<-gam(collar_aligned_co2_1~s(ppt,k=5)+s(biomass,k=5)+s(sample_day,k=5)+s(vpd,k=5)+s(tmean,k=5)+s(sample_year,k=3)+s(sample_month,k=5)+s(ch4_flux,k=5),data = wes, method = "REML") 

#plot(gam_co2_1, residuals = TRUE, pch = 1,shade=TRUE, seWithMean = TRUE,page=1)
gam.check(gam_co2_1)

summary(gam_co2_1)
logLik(gam_co2_1)
```
##load new data for predictions 

```{r}

root.path<-"D:\\SanDiskSecureAccess\\EdenLanding\\EL_chamber_data\\GAM\\other_sites\\new_data\\"

cdata.file2<-paste0("wes_co2_1")


wes_co2_1<-read.csv(paste(root.path,cdata.file2,".csv",sep=""),
                header=F,
                skip=1,
                na.strings="NA",
                stringsAsFactors=F)


colnames(wes_co2_1)<-colnames(read.csv(paste(root.path,cdata.file2,".csv",sep=""),                                                                 na.strings="NaN"))


```


#making predictions for co2 with light 

```{r}

gam_co2_1 <- gam(co2_flux_1~s(ppt,k=5)+s(biomass,k=5)+s(sample_day,k=5)+s(vpd,k=5)+s(tmean,k=5)+s(sample_year,k=3)+s(sample_month,k=5),data = wes, method = "REML") 

wes_co2_1$biomass=wes_co2_1$p.biomass

pred<-predict(gam_co2_1,wes_co2_1,type="link",se.fit=TRUE,terms=NULL,
        exclude=NULL,block.size=NULL,newdata.guaranteed=FALSE,
        na.action=na.pass,unconditional=FALSE,iterms.type=NULL)


plot(pred$fit)
plot(pred$se.fit)


wes_co2_1_predictions <- data.frame(matrix(unlist(pred), nrow=length(pred), byrow=TRUE))

#wes_co2_1_predictions <-t(wes_co2_1_predictions) 

#plot(wes_co2_1_predictions$V1)
```

## making predictions for co2 without light 

```{r}

wes_co2_1$biomass=wes_co2_1$p.biomass

pred<-predict(gam_co2_0,wes_co2_1,type="link",se.fit=TRUE,terms=NULL,
        exclude=NULL,block.size=NULL,newdata.guaranteed=FALSE,
        na.action=na.pass,unconditional=FALSE,iterms.type=NULL)


plot(pred$fit)
plot(pred$se.fit)


wes_co2_0_predictions <- data.frame(matrix(unlist(pred), nrow=length(pred), byrow=TRUE))

```

#making predicitons for ch4 
```{r}
gam_ch4 <- gam(ch4_flux~s(tmean,k=5)+s(vpd,k=5)+s(sample_day,k=5)+s(cond,k=5)+s(biomass)+s(ppt,k=3),data = wes, method = "REML") 


wes_co2_1$biomass=wes_co2_1$p.biomass
wes_co2_1$cond=wes$p.cond

pred<-predict(gam_ch4,wes_co2_1,type="link",se.fit=TRUE,terms=NULL,
        exclude=NULL,block.size=NULL,newdata.guaranteed=FALSE,
        na.action=na.pass,unconditional=FALSE,iterms.type=NULL)


plot(pred$fit)
plot(pred$se.fit)


wes_ch4_predictions <- data.frame(matrix(unlist(pred), nrow=length(pred), byrow=TRUE))


```

#save data 

```{r}
##updated original data with linear relationships

out.dir<-"D:\\SanDiskSecureAccess\\EdenLanding\\EL_chamber_data\\GAM\\other_sites\\"

write.csv(wes,
          paste(out.dir,"Weston_et_al_2014_4_GAM_2.csv",sep=""),
          quote = T,
          row.names = F)


##newly predicted data, rename the output each time 

out.dir<-"D:\\SanDiskSecureAccess\\EdenLanding\\EL_chamber_data\\GAM\\other_sites\\predicted\\"

write.csv(wes_ch4_predictions,
          paste(out.dir,"ch4_predicted_data_model_29.csv",sep=""),
          quote = T,
          row.names = F)

```
































