---
title: "R Notebook"
output: html_notebook
---

#Read_proc to GF missing data after GF with GAM. also filters based on U star

```{r}

library(REddyProc)
library(dplyr)
library(bigleaf)
```


## change to local dir
```{r}

root.ditr<-"C:\\Users\\Tommy\\flux\\Data-exploring\\02_Concord\\"
data.dir<-paste0(root.ditr,"04_Reddy_Proc_data\\") ##  2021-09-14_Boot_strap_Control_side_gap_filled_via_GAM.txt locate
out.dir<-paste0(root.ditr,"18_treat_side_read_proc_gf\\") ## store all output figures/files

flux.var <- c('NEE', 'h2o_flux', 'LE', 'H')
met.var <- c('Rg', 'Tair', 'Tsoil', 'VPD', 'Ustar', 'rH')


# ## change root.path as needed
# root.path<-"C:\\Users\\Tommy\\flux\\Data-exploring\\02_Concord\\"
# #root.path<-"D:\\Housen\\Flux\\Data-exploring\\02_Concord\\"
# 
# combined.path<-paste0(root.path,"03_combined_data\\") ## this is where the combined data lives
# 
# 
# path.in_CIMIS<-paste0(root.path,"05_CIMIS_Data\\")
#  ver<-"cimis_data" 
# 
# # hc: Use this for storing combined file
# path.out<-paste(root.path,"06_CIMIS_gap_fill\\",sep="")


```

# REddyProc typical workflow
```{r}
####################################################################################

#+++ Load data with 1 header and 1 unit row from (tab-delimited) text file
fileName <- "2021-09-14_Boot_strap_Treatment_side_gap_filled_via_GAM.txt"
EddyData <- fLoadTXTIntoDataframe(fileName,Dir = data.dir)

head(EddyData)

tail(EddyData)


```


```{r}
#+++ Replace long runs (repeated constants) of flux variables by NA
EddyData <- filterLongRuns(EddyData, flux.var)
```


#gettting in timestamp format
```{r}
EddyData$TIMESTAMP<-strptime(paste(EddyData$TIMESTAMP,EddyData$Hour,sep=" "),
                          format="%m/%d/%Y %H:%M", 
                          tz = "Etc/GMT-8")

EddyDataWithPosix <-EddyData

EddyDataWithPosix$Hour<-NULL

head(EddyDataWithPosix)


head(EddyDataWithPosix$TIMESTAMP)
tail(EddyDataWithPosix$TIMESTAMP)


EddyDataWithPosix
```

#calculating VPD
```{r}

EddyDataWithPosix$VPD<-rH.to.VPD(EddyDataWithPosix$rH/100, EddyDataWithPosix$Tair, Esat.formula = c("Sonntag_1990", "Alduchov_1996",
  "Allen_1998"), constants = bigleaf.constants())

EddyDataWithPosix

```

#+++ Initalize R5 reference class sEddyProc for post-processing of eddy data
#+++ with the variables needed for post-processing later

```{r}

EProc <- sEddyProc$new('Concord',
                       Data = EddyDataWithPosix,
                       ColNames = c(flux.var,met.var),
                       ColPOSIXTime = 'TIMESTAMP',
                       LatDeg = 37.93799591, LongDeg = -121.9761047, TimeZoneHour = -7)

# Lat/long and time zone to compute sunrise and sunset, used to differentiate daytime/nighttime.
EProc$sSetLocationInfo(LatDeg = 37.93799591, LongDeg = -121.9761047, TimeZoneHour = -7)
```

#plotting flux variables before gapfilling
```{r}
## plot flux variables before gap-filling 
for(i in 1:length(flux.var)){

  EProc$sPlotDiurnalCycle(flux.var[i],
                          Dir = out.dir)
  EProc$sPlotHHFluxes(flux.var[i],
                      Dir = out.dir)
  
}

```

```{r}

## plot met variables before gap-filling 
for(i in 1:length(met.var)){

  EProc$sPlotDiurnalCycle(met.var[i],
                          Dir = out.dir)
  EProc$sPlotHHFluxes(met.var[i],
                      Dir = out.dir)
  
}

```


###### NEE processing
#### Ustar threshold determination; moving-point-transition (MP) 
#    described originally by Reichstein et al.2005 and Papale et al.2006
#    include bootstrapping to get a distribution of possible ustar thresholds
```{r}
EProc$sEstimateUstarScenarios(
    nSample = 100L, probs = c(0.05, 0.5, 0.95))## 5th, 50th, 95th precentiles of ustar thresholds


```

# inspect the thresholds to be used by default
```{r}
# inspect the thresholds to be used by default
EProc$sGetEstimatedUstarThresholdDistribution()
EProc$sGetUstarScenarios()
```

#Latent and sensible heat
```{r}
#################################################################################################
###### LE and H processing
#### Gap fill variable with specified variables and limits (change as needed)
#    Marginal distribution sampling method by Reichstein et al.2005
#    It loops through gaps, and fill them iteratively by diff environmental condition, window size 
EProc$sMDSGapFill(Var = 'LE',
                  V1 = 'Rg', T1 = 30,   ## 'Rg' within +/-30 W m-2
                  V2 = 'VPD', T2 = 0.5,   ## 'VPD' within +/-0.5 kPa)
                  FillAll = TRUE)   

EProc$sMDSGapFill(Var = 'H',
                  V1 = 'Rg', T1 = 30,   ## 'Rg' within +/-30 W m-2
                  V2 = 'Tair', T2 = 2,  ## 'Tair' within +/-2 degC 
                  FillAll = TRUE)  










```
#plotting sensible and latent heat
```{r}


# plot flux variables after gap-filling
for(i in 3:length(flux.var)){

  EProc$sPlotDiurnalCycle(paste0(flux.var[i],"_f"),
                          Dir = out.dir)
  EProc$sPlotHHFluxes(paste0(flux.var[i],"_f"),
                      Dir = out.dir)

}

```

```{r}
#### Gap fill variable with specified variables and limits (change as needed)
#    Marginal distribution sampling method by Reichstein et al.2005
#    It loops through gaps, and fill them iteratively by diff environmental condition, window size 
EProc$sMDSGapFillUStarScens('NEE',
                            V1 = 'Rg', T1 = 30, ## 'Rg' within +/-30 W m-2
                            V2 = 'Tair', T2 = 2,  ## 'Tair' within +/-2 degC
                            V3 = 'VPD', T3 = 0.5,   ## 'VPD' within +/-0.5 kPa
                            FillAll = TRUE)

```

#plotting NEE after gapfilling
```{r}
# get a list of gap-filled NEE, based on diff ustar thresholds
flux.gf.var <- grep("NEE_.*_f$",names(EProc$sExportResults()), value = TRUE)

for(i in 1:length(flux.gf.var)){
  
  EProc$sPlotDiurnalCycle(flux.gf.var[i],
                          Dir = out.dir)
  EProc$sPlotHHFluxes(flux.gf.var[i],
                      Dir = out.dir)
  
}

```

#h20flux gap filling
```{r}
#### Gap fill variable with specified variables and limits (change as needed)
#    Marginal distribution sampling method by Reichstein et al.2005
#    It loops through gaps, and fill them iteratively by diff environmental condition, window size 
EProc$sMDSGapFillUStarScens('h2o_flux',
                            V1 = 'Rg', T1 = 30, ## 'Rg' within +/-30 W m-2
                            V2 = 'Tair', T2 = 2,  ## 'Tair' within +/-2 degC
                            V3 = 'VPD', T3 = 0.5,   ## 'VPD' within +/-0.5 kPa
                            FillAll = TRUE)
```

#plotting h20_flux
```{r}
# get a list of gap-filled h2o_flux, based on diff ustar thresholds
flux.gf.var <- grep("h2o_flux_.*_f$",names(EProc$sExportResults()), value = TRUE)

for(i in 1:length(flux.gf.var)){
  
  EProc$sPlotDiurnalCycle(flux.gf.var[i],
                          Dir = out.dir)
  EProc$sPlotHHFluxes(flux.gf.var[i],
                      Dir = out.dir)
  
}
```






#For each of the different u∗ threshold estimates a separate set of output columns of filled NEE and its uncertainty is generated, distinguished by the suffixes given with uStarSuffixes. "_f" denotes the filled value and "_fsd" the estimated standard deviation of its uncertainty.
```{r}
grep("NEE_.*_f$",names(EProc$sExportResults()), value = TRUE)
grep("NEE_.*_fsd$",names(EProc$sExportResults()), value = TRUE)
```

#Sensible Heat
```{r}
grep("H_.*_f$",names(EProc$sExportResults()), value = TRUE)
grep("H_.*_fsd$",names(EProc$sExportResults()), value = TRUE)
```

#Latent Heat

```{r}
grep("LE_.*_f$",names(EProc$sExportResults()), value = TRUE)
grep("LE_.*_fsd$",names(EProc$sExportResults()), value = TRUE)
```

##################################################################################################
######  Partitioning NEE into GPP and Reco
####    Two approaches: 1) nighttime-based (Reichstein et al.2005)
#                       2) daytime-based (Lasslop et al. 2010)


```{r}
# while these variables don't needed gap-filling, the following partition functions need qc flags for these met variables 
EProc$sMDSGapFill('Tair', FillAll = FALSE,  minNWarnRunLength = NA)   
EProc$sMDSGapFill('Rg', FillAll = FALSE, minNWarnRunLength = NA)
EProc$sMDSGapFill('VPD', FillAll = FALSE,  minNWarnRunLength = NA) 
```

```{r}
## Nighttime-based approach, partition all NEEs (e.g., NEE_ustar,NEE_U50,...) to corresponding GPP/RECO 
EProc$sMRFluxPartitionUStarScens(TempVar = 'Tair') # specify which temperature to use for building respiration model

```
#Nighttime 
```{r}
# get a list of Reco and GPP_f by the respective ustar thresholds

grep("GPP.*_f$|Reco",names(EProc$sExportResults()), value = TRUE)

gppreco.var.nt <- grep("GPP.*_f$|Reco.*",names(EProc$sExportResults()), value = TRUE)
#gppreco.var.nt <- gppreco.var.nt[-which(grepl("_SD",gppreco.var.nt))]

for(i in 1:length(gppreco.var.nt)){
  
  EProc$sPlotDiurnalCycle(gppreco.var.nt[i],
                          Dir = out.dir)
  EProc$sPlotHHFluxes(gppreco.var.nt[i],
                      Dir = out.dir)
  
}
```

```{r}
## Daytime-based approach, partition all NEEs (e.g., NEE_ustar,NEE_U50,...) to corresponding GPP/RECO 
#   two versions present: 1) sGLFluxPartitionUStarScens, based on original Lasslop 2010
#                         2) sTKFluxPartitionUStarScens, based on a modified version in Keenan 2019
#   note: this method takes long time & breaks sometimes, the argument 'uStarScenKeep' specify which 
#         ustar version should run to save time

#EProc$sGLFluxPartitionUStarScens(uStarScenKeep = "U50")
# EProc$sTKFluxPartitionUStarScens(uStarScenKeep = "U50")
# 
# # get a list of Reco and GPP_f by the respective ustar thresholds
# gppreco.var.dt <- grep("GPP_DT|Reco_DT",names(EProc$sExportResults()), value = TRUE)
# gppreco.var.dt <- gppreco.var.dt[-which(grepl("_SD",gppreco.var.dt))]
# 
# for(i in 1:length(gppreco.var.dt)){
#   
#   EProc$sPlotDiurnalCycle(gppreco.var.dt[i],
#                           Dir = out.dir)
#   EProc$sPlotHHFluxes(gppreco.var.dt[i],
#                       Dir = out.dir)
#   
# }

```
#Estimating the uncertainty of aggregated results
#The results of the different u∗ threshold scenarios can be used for estimating the uncertainty due to not knowing the threshold.

#First, the mean of the GPP across all the year is computed for each u∗-scenario and converted from μmolCO2m−2s−1 to gCm−2yr−1.


```{r}
FilledEddyData <- EProc$sExportResults()
uStarSuffixes <- colnames(EProc$sGetUstarScenarios())[-1]
#suffix <- uStarSuffixes[2]
GPPAggCO2 <- sapply( uStarSuffixes, function(suffix) {
    GPPHalfHour <- FilledEddyData[[paste0("GPP_",suffix,"_f")]]
    mean(GPPHalfHour, na.rm = TRUE)
})
molarMass <- 12.011
GPPAgg <- GPPAggCO2 * 1e-6 * molarMass * 3600*24*365.25
print(GPPAgg)


```

#The difference between those aggregated values is a first estimate of uncertainty range in GPP due to uncertainty of the u∗ threshold.
```{r}
(max(GPPAgg) - min(GPPAgg)) / median(GPPAgg) 
```


#For a better but more time consuming uncertainty estimate, specify a larger sample of u∗ threshold values, for each repeat the post-processing, and compute statistics from the larger sample of resulting GPP columns. This can be achieved by specifying a larger sequence of quantiles when calling sEstimateUstarScenarios in place of the command shown above.

```{r}
# EProc$sEstimateUstarScenarios( 
#   nSample = 200, probs = seq(0.025,0.975,length.out = 39) )
```

#exporting the data
```{r}
###############################################################################################################
# Storing the results in a csv-file
# The results still reside inside the sEddyProc class. We first export them to an R Data.frame, append the
# columns to the original input data, and write this data.frame to text file in a temporary directory.

FilledEddyData <- EProc$sExportResults()
CombinedData <- cbind(EddyData, FilledEddyData)

fWriteDataframeToFile(CombinedData,
                      'Concord_2019-2020.txt',
                      Dir = out.dir)

write.csv(CombinedData,
          paste(out.dir,Sys.Date(),"_gap_fill_treat_combo_Concord.csv",sep=""),
          quote = T,
          row.names = F)

```


