---
title: "Analyzing treatment data gapfilled  with readyproc and control side data gap filled primarily with chamber measurements and a little ready proc (161 N/As)"
output:
  html_document:
    df_print: paged
---



```{r}
rm(list=ls())

require(stringr)
require(zoo)
require(openair)

na.count<-function(x) sum(is.na(x))
na.mean<-function(x) ifelse(is.nan(mean(x,na.rm=T)),NA,mean(x,na.rm=T))

library(REddyProc)

library(car)
library(stringr)

library(tidyverse)
library(ggpubr)
library(rstatix)
library(broom)
library(psych)

library(lme4)
library(dplyr)
```

#Defining the data I/O directory
#2021-09-13_master_eddy_met_concord_postfiltering
```{r}
## change root.path as needed
root.path<-"C:\\Users\\Tommy\\flux\\Data-exploring\\02_Concord\\"
#root.path<-"D:\\Housen\\Flux\\Data-exploring\\02_Concord_Eden\\"

treat_gap_fill.path<-paste0(root.path,"17_Control_treat_full_GF\\") ## this is where the gapfilled data lives


control_gap_fill.path <- paste0(root.path,"17_Control_treat_full_GF\\") ## this is where the control gap filled data lives



control_and_treat_gap_fill.path<-paste0(root.path,"17_Control_treat_full_GF\\") #where the combined treatment and control gapfilled file lives. 


post_filter.path<-paste0(root.path,"17_Control_treat_full_GF\\") #where the postfiltered VWC dataamong everythin for both live. 




out.path<-paste0(root.path, "10_figures_etc\\")
```

#reading in a specific file

```{r}
## use follows to specify the versions of the combined file
# file name of the combined_file
postfilter.file_gap_fill_treat<-paste0("Treatment-2020-2021_growing_season.csv")



postfilter.file_gap_fill_control <- paste("Control-2020-2021_growing_season.csv")


postfilter.file_gap_fill_control_and_treat <- paste("Treat_and _Control-2020-2021_growing_season.csv")

postfilter.file_post_filter <-paste("2021-09-13_master_eddy_met_concord_postfiltering.csv")
 
```


# Read in gap filled fulloutput files
# parse variable names and define N/As

```{r}
## read in full output file of treatment gap filled data
treat_gap_filled <-
  read.csv(
    paste0(treat_gap_fill.path, postfilter.file_gap_fill_treat, sep = ""),
    header = T,
    na.strings = "NA",
    stringsAsFactors = F
  )
colnames(treat_gap_filled) <-
  colnames(read.csv(
    paste(treat_gap_fill.path, postfilter.file_gap_fill_treat, sep = ""),
    header = T,
    na.strings = "NA"
  ))

head(treat_gap_filled)

tail(treat_gap_filled)

```


```{r}

## read in full output file of control gap filled data
control_gap_filled <-
  read.csv(
    paste0(control_gap_fill.path, postfilter.file_gap_fill_control, sep = ""),
    header = T,
    na.strings = "NA",
    stringsAsFactors = F
  )
colnames(control_gap_filled) <-
  colnames(read.csv(
    paste(control_gap_fill.path, postfilter.file_gap_fill_control, sep = ""),
    header = T,
    na.strings = "NA"
  ))

head(control_gap_filled)

tail(control_gap_filled)

```



```{r}
## read in full output file of treatment and control gap filled data
treat_and_cont_gap_filled <-
  read.csv(
    paste0(control_and_treat_gap_fill.path, postfilter.file_gap_fill_control_and_treat, sep = ""),
    header = T,
    na.strings = "NA",
    stringsAsFactors = F
  )
colnames(treat_and_cont_gap_filled) <-
  colnames(read.csv(
    paste(control_and_treat_gap_fill.path, postfilter.file_gap_fill_control_and_treat, sep = ""),
    header = T,
    na.strings = "NA"
  ))

head(treat_and_cont_gap_filled)

tail(treat_and_cont_gap_filled)

colnames(treat_and_cont_gap_filled)

#not sure why did this below... may not have to do it
names(treat_and_cont_gap_filled)[names(treat_and_cont_gap_filled) == "ï..TIMESTAMP"] <- "TIMESTAMP"

colnames(treat_and_cont_gap_filled)

```
#read in post filter file for getting VWc data
```{r}
## read in full output file of treatment and control gap filled data
postfilter <-
  read.csv(
    paste0(post_filter.path, postfilter.file_post_filter, sep = ""),
    header = T,
    na.strings = "NA",
    stringsAsFactors = F
  )
colnames(postfilter) <-
  colnames(read.csv(
    paste(post_filter.path, postfilter.file_post_filter, sep = ""),
    header = T,
    na.strings = "NA"
  ))

head(postfilter)

tail(postfilter)

colnames(postfilter)



colnames(postfilter)
```

#adding back timestamps to files
```{r}


treat_gap_filled$TIMESTAMP <- strptime(paste(treat_gap_filled$TIMESTAMP),
                                 format = "%m/%d/%Y %H:%M",
                                 tz = "Etc/GMT-8")

head(treat_gap_filled$TIMESTAMP)

head(treat_gap_filled)

#######################################################

control_gap_filled$TIMESTAMP <- strptime(paste(control_gap_filled$TIMESTAMP),
                                 format = "%m/%d/%Y %H:%M",
                                 tz = "Etc/GMT-8")

head(control_gap_filled$TIMESTAMP)

head(control_gap_filled)



########################################################

treat_and_cont_gap_filled$TIMESTAMP <- strptime(paste(treat_and_cont_gap_filled$TIMESTAMP),
                                 format = "%m/%d/%Y %H:%M",
                                 tz = "Etc/GMT-8")

head(treat_and_cont_gap_filled$TIMESTAMP)

head(treat_and_cont_gap_filled)




#########################################################
postfilter$TIMESTAMP <- strptime(paste(postfilter$TIMESTAMP),
                                 format = "%m/%d/%Y %H:%M",
                                 tz = "Etc/GMT-8")

head(postfilter$TIMESTAMP)

head(postfilter)
```





#addding time.id gap filled
```{r}
treat_gap_filled$time.id <- treat_gap_filled$TIMESTAMP$year + 1900 +
  (treat_gap_filled$TIMESTAMP$yday) / 366 +
  (treat_gap_filled$TIMESTAMP$hour) / 366 / 24 +
  (treat_gap_filled$TIMESTAMP$min) / 366 / 24 / 60

treat_gap_filled$time.id[1:50]
plot(treat_gap_filled$TIMESTAMP, treat_gap_filled$time.id)
which(duplicated(treat_gap_filled$time.id))

###############################
control_gap_filled$time.id <- control_gap_filled$TIMESTAMP$year + 1900 +
  (control_gap_filled$TIMESTAMP$yday) / 366 +
  (control_gap_filled$TIMESTAMP$hour) / 366 / 24 +
  (control_gap_filled$TIMESTAMP$min) / 366 / 24 / 60

control_gap_filled$time.id[1:50]
plot(control_gap_filled$TIMESTAMP, control_gap_filled$time.id)
which(duplicated(control_gap_filled$time.id))

##################################
treat_and_cont_gap_filled$time.id <- treat_and_cont_gap_filled$TIMESTAMP$year + 1900 +
  (treat_and_cont_gap_filled$TIMESTAMP$yday) / 366 +
  (treat_and_cont_gap_filled$TIMESTAMP$hour) / 366 / 24 +
  (treat_and_cont_gap_filled$TIMESTAMP$min) / 366 / 24 / 60

treat_and_cont_gap_filled$time.id[1:50]
plot(treat_and_cont_gap_filled$TIMESTAMP, treat_and_cont_gap_filled$time.id)


#####################################
postfilter$time.id <- postfilter$TIMESTAMP$year + 1900 +
  (postfilter$TIMESTAMP$yday) / 366 +
  (postfilter$TIMESTAMP$hour) / 366 / 24 +
  (postfilter$TIMESTAMP$min) / 366 / 24 / 60

postfilter$time.id[1:50]
plot(postfilter$TIMESTAMP, postfilter$time.id)



```





#Creating DOY
```{r}
treat_gap_filled$DOY <- treat_gap_filled$TIMESTAMP$year + 1900 +
  (treat_gap_filled$TIMESTAMP$yday) / 366

head(treat_gap_filled$DOY, 50)

###############################
control_gap_filled$DOY <- control_gap_filled$TIMESTAMP$year + 1900 +
  (control_gap_filled$TIMESTAMP$yday) / 366

head(control_gap_filled$DOY, 50)

#########################################
treat_and_cont_gap_filled$DOY <- treat_and_cont_gap_filled$TIMESTAMP$year + 1900 +
  (treat_and_cont_gap_filled$TIMESTAMP$yday) / 366

head(treat_and_cont_gap_filled$DOY, 50)

##############################################
postfilter$DOY <- postfilter$TIMESTAMP$year + 1900 +
  (postfilter$TIMESTAMP$yday) / 366

head(postfilter$DOY, 50)


```





#creating neg GPP to add respiration and GPP to test if correct
```{r}

treat_gap_filled$Gpp_neg <- (treat_gap_filled$GPP_U50_f * -1)

plot(treat_gap_filled$DOY,
     treat_gap_filled$Gpp_neg)

treat_gap_filled$NEE_test <- (treat_gap_filled$Gpp_neg + treat_gap_filled$Reco_U50)

plot(treat_gap_filled$DOY,
     treat_gap_filled$NEE_test)


#############################################################

treat_and_cont_gap_filled$Gpp_neg <- (treat_and_cont_gap_filled$GPP_U50_f * -1)

plot(treat_and_cont_gap_filled$DOY,
     treat_and_cont_gap_filled$Gpp_neg)

treat_and_cont_gap_filled$NEE_test <- (treat_and_cont_gap_filled$Gpp_neg + treat_and_cont_gap_filled$Reco_U50)

plot(treat_and_cont_gap_filled$DOY,
     treat_and_cont_gap_filled$NEE_test)
################################################################
control_gap_filled$Gpp_neg <- (control_gap_filled$GPP_U50_f * -1)

plot(control_gap_filled$DOY,
     control_gap_filled$Gpp_neg)

control_gap_filled$NEE_test <- (control_gap_filled$Gpp_neg + control_gap_filled$Reco_U50)

plot(control_gap_filled$DOY,
     control_gap_filled$NEE_test)



```


# Making all night time GPP values zero
## HC: it's ok to have some positive hourly gpp, to conserve sum(nee) = sum(gpp+reco)

```{r}

#making all GPP values that we measure at night Zero

#####################################
#treat_gap_filled$Gpp_neg[(treat_gap_filled$PotRad_U50 == 0)] <- 0

################################
#control_gap_filled$Gpp_neg[(control_gap_filled$PotRad_U50 == 0)] <- 0


##########################################
#treat_and_cont_gap_filled$Gpp_neg[(treat_and_cont_gap_filled$PotRad_U50 == 0)] <- 0




```

#Creating a new data column for respiration 
#combination of Day Reco_U50 and night NEE_U50_f
#Our night time respiration data will be directly measured, while our daytime respiration data will be modeled. 
## HC: it's ok to have some negative hourly respiration, to conserve sum(nee) = sum(gpp+reco)

```{r}

############################################################
#Treatment
# creating a new column called respiration
treat_gap_filled$respiration <- (treat_gap_filled$Reco_U50 * 1)

# Assigning all nighttime respiration values from original gap-filled nee
treat_gap_filled$respiration[(treat_gap_filled$PotRad_U50 == 0)] <-
  treat_gap_filled$NEE_U50_f[(treat_gap_filled$PotRad_U50 == 0)]

#Now turn any respiration values less than zero to NA's
# treat_gap_filled$respiration[(treat_gap_filled$respiration <= 0)] <-
#   NA

#blank
treat_gap_filled$blank = (treat_gap_filled$Reco_U50 *
                                      0)

treat_gap_filled$blank[(treat_gap_filled$blank == 0)] <-
  NA

plot(treat_gap_filled$respiration)

plot(treat_gap_filled$Reco_U50)

################################################################
#control
control_gap_filled$respiration <- (control_gap_filled$Reco_U50 * 1)

# Assigning all nighttime respiration values from original gap-filled nee
control_gap_filled$respiration[(control_gap_filled$PotRad_U50 == 0)] <-
  control_gap_filled$NEE_U50_f[(control_gap_filled$PotRad_U50 == 0)]

#Now turn any respiration values less than zero to NA's
# control_gap_filled$respiration[(control_gap_filled$respiration <= 0)] <-
#   NA

#blank
control_gap_filled$blank = (control_gap_filled$Reco_U50 *
                                      0)

control_gap_filled$blank[(control_gap_filled$blank == 0)] <-
  NA

plot(control_gap_filled$respiration)

plot(control_gap_filled$respiration[control_gap_filled$PotRad_U50 == 0])

plot(control_gap_filled$NEE_U50_f[control_gap_filled$PotRad_U50 == 0])

plot(control_gap_filled$Reco_U50)
#######################################
#control and treatment
treat_and_cont_gap_filled$respiration <- (treat_and_cont_gap_filled$Reco_U50 * 1)

# Assigning all nighttime respiration values from original gap-filled nee
treat_and_cont_gap_filled$respiration[(treat_and_cont_gap_filled$PotRad_U50 == 0)] <-
  treat_and_cont_gap_filled$NEE_U50_f[(treat_and_cont_gap_filled$PotRad_U50 == 0)]

#Now turn any respiration values less than zero to NA's
# treat_and_cont_gap_filled$respiration[(treat_and_cont_gap_filled$respiration <= 0)] <-
#   NA

#blank
treat_and_cont_gap_filled$blank = (treat_and_cont_gap_filled$Reco_U50 *
                                      0)

treat_and_cont_gap_filled$blank[(treat_and_cont_gap_filled$blank == 0)] <-
  NA



```


#looking at the control data. original GAM filled remainder with ready proc

```{r}

plot(control_gap_filled$TIMESTAMP, control_gap_filled$NEE_original,
     ylim = c(-20,40),
     col ="red")

par(new= TRUE)

plot(control_gap_filled$TIMESTAMP, control_gap_filled$NEE_U50_f, 
     ylim = c(-20,40),
     col ="blue")

```





#Plotting NEE variables###

####panel 1 half-hourly non-gap filled and half hourly gap filled###
#panel 2 GPP_neg and Respiration
#panel 3 cumulative sums of NEE, Respiration and neg GPP


#Treatment side

```{r}

treat_gap_filled$NEE_U50_f_1 = (treat_gap_filled$NEE_U50_f * 1)

target.plot.var_nee <- c("NEE_U50_f",
                         "Gpp_neg",
                         "blank")

target.plot.var_nee.title <- c(
  expression(FC ~ '(' ~ mu ~ mol ~ m ^ {-2 } ~ s ^ { -1 } ~ ')'),
  expression(GPP ~ ';' ~ Reco~'(' ~ mu ~ mol ~ m ^ {-2 } ~ s ^ { -1 } ~ ')'),
  expression(Cumulative~sum~ '(' ~ g ~ C ~ m ^ {-2 } ~ ')')
)

## locate the start of each month
month.loc <- which(
  treat_gap_filled$TIMESTAMP$mday == 1 &
    treat_gap_filled$TIMESTAMP$hour == 0 &
    treat_gap_filled$TIMESTAMP$min == 0
)
month.ticks <-
  substr(seq(
    treat_gap_filled$TIMESTAMP[month.loc[1]],
    treat_gap_filled$TIMESTAMP[month.loc[length(month.loc)]],
    by = "months"
  ), 6, 7)

## daily average values
daily_nee.tmp <-
  data.frame(
    date = tapply(
      treat_gap_filled$time.id,
      treat_gap_filled$DOY,
      min
    ),
    daily_nee = tapply(
      treat_gap_filled$NEE_U50_f,
      treat_gap_filled$DOY,
      na.mean
    ),
    daily_gpp = tapply(
      treat_gap_filled$Gpp_neg,
      treat_gap_filled$DOY,
      na.mean
    ),
    daily_reco = tapply(
      treat_gap_filled$Reco_U50,
      treat_gap_filled$DOY,
      na.mean
    )
  )

## convert NEE, Reco_U50 gpp to cumulative sum of carbon
# convert to cumulative carbon
for(ll in 2:4) {
  # convert to daily units
  daily_nee.tmp[, ll] <-
    daily_nee.tmp[, ll] * 12 / 1000000 * 1800 * 48
  daily_nee.tmp[is.na(daily_nee.tmp[, ll]), ll] <- 0
  
  # calculate cumulative sum, hard-coded with first/second years
  daily_nee.tmp[1:365, ll] <-
    cumsum(daily_nee.tmp[1:365, ll])
  daily_nee.tmp[366:nrow(daily_nee.tmp), ll] <-
    cumsum(daily_nee.tmp[366:nrow(daily_nee.tmp), ll])
  
  # set break (missing value) between two years
  daily_nee.tmp[366, ll] <- NA
}

## begin plot   
png(
  paste0(out.path, "NEE_treatment_growing_post_compost_concord",
    treat_gap_filled$TIMESTAMP$year[1] + 1900, "_",
    treat_gap_filled$TIMESTAMP$yday[1] + 1, "_",
    treat_gap_filled$TIMESTAMP$year[nrow(treat_gap_filled)] + 1900, "_",
    treat_gap_filled$TIMESTAMP$yday[nrow(treat_gap_filled)] + 1, "_",
    "all_NEE_",
    Sys.Date(), ".png"
  ),
  width = 5.5,
  height = 6,
  units = "in",
  res = 300,
  pointsize = 11,
  bg = "white"
)
par(oma = c(4, 4.5, 0.5, 0.5),
    mar = c(0, 0, 0.25, 0))

par(fig = c(0, 1, 2 / 3, 1), new = FALSE)
plot(
  treat_gap_filled$time.id[is.na(treat_gap_filled$NEE_original)],
  treat_gap_filled$NEE_U50_f[is.na(treat_gap_filled$NEE_original)],
  xlab = "",
  ylab = "",
  cex = 0.5,
  col = "darkgrey",
  bg = "lightgrey",
  xaxt = "n",
  las = 1,
  pch = 21,
  xaxs = "i",
  ylim = c(-10, 10),
  cex.axis = 0.8
)

points(
  treat_gap_filled$time.id[!is.na(treat_gap_filled$NEE_original)],
  treat_gap_filled$NEE_U50_f[!is.na(treat_gap_filled$NEE_original)],
  cex = 0.5,
  col = "black",
  bg = "black",
  pch = 21,
)

abline(
  v = 2020 + 290 / 366,
  col = "red",
  lwd = 2,
  lty = 4
)
abline(h = 0, col = "black")
abline(v = daily_nee.tmp$date[366], lwd= 1.5, col = "black")

text(
  x = treat_gap_filled$time.id[1],
  y = 30,
  paste0("(a)"),
  adj = c(0, 1),
  cex = 0.9
)

mtext(
  side = 2,
  target.plot.var_nee.title[[1]],
  line = 3,
  outer = FALSE,
  cex = 0.8
)

## panel b
par(fig = c(0, 1, 1 / 3, 2 / 3), new = TRUE)
plot(
  treat_gap_filled$time.id,
  treat_gap_filled$Gpp_neg,
  xlab = "",
  ylab = "",
  cex = 0.5,
  col = "darkgrey",
  bg = "lightgrey",
  xaxt = "n",
  las = 1,
  pch = 21,
  xaxs = "i",
  ylim = c(-10, 10),
  cex.axis = 0.8
)

points(
  treat_gap_filled$time.id,
  treat_gap_filled$Reco_U50,
  cex = 0.5,
  col = "black",
  bg = "black",
  pch = 21,
)

abline(
  v = 2020 + 290 / 366,
  col = "red",
  lwd = 2,
  lty = 4
)
abline(h = 0, col = "black")
abline(v = daily_nee.tmp$date[366], lwd= 1.5, col = "black")

text(
  x = treat_gap_filled$time.id[1],
  y = 30,
  paste0("(b)"),
  adj = c(0, 1),
  cex = 0.9
)

mtext(
  side = 2,
  target.plot.var_nee.title[[2]],
  line = 3,
  outer = FALSE,
  cex = 0.8
)


## panel c
par(fig = c(0, 1, 0, 1 / 3), new = TRUE)
plot(
  daily_nee.tmp$date,
  daily_nee.tmp$daily_nee,
  type = "l",
  lwd = 1.5,
  col = "black",
  xlab = "",
  ylab = "",
  xaxt = "n",
  las = 1,
  xaxs = "i",
  ylim = c(-375, 375),
  cex.axis = 0.8
)

lines(daily_nee.tmp$date,
      daily_nee.tmp$daily_gpp,
      lwd = 1.5,
      col = "forestgreen",
      lty = 2
      )

lines(daily_nee.tmp$date,
      daily_nee.tmp$daily_reco,
      lwd = 1.5,
      col = "red",
      lty = 3
      )

abline(
  v = 2020 + 290 / 366,
  col = "red",
  lwd = 2,
  lty = 4
)
abline(h = 0, col = "black")
abline(v = daily_nee.tmp$date[366], lwd= 1.5, col = "black")

axis(
  side = 1,
  at = treat_gap_filled$time.id[month.loc],
  labels = month.ticks,
  tck = -.025,
  cex.axis = 0.8
)

text(
  x = treat_gap_filled$time.id[1],
  y = 1200,
  paste0("(c)"),
  adj = c(0, 1),
  cex = 0.9
)

mtext(
  side = 2,
  target.plot.var_nee.title[[3]],
  line = 3,
  outer = FALSE,
  cex = 0.8
)

axis(
  side = 1,
  at = c(2019.75, 2020.5, 2021.17),
  label = c(2019, 2020, 2021),
  cex.axis = 0.8,
  tck = -.025,
  lty = 0,
  bty = "n",
  line = 0.9
)

mtext(
  side = 1,
  "Month / Year",
  line = 3,
  outer = FALSE,
  cex = 0.8
)


dev.off()
```
#Control Side NEE

```{r}

control_gap_filled$NEE_U50_f_1 = (control_gap_filled$NEE_U50_f * 1)

target.plot.var_nee <- c("NEE_U50_f",
                         "Gpp_neg",
                         "blank")

target.plot.var_nee.title <- c(
  expression(FC ~ '(' ~ mu ~ mol ~ m ^ {-2 } ~ s ^ { -1 } ~ ')'),
  expression(GPP ~ ';' ~ Reco~'(' ~ mu ~ mol ~ m ^ {-2 } ~ s ^ { -1 } ~ ')'),
  expression(Cumulative~sum~ '(' ~ g ~ C ~ m ^ {-2 } ~ ')')
)

## locate the start of each month
month.loc <- which(
  control_gap_filled$TIMESTAMP$mday == 1 &
    control_gap_filled$TIMESTAMP$hour == 0 &
    control_gap_filled$TIMESTAMP$min == 0
)
month.ticks <-
  substr(seq(
    control_gap_filled$TIMESTAMP[month.loc[1]],
    control_gap_filled$TIMESTAMP[month.loc[length(month.loc)]],
    by = "months"
  ), 6, 7)

## daily average values
daily_nee.tmp <-
  data.frame(
    date = tapply(
      control_gap_filled$time.id,
      control_gap_filled$DOY,
      min
    ),
    daily_nee = tapply(
      control_gap_filled$NEE_U50_f,
      control_gap_filled$DOY,
      na.mean
    ),
    daily_gpp = tapply(
      control_gap_filled$Gpp_neg,
      control_gap_filled$DOY,
      na.mean
    ),
    daily_reco = tapply(
      control_gap_filled$Reco_U50,
      control_gap_filled$DOY,
      na.mean
    )
  )

## convert NEE, Reco_U50 gpp to cumulative sum of carbon
# convert to cumulative carbon
for(ll in 2:4) {
  # convert to daily units
  daily_nee.tmp[, ll] <-
    daily_nee.tmp[, ll] * 12 / 1000000 * 1800 * 48
  daily_nee.tmp[is.na(daily_nee.tmp[, ll]), ll] <- 0
  
  # calculate cumulative sum, hard-coded with first/second years
  daily_nee.tmp[1:365, ll] <-
    cumsum(daily_nee.tmp[1:365, ll])
  daily_nee.tmp[366:nrow(daily_nee.tmp), ll] <-
    cumsum(daily_nee.tmp[366:nrow(daily_nee.tmp), ll])
  
  # set break (missing value) between two years
  daily_nee.tmp[366, ll] <- NA
}

## begin plot   
png(
  paste0(out.path, "NEE_control_growing_post_compost_concord",
    control_gap_filled$TIMESTAMP$year[1] + 1900, "_",
    control_gap_filled$TIMESTAMP$yday[1] + 1, "_",
    control_gap_filled$TIMESTAMP$year[nrow(control_gap_filled)] + 1900, "_",
    control_gap_filled$TIMESTAMP$yday[nrow(control_gap_filled)] + 1, "_",
    "all_NEE_",
    Sys.Date(), ".png"
  ),
  width = 5.5,
  height = 6,
  units = "in",
  res = 300,
  pointsize = 11,
  bg = "white"
)
par(oma = c(4, 4.5, 0.5, 0.5),
    mar = c(0, 0, 0.25, 0))

par(fig = c(0, 1, 2 / 3, 1), new = FALSE)
plot(
  control_gap_filled$time.id[is.na(control_gap_filled$NEE_original)],
  control_gap_filled$NEE_U50_f[is.na(control_gap_filled$NEE_original)],
  xlab = "",
  ylab = "",
  cex = 0.5,
  col = "darkgrey",
  bg = "lightgrey",
  xaxt = "n",
  las = 1,
  pch = 21,
  xaxs = "i",
  ylim = c(-10, 10),
  cex.axis = 0.8
)

points(
  control_gap_filled$time.id[!is.na(control_gap_filled$NEE_original)],
  control_gap_filled$NEE_U50_f[!is.na(control_gap_filled$NEE_original)],
  cex = 0.5,
  col = "black",
  bg = "black",
  pch = 21,
)

abline(
  v = 2020 + 290 / 366,
  col = "red",
  lwd = 2,
  lty = 4
)
abline(h = 0, col = "black")
abline(v = daily_nee.tmp$date[366], lwd= 1.5, col = "black")

text(
  x = control_gap_filled$time.id[1],
  y = 30,
  paste0("(a)"),
  adj = c(0, 1),
  cex = 0.9
)

mtext(
  side = 2,
  target.plot.var_nee.title[[1]],
  line = 3,
  outer = FALSE,
  cex = 0.8
)

## panel b
par(fig = c(0, 1, 1 / 3, 2 / 3), new = TRUE)
plot(
  control_gap_filled$time.id,
  control_gap_filled$Gpp_neg,
  xlab = "",
  ylab = "",
  cex = 0.5,
  col = "darkgrey",
  bg = "lightgrey",
  xaxt = "n",
  las = 1,
  pch = 21,
  xaxs = "i",
  ylim = c(-10, 10),
  cex.axis = 0.8
)

points(
  control_gap_filled$time.id,
  control_gap_filled$Reco_U50,
  cex = 0.5,
  col = "black",
  bg = "black",
  pch = 21,
)

abline(
  v = 2020 + 290 / 366,
  col = "red",
  lwd = 2,
  lty = 4
)
abline(h = 0, col = "black")
abline(v = daily_nee.tmp$date[366], lwd= 1.5, col = "black")

text(
  x = control_gap_filled$time.id[1],
  y = 30,
  paste0("(b)"),
  adj = c(0, 1),
  cex = 0.9
)

mtext(
  side = 2,
  target.plot.var_nee.title[[2]],
  line = 3,
  outer = FALSE,
  cex = 0.8
)


## panel c
par(fig = c(0, 1, 0, 1 / 3), new = TRUE)
plot(
  daily_nee.tmp$date,
  daily_nee.tmp$daily_nee,
  type = "l",
  lwd = 1.5,
  col = "black",
  xlab = "",
  ylab = "",
  xaxt = "n",
  las = 1,
  xaxs = "i",
  ylim = c(-375, 375),
  cex.axis = 0.8
)

lines(daily_nee.tmp$date,
      daily_nee.tmp$daily_gpp,
      lwd = 1.5,
      col = "forestgreen",
      lty = 2
      )

lines(daily_nee.tmp$date,
      daily_nee.tmp$daily_reco,
      lwd = 1.5,
      col = "red",
      lty = 3
      )

abline(
  v = 2020 + 290 / 366,
  col = "red",
  lwd = 2,
  lty = 4
)
abline(h = 0, col = "black")
abline(v = daily_nee.tmp$date[366], lwd= 1.5, col = "black")

axis(
  side = 1,
  at = control_gap_filled$time.id[month.loc],
  labels = month.ticks,
  tck = -.025,
  cex.axis = 0.8
)

text(
  x = control_gap_filled$time.id[1],
  y = 1200,
  paste0("(c)"),
  adj = c(0, 1),
  cex = 0.9
)

mtext(
  side = 2,
  target.plot.var_nee.title[[3]],
  line = 3,
  outer = FALSE,
  cex = 0.8
)

axis(
  side = 1,
  at = c(2019.75, 2020.5, 2021.17),
  label = c(2019, 2020, 2021),
  cex.axis = 0.8,
  tck = -.025,
  lty = 0,
  bty = "n",
  line = 0.9
)

mtext(
  side = 1,
  "Month / Year",
  line = 3,
  outer = FALSE,
  cex = 0.8
)


dev.off()

```
#Comparing VWC



```{r}

plot(postfilter$TIMESTAMP[postfilter$TIMESTAMP > as.POSIXct("2021-02-02")], postfilter$VWC_2_Avg_Control[postfilter$TIMESTAMP > as.POSIXct("2021-02-02")])

plot(postfilter$TIMESTAMP[postfilter$TIMESTAMP > as.POSIXct("2021-02-02")], postfilter$VWC_Avg[postfilter$TIMESTAMP > as.POSIXct("2021-02-02")])


## Generic time series plot
target.plot.var<-c(
                   "VWC_Avg",
                   "VWC_2_Avg_Control"
                   )
target.plot.var.title<-c(
                         expression(Soil~water~content~treatment~side~'('~m^{3}~m^{-3}~')'),
                         expression(Soil~water~content~control~side~'('~m^{3}~m^{-3}~')'))  

for(k1 in 1:length(target.plot.var)){
  
  ## locate the start of each month
  month.loc<-which(postfilter$TIMESTAMP$mday==1&
                     postfilter$TIMESTAMP$hour==0&
                     postfilter$TIMESTAMP$min==0)
  month.ticks <- seq(postfilter$TIMESTAMP[month.loc[1]],
                     postfilter$TIMESTAMP[month.loc[length(month.loc)]],by="months")
  
  png(paste0(out.path,
             "Concord_",
             postfilter$TIMESTAMP$year[1]+1900,"_",
             postfilter$TIMESTAMP$yday[1]+1,"_",
             postfilter$TIMESTAMP$year[nrow(postfilter)]+1900,"_",
             postfilter$TIMESTAMP$yday[nrow(postfilter)]+1,"_",
             target.plot.var[k1],"_",
             Sys.Date(),".png"),
      width=6,
      height=4,
      units="in",
      res=300,
      pointsize = 11,
      bg = "white")
  
  par(oma=c(0.5,0.5,0.5,0.5),mar=c(4,4.5,0,0))
  plot(postfilter$TIMESTAMP,
       postfilter[,target.plot.var[k1]],
       xlab="TIMESTAMP",
       ylab=target.plot.var.title[k1],
       cex=0.5,col="grey",bg="lightgrey",
       las=1,pch=21,
       xaxs="i",yaxs="i"
  )
  
  abline(h=0,col="darkgrey")
  
  ## daily averge line
  daily.tmp<-data.frame(date=tapply(postfilter$time.id,postfilter$doy.id,min),
                        daily=tapply(postfilter[,target.plot.var[k1]],postfilter$doy.id,na.mean))
  
  lines(postfilter$TIMESTAMP[which(postfilter$time.id %in% daily.tmp$date)],
        daily.tmp$daily,
        lwd=1.5,col="black")
  
  ## loess fit line
  loess.tmp<-loess(postfilter[,target.plot.var[k1]]~c(1:nrow(postfilter)),span=0.1)
  
  ## avoid plotting long gaps
  long.gap<-which(loess.tmp$x[-1]-loess.tmp$x[-length(loess.tmp$x)]>48*3)
  
  if(length(long.gap)>0){ ## skip if any long gaps
    if(long.gap[1]>1) long.gap<-c(1,long.gap)
    if(long.gap[length(long.gap)]<length(loess.tmp$x)) long.gap<-c(long.gap,length(loess.tmp$x))
    
    for(k1 in 1:(length(long.gap)-1)){
      lines(postfilter$TIMESTAMP[round(loess.tmp$x[c((long.gap[k1]+1):(long.gap[k1+1]-1))])],
            loess.tmp$fitted[c((long.gap[k1]+1):(long.gap[k1+1]-1))],
            lwd=1.5,col="red")
    }  
  }else{
      lines(postfilter$TIMESTAMP[round(loess.tmp$x)],
            loess.tmp$fitted,
            lwd=1.5,col="red")
  }

  axis(1, at = month.ticks, labels = FALSE, tcl = -0.3)
  dev.off()
}

```



```{r}
colnames(treat_gap_filled)
```


#analyzing Latent heat on the treatment side
#panel A gapfilled and non-gapfilled LE fluxes
#panel B cumulative sum of LE
```{r}



target.plot.var_LE <- c("LE_f",
                         "blank")

target.plot.var_LE.title <- c(
  expression(LE ~ '(' ~ W ~ m ^ {-2 } ~  ')'),
  expression(Cumulative~sum~LE~ '(' ~ W ~ m ^ {-2 } ~ ')')
)

## locate the start of each month
month.loc <- which(
  treat_gap_filled$TIMESTAMP$mday == 1 &
    treat_gap_filled$TIMESTAMP$hour == 0 &
    treat_gap_filled$TIMESTAMP$min == 0
)
month.ticks <-
  substr(seq(
    treat_gap_filled$TIMESTAMP[month.loc[1]],
    treat_gap_filled$TIMESTAMP[month.loc[length(month.loc)]],
    by = "months"
  ), 6, 7)

## daily average values
daily_LE.tmp <-
  data.frame(
    date = tapply(
      treat_gap_filled$time.id,
      treat_gap_filled$DOY,
      min
    ),
    daily_LE = tapply(
      treat_gap_filled$LE_f,
      treat_gap_filled$DOY,
      na.mean
    )
  )

## convert NEE, Reco_U50 gpp to cumulative sum of carbon
# convert to cumulative carbon
for(ll in 2:2) {
  # convert to daily units
  daily_LE.tmp[, ll] <-
    daily_LE.tmp[, ll]*1
  daily_LE.tmp[is.na(daily_LE.tmp[, ll]), ll] <- 0
  
  # calculate cumulative sum, hard-coded with first/second years
  daily_LE.tmp[1:365, ll] <-
    cumsum(daily_LE.tmp[1:365, ll])
  daily_LE.tmp[366:nrow(daily_LE.tmp), ll] <-
    cumsum(daily_LE.tmp[366:nrow(daily_LE.tmp), ll])
  
  # set break (missing value) between two years
  daily_LE.tmp[366, ll] <- NA
}

## begin plot   
png(
  paste0(out.path, "Treatment_LE_concord_growing",
    treat_gap_filled$TIMESTAMP$year[1] + 1900, "_",
    treat_gap_filled$TIMESTAMP$yday[1] + 1, "_",
    treat_gap_filled$TIMESTAMP$year[nrow(treat_gap_filled)] + 1900, "_",
    treat_gap_filled$TIMESTAMP$yday[nrow(treat_gap_filled)] + 1, "_",
    "all_LE_",
    Sys.Date(), ".png"
  ),
  width = 5.5,
  height = 6,
  units = "in",
  res = 300,
  pointsize = 11,
  bg = "white"
)
par(oma = c(4, 4.5, 0.5, 0.5),
    mar = c(0, 0, 0.25, 0))

par(fig = c(0, 1, 1 / 2, 1), new = FALSE)
plot(
  treat_gap_filled$time.id[is.na(treat_gap_filled$LE_orig)],
  treat_gap_filled$LE_f[is.na(treat_gap_filled$LE_orig)],
  xlab = "",
  ylab = "",
  cex = 0.5,
  col = "darkgrey",
  bg = "lightgrey",
  xaxt = "n",
  las = 1,
  pch = 21,
  xaxs = "i",
  ylim = c(-50, 300),
  cex.axis = 0.8
)

points(
  treat_gap_filled$time.id[!is.na(treat_gap_filled$LE_orig)],
  treat_gap_filled$LE_f[!is.na(treat_gap_filled$LE_orig)],
  cex = 0.5,
  col = "black",
  bg = "black",
  pch = 21,
)

abline(
  v = 2020 + 290 / 366,
  col = "red",
  lwd = 2,
  lty = 4
)
abline(h = 0, col = "black")
abline(v = daily_LE.tmp$date[366], lwd= 1.5, col = "black")

text(
  x = treat_gap_filled$time.id[1],
  y = 30,
  paste0(""),
  adj = c(0, 1),
  cex = 0.9
)

mtext(
  side = 2,
  target.plot.var_LE.title[[1]],
  line = 3,
  outer = FALSE,
  cex = 0.8
)




## panel b
par(fig = c(0, 1, 0, 1 / 2), new = TRUE)
plot(
  daily_LE.tmp$date,
  daily_LE.tmp$daily_LE,
  type = "l",
  lwd = 1.5,
  col = "black",
  xlab = "",
  ylab = "",
  xaxt = "n",
  las = 1,
  xaxs = "i",
  ylim = c(0, 5500),
  cex.axis = 0.8
)


abline(
  v = 2020 + 290 / 366,
  col = "red",
  lwd = 2,
  lty = 4
)
abline(h = 0, col = "black")
abline(v = daily_LE.tmp$date[366], lwd= 1.5, col = "black")

axis(
  side = 1,
  at = treat_gap_filled$time.id[month.loc],
  labels = month.ticks,
  tck = -.025,
  cex.axis = 0.8
)

text(
  x = treat_gap_filled$time.id[1],
  y = 1200,
  paste0(""),
  adj = c(0, 1),
  cex = 0.9
)

mtext(
  side = 2,
  target.plot.var_LE.title[[2]],
  line = 3,
  outer = FALSE,
  cex = 0.8
)

axis(
  side = 1,
  at = c(2019.75, 2020.5, 2021.17),
  label = c(2019, 2020, 2021),
  cex.axis = 0.8,
  tck = -.025,
  lty = 0,
  bty = "n",
  line = 0.9
)

mtext(
  side = 1,
  "Month / Year",
  line = 3,
  outer = FALSE,
  cex = 0.8
)


dev.off()
```
#analyzing Latent heat on the control side side
#panel A gapfilled and non-gapfilled LE fluxes
#panel B cumulative sum of LE
```{r}



target.plot.var_LE <- c("LE_f",
                         "blank")

target.plot.var_LE.title <- c(
  expression(LE ~ '(' ~ W ~ m ^ {-2 } ~  ')'),
  expression(Cumulative~sum~LE~ '(' ~ W ~ m ^ {-2 } ~ ')')
)

## locate the start of each month
month.loc <- which(
  control_gap_filled$TIMESTAMP$mday == 1 &
    control_gap_filled$TIMESTAMP$hour == 0 &
    control_gap_filled$TIMESTAMP$min == 0
)
month.ticks <-
  substr(seq(
    control_gap_filled$TIMESTAMP[month.loc[1]],
    control_gap_filled$TIMESTAMP[month.loc[length(month.loc)]],
    by = "months"
  ), 6, 7)

## daily average values
daily_LE.tmp <-
  data.frame(
    date = tapply(
      control_gap_filled$time.id,
      control_gap_filled$DOY,
      min
    ),
    daily_LE = tapply(
      control_gap_filled$LE_f,
      control_gap_filled$DOY,
      na.mean
    )
  )

## convert NEE, Reco_U50 gpp to cumulative sum of carbon
# convert to cumulative carbon
for(ll in 2:2) {
  # convert to daily units
  daily_LE.tmp[, ll] <-
    daily_LE.tmp[, ll]*1
  daily_LE.tmp[is.na(daily_LE.tmp[, ll]), ll] <- 0
  
  # calculate cumulative sum, hard-coded with first/second years
  daily_LE.tmp[1:365, ll] <-
    cumsum(daily_LE.tmp[1:365, ll])
  daily_LE.tmp[366:nrow(daily_LE.tmp), ll] <-
    cumsum(daily_LE.tmp[366:nrow(daily_LE.tmp), ll])
  
  # set break (missing value) between two years
  daily_LE.tmp[366, ll] <- NA
}

## begin plot   
png(
  paste0(out.path, "Control_LE_concord_growing",
    control_gap_filled$TIMESTAMP$year[1] + 1900, "_",
    control_gap_filled$TIMESTAMP$yday[1] + 1, "_",
    control_gap_filled$TIMESTAMP$year[nrow(control_gap_filled)] + 1900, "_",
    control_gap_filled$TIMESTAMP$yday[nrow(control_gap_filled)] + 1, "_",
    "all_LE_",
    Sys.Date(), ".png"
  ),
  width = 5.5,
  height = 6,
  units = "in",
  res = 300,
  pointsize = 11,
  bg = "white"
)
par(oma = c(4, 4.5, 0.5, 0.5),
    mar = c(0, 0, 0.25, 0))

par(fig = c(0, 1, 1 / 2, 1), new = FALSE)
plot(
  control_gap_filled$time.id[is.na(control_gap_filled$LE_orig)],
  control_gap_filled$LE_f[is.na(control_gap_filled$LE_orig)],
  xlab = "",
  ylab = "",
  cex = 0.5,
  col = "darkgrey",
  bg = "lightgrey",
  xaxt = "n",
  las = 1,
  pch = 21,
  xaxs = "i",
  ylim = c(-50, 300),
  cex.axis = 0.8
)

points(
  control_gap_filled$time.id[!is.na(control_gap_filled$LE_orig)],
  control_gap_filled$LE_f[!is.na(control_gap_filled$LE_orig)],
  cex = 0.5,
  col = "black",
  bg = "black",
  pch = 21,
)

abline(
  v = 2020 + 290 / 366,
  col = "red",
  lwd = 2,
  lty = 4
)
abline(h = 0, col = "black")
abline(v = daily_LE.tmp$date[366], lwd= 1.5, col = "black")

text(
  x = control_gap_filled$time.id[1],
  y = 30,
  paste0(""),
  adj = c(0, 1),
  cex = 0.9
)

mtext(
  side = 2,
  target.plot.var_LE.title[[1]],
  line = 3,
  outer = FALSE,
  cex = 0.8
)




## panel b
par(fig = c(0, 1, 0, 1 / 2), new = TRUE)
plot(
  daily_LE.tmp$date,
  daily_LE.tmp$daily_LE,
  type = "l",
  lwd = 1.5,
  col = "black",
  xlab = "",
  ylab = "",
  xaxt = "n",
  las = 1,
  xaxs = "i",
  ylim = c(0, 5500),
  cex.axis = 0.8
)


abline(
  v = 2020 + 290 / 366,
  col = "red",
  lwd = 2,
  lty = 4
)
abline(h = 0, col = "black")
abline(v = daily_LE.tmp$date[366], lwd= 1.5, col = "black")

axis(
  side = 1,
  at = control_gap_filled$time.id[month.loc],
  labels = month.ticks,
  tck = -.025,
  cex.axis = 0.8
)

text(
  x = control_gap_filled$time.id[1],
  y = 1200,
  paste0(""),
  adj = c(0, 1),
  cex = 0.9
)

mtext(
  side = 2,
  target.plot.var_LE.title[[2]],
  line = 3,
  outer = FALSE,
  cex = 0.8
)

axis(
  side = 1,
  at = c(2019.75, 2020.5, 2021.17),
  label = c(2019, 2020, 2021),
  cex.axis = 0.8,
  tck = -.025,
  lty = 0,
  bty = "n",
  line = 0.9
)

mtext(
  side = 1,
  "Month / Year",
  line = 3,
  outer = FALSE,
  cex = 0.8
)


dev.off()
```
#sensible heat on treatment side
```{r}
target.plot.var_LE <- c("H_f",
                         "blank")

target.plot.var_LE.title <- c(
  expression(H ~ '(' ~ W ~ m ^ {-2 } ~  ')'),
  expression(Cumulative~sum~H~ '(' ~ W ~ m ^ {-2 } ~ ')')
)

## locate the start of each month
month.loc <- which(
  treat_gap_filled$TIMESTAMP$mday == 1 &
    treat_gap_filled$TIMESTAMP$hour == 0 &
    treat_gap_filled$TIMESTAMP$min == 0
)
month.ticks <-
  substr(seq(
    treat_gap_filled$TIMESTAMP[month.loc[1]],
    treat_gap_filled$TIMESTAMP[month.loc[length(month.loc)]],
    by = "months"
  ), 6, 7)

## daily average values
daily_H.tmp <-
  data.frame(
    date = tapply(
      treat_gap_filled$time.id,
      treat_gap_filled$DOY,
      min
    ),
    daily_LE = tapply(
      treat_gap_filled$H_f,
      treat_gap_filled$DOY,
      na.mean
    )
  )

## convert H ti cumulative sum
# convert to cumulative carbon
for(ll in 2:2) {
  # convert to daily units
  daily_H.tmp[, ll] <-
    daily_H.tmp[, ll]*1
  daily_H.tmp[is.na(daily_H.tmp[, ll]), ll] <- 0
  
  # calculate cumulative sum, hard-coded with first/second years
  daily_H.tmp[1:365, ll] <-
    cumsum(daily_H.tmp[1:365, ll])
  daily_H.tmp[366:nrow(daily_H.tmp), ll] <-
    cumsum(daily_H.tmp[366:nrow(daily_H.tmp), ll])
  
  # set break (missing value) between two years
  daily_H.tmp[366, ll] <- NA
}

## begin plot   
png(
  paste0(out.path, "Treatment_H_concord_growing",
    treat_gap_filled$TIMESTAMP$year[1] + 1900, "_",
    treat_gap_filled$TIMESTAMP$yday[1] + 1, "_",
    treat_gap_filled$TIMESTAMP$year[nrow(treat_gap_filled)] + 1900, "_",
    treat_gap_filled$TIMESTAMP$yday[nrow(treat_gap_filled)] + 1, "_",
    "growing_H_",
    Sys.Date(), ".png"
  ),
  width = 5.5,
  height = 6,
  units = "in",
  res = 300,
  pointsize = 11,
  bg = "white"
)
par(oma = c(4, 4.5, 0.5, 0.5),
    mar = c(0, 0, 0.25, 0))

par(fig = c(0, 1, 1 / 2, 1), new = FALSE)
plot(
  treat_gap_filled$time.id[is.na(treat_gap_filled$H_orig)],
  treat_gap_filled$H_f[is.na(treat_gap_filled$H_orig)],
  xlab = "",
  ylab = "",
  cex = 0.5,
  col = "darkgrey",
  bg = "lightgrey",
  xaxt = "n",
  las = 1,
  pch = 21,
  xaxs = "i",
  ylim = c(-100, 400),
  cex.axis = 0.8
)

points(
  treat_gap_filled$time.id[!is.na(treat_gap_filled$H_orig)],
  treat_gap_filled$H_f[!is.na(treat_gap_filled$H_orig)],
  cex = 0.5,
  col = "black",
  bg = "black",
  pch = 21,
)

abline(
  v = 2020 + 290 / 366,
  col = "red",
  lwd = 2,
  lty = 4
)
abline(h = 0, col = "black")
abline(v = daily_H.tmp$date[366], lwd= 1.5, col = "black")

text(
  x = treat_gap_filled$time.id[1],
  y = 30,
  paste0(""),
  adj = c(0, 1),
  cex = 0.9
)

mtext(
  side = 2,
  target.plot.var_LE.title[[1]],
  line = 3,
  outer = FALSE,
  cex = 0.8
)




## panel b
par(fig = c(0, 1, 0, 1 / 2), new = TRUE)
plot(
  daily_H.tmp$date,
  daily_H.tmp$daily_LE,
  type = "l",
  lwd = 1.5,
  col = "black",
  xlab = "",
  ylab = "",
  xaxt = "n",
  las = 1,
  xaxs = "i",
  ylim = c(-100, 5000),
  cex.axis = 0.8
)


abline(
  v = 2020 + 290 / 366,
  col = "red",
  lwd = 2,
  lty = 4
)
abline(h = 0, col = "black")
abline(v = daily_H.tmp$date[366], lwd= 1.5, col = "black")

axis(
  side = 1,
  at = treat_gap_filled$time.id[month.loc],
  labels = month.ticks,
  tck = -.025,
  cex.axis = 0.8
)

text(
  x = treat_gap_filled$time.id[1],
  y = 1200,
  paste0(""),
  adj = c(0, 1),
  cex = 0.9
)

mtext(
  side = 2,
  target.plot.var_LE.title[[2]],
  line = 3,
  outer = FALSE,
  cex = 0.8
)

axis(
  side = 1,
  at = c(2019.75, 2020.5, 2021.17),
  label = c(2019, 2020, 2021),
  cex.axis = 0.8,
  tck = -.025,
  lty = 0,
  bty = "n",
  line = 0.9
)

mtext(
  side = 1,
  "Month / Year",
  line = 3,
  outer = FALSE,
  cex = 0.8
)


dev.off()
```
#control side sensible heat

```{r}
target.plot.var_LE <- c("H_f",
                         "blank")

target.plot.var_LE.title <- c(
  expression(H ~ '(' ~ W ~ m ^ {-2 } ~  ')'),
  expression(Cumulative~sum~H~ '(' ~ W ~ m ^ {-2 } ~ ')')
)

## locate the start of each month
month.loc <- which(
  control_gap_filled$TIMESTAMP$mday == 1 &
    control_gap_filled$TIMESTAMP$hour == 0 &
    control_gap_filled$TIMESTAMP$min == 0
)
month.ticks <-
  substr(seq(
    control_gap_filled$TIMESTAMP[month.loc[1]],
    control_gap_filled$TIMESTAMP[month.loc[length(month.loc)]],
    by = "months"
  ), 6, 7)

## daily average values
daily_H.tmp <-
  data.frame(
    date = tapply(
      control_gap_filled$time.id,
      control_gap_filled$DOY,
      min
    ),
    daily_LE = tapply(
      control_gap_filled$H_f,
      control_gap_filled$DOY,
      na.mean
    )
  )

## convert H ti cumulative sum
# convert to cumulative carbon
for(ll in 2:2) {
  # convert to daily units
  daily_H.tmp[, ll] <-
    daily_H.tmp[, ll]*1
  daily_H.tmp[is.na(daily_H.tmp[, ll]), ll] <- 0
  
  # calculate cumulative sum, hard-coded with first/second years
  daily_H.tmp[1:365, ll] <-
    cumsum(daily_H.tmp[1:365, ll])
  daily_H.tmp[366:nrow(daily_H.tmp), ll] <-
    cumsum(daily_H.tmp[366:nrow(daily_H.tmp), ll])
  
  # set break (missing value) between two years
  daily_H.tmp[366, ll] <- NA
}

## begin plot   
png(
  paste0(out.path, "Control_H_concord_growing",
    control_gap_filled$TIMESTAMP$year[1] + 1900, "_",
    control_gap_filled$TIMESTAMP$yday[1] + 1, "_",
    control_gap_filled$TIMESTAMP$year[nrow(control_gap_filled)] + 1900, "_",
    control_gap_filled$TIMESTAMP$yday[nrow(control_gap_filled)] + 1, "_",
    "growing_H_",
    Sys.Date(), ".png"
  ),
  width = 5.5,
  height = 6,
  units = "in",
  res = 300,
  pointsize = 11,
  bg = "white"
)
par(oma = c(4, 4.5, 0.5, 0.5),
    mar = c(0, 0, 0.25, 0))

par(fig = c(0, 1, 1 / 2, 1), new = FALSE)
plot(
  control_gap_filled$time.id[is.na(control_gap_filled$H_orig)],
  control_gap_filled$H_f[is.na(control_gap_filled$H_orig)],
  xlab = "",
  ylab = "",
  cex = 0.5,
  col = "darkgrey",
  bg = "lightgrey",
  xaxt = "n",
  las = 1,
  pch = 21,
  xaxs = "i",
  ylim = c(-100, 400),
  cex.axis = 0.8
)

points(
  control_gap_filled$time.id[!is.na(control_gap_filled$H_orig)],
  control_gap_filled$H_f[!is.na(control_gap_filled$H_orig)],
  cex = 0.5,
  col = "black",
  bg = "black",
  pch = 21,
)

abline(
  v = 2020 + 290 / 366,
  col = "red",
  lwd = 2,
  lty = 4
)
abline(h = 0, col = "black")
abline(v = daily_H.tmp$date[366], lwd= 1.5, col = "black")

text(
  x = control_gap_filled$time.id[1],
  y = 30,
  paste0(""),
  adj = c(0, 1),
  cex = 0.9
)

mtext(
  side = 2,
  target.plot.var_LE.title[[1]],
  line = 3,
  outer = FALSE,
  cex = 0.8
)




## panel b
par(fig = c(0, 1, 0, 1 / 2), new = TRUE)
plot(
  daily_H.tmp$date,
  daily_H.tmp$daily_LE,
  type = "l",
  lwd = 1.5,
  col = "black",
  xlab = "",
  ylab = "",
  xaxt = "n",
  las = 1,
  xaxs = "i",
  ylim = c(-100, 5000),
  cex.axis = 0.8
)


abline(
  v = 2020 + 290 / 366,
  col = "red",
  lwd = 2,
  lty = 4
)
abline(h = 0, col = "black")
abline(v = daily_H.tmp$date[366], lwd= 1.5, col = "black")

axis(
  side = 1,
  at = control_gap_filled$time.id[month.loc],
  labels = month.ticks,
  tck = -.025,
  cex.axis = 0.8
)

text(
  x = control_gap_filled$time.id[1],
  y = 1200,
  paste0(""),
  adj = c(0, 1),
  cex = 0.9
)

mtext(
  side = 2,
  target.plot.var_LE.title[[2]],
  line = 3,
  outer = FALSE,
  cex = 0.8
)

axis(
  side = 1,
  at = c(2019.75, 2020.5, 2021.17),
  label = c(2019, 2020, 2021),
  cex.axis = 0.8,
  tck = -.025,
  lty = 0,
  bty = "n",
  line = 0.9
)

mtext(
  side = 1,
  "Month / Year",
  line = 3,
  outer = FALSE,
  cex = 0.8
)


dev.off()
```


#GLMM with ancova looking at effect of treatment on nee. not significant.Also treating treatment as a random effect to account for the lack of independence between measurments from the respective sides. 
```{r}
#colnames(treat_and_cont_gap_filled)
#ANCOVA and Daytime NEE all year Comparison treatment and control area
NEE_by_treatment_post_compost<- glmer(NEE_U50_f ~  Treatment+Rg_f
                     + (1|Treatment), 
                  data = treat_and_cont_gap_filled [treat_and_cont_gap_filled$PotRad_U50>0,], )

summary(NEE_by_treatment_post_compost)
Anova(NEE_by_treatment_post_compost)

```
```{r}
Reco_by_treatment_post_compost<- glmer(Reco_U50 ~  Treatment+Rg_f
                     + (1|Treatment), 
                  data = treat_and_cont_gap_filled [treat_and_cont_gap_filled$PotRad_U50>0,], )

summary(Reco_by_treatment_post_compost)
Anova(Reco_by_treatment_post_compost)

GPP_by_treatment_post_compost<- glmer(Reco_U50 ~  Treatment+Rg_f
                     + (1|Treatment), 
                  data = treat_and_cont_gap_filled [treat_and_cont_gap_filled$PotRad_U50>0,], )

summary(Reco_by_treatment_post_compost)
Anova(Reco_by_treatment_post_compost)

```

`