---
title: "Concord 2020 Soils"
author: "Isabel Torres"
date: "11/18/2021"
output: html_document
---
#Concord, CA 2020 Soil Sample Analyses 
#Total Carbon, Total Nitrogen, pH, and EC for soil samples 0-100cm depth. 
#Isabel L. Torres 
#CSU East Bay 2022

# Updated by Adam Zeilinger, 2023-01-27
# Includes analysis of 2020 and 2021 data

##################################
#Data Import
##################################


```{r, include=FALSE}

install.packages("lme4")

install.packages("tidyverse") # Includes ggplot2

install.packages("cowplot")

## Install package from GitHub for the nonparametric tests from Stanley et al. (2023) paper
devtools::install_github('spertus/nptests')


```

```{r}
library(lme4)
library(tidyverse) # Includes ggplot2
library(cowplot)
library(readr)
library(nptests)

## Load functions
source("functions/make_labelstring.R")

```

```{r times series plot, echo=FALSE}

#data <- read_csv("~/Desktop/R data/ESM/Concord_CN_master.csv")
data <- read_csv("data/Concord_CN_master.csv")

str(data)
head(data)

#### Rename columns to make them easier to type and read in R
#names(data) <- c("trt", "year", "plot", "sampleID", "depth", "oc_mg_ha", "on_mg_ha")
data <- data %>%
  rename(sampleID = `Sample ID`,
         oc_mg_ha = `OC (Mg/Ha)`,
         on_mg_ha = `ON (Mg/Ha)`)
str(data)
summary(data)

#### Looking at data
with(data, table(Year, Plot))
table(data$Treatment)
table(data$Depth)



```

Carbon (Mg/Ha) in soil by 10cm intervals, up to 100 cm depth. 
```{r}
ggplot(data = data, aes(x = data$Depth, y = data$oc_mg_ha)) +
  geom_point(color = "black", alpha = 0.5) +
  theme_bw()


```

Nitrogen (Mg/Ha) in soil by 10cm intervals, up to 100 cm depth. 
```{r}
ggplot(data = data, aes(x = data$Depth, y = data$on_mg_ha)) +
  geom_point(color = "black", alpha = 0.5) +
  theme_bw()

```


#### Preliminary exploration of nonparametric test from Stanley et al. (2023)
```{r}

## Pivot to a wider format so each treatment is in a separate column
dataDepth10 <- data %>% dplyr::filter(Depth == 10) %>%
  pivot_wider(id_cols = Plot, names_from = Treatment, values_from = oc_mg_ha)
dataDepth10

## Gaffke nonparametric test for depth 10 only
## Note: the test requires lower and upper bounds on the data ...
## here I chose 50 as an upper bound because this was the same cutoff for outliers, may need to be modified
## Only provides p-value of one-sided test of mu_2 <= mu_1...
## where mu_2 and mu_1 are means of sample_2 and sample_1 vectors, respectively
gaffkeTestDepth10 <- two_sample_gaffke(sample_1 = dataDepth10$TRT,
                                       sample_2 = dataDepth10$CTL,
                                       bounds = c(0,60))
gaffkeTestDepth10


## Test the Gaffke CI function
gaffkeCI_depth10Trt <- c(gaffke_CI(dataDepth10$TRT, side = "upper"),
                         mean(dataDepth10$TRT),
                         gaffke_CI(dataDepth10$TRT, side = "lower"))


gaffkeCI_depth10Trt

```

# Load and combine data from both years

```{r}

#### Load and combine year data
data20 <- data
data21 <- read_csv("data/Concord_CN_master_2021_edited.csv")
str(data21)

## Rename 2021 data
data21 <- data21 %>%
  rename(sampleID = `Sample ID`,
         oc_mg_ha = `OC (Mg/Ha)`,
         on_mg_ha = `ON (Mg/Ha)`)
summary(data21)

#### Looking at data
with(data21, table(Year, Plot))
table(data21$Treatment)
table(data21$Depth)


## Combine data sets
data <- bind_rows(data20, data21)

#### Looking at data
with(data, table(Year, Plot))
with(data, table(Year, Treatment))
with(data, table(Year, Depth))

saveRDS(data, file = "output/combined_years_CN_data_set.rds")



```


#### Exploring Carbon data

```{r}

#### data set includes both years
data <- readRDS("output/combined_years_CN_data_set.rds")


## Boxplot by treatment
trtCBoxplot <- ggplot(data = data, aes(y = oc_mg_ha, x = Treatment)) +
  geom_boxplot() +
  facet_wrap(~ Year) +
  theme_bw()
trtCBoxplot

## Scatter plot by depth and treatment
trtCScatterplot <- ggplot(data = data, aes(y = oc_mg_ha, x = Depth, group = Treatment)) +
  geom_point(aes(color = Treatment)) +
  facet_wrap(~ Year) +
  theme_bw()
trtCScatterplot


## Histograms of the data by treatment
TrtCHistograms <- ggplot(data = data, aes(x = oc_mg_ha, group = Treatment)) +
  geom_histogram(binwidth = 5) +
  facet_wrap(~Treatment + Year, nrow = 2) +
  theme_bw()
TrtCHistograms
## Both treatments are heavily skewed to the right (have heavy right tails)
## Outliers in Control treatment
## Outlier cutoffs: include all data < 60
## Apply to both years

outlier_C_upper_cutoff <- 60

```



#### Exploring Nitrogen data
```{r}

data <- readRDS("output/combined_years_CN_data_set.rds")
  
## Boxplot by treatment
trtNBoxplot <- ggplot(data = data, aes(y = on_mg_ha, x = Treatment)) +
  geom_boxplot() +
  facet_wrap(~ Year, scales = "free_y") +
  theme_bw()
trtNBoxplot

## Scatter plot by depth and treatment
trtNScatterplot <- ggplot(data = data, aes(y = on_mg_ha, x = Depth, group = Treatment)) +
  geom_point(aes(color = Treatment)) +
  facet_wrap(~ Year, scales = "free_y") +
  theme_bw()
trtNScatterplot


## Histograms of the data by treatment
TrtNHistograms <- ggplot(data = data, aes(x = on_mg_ha, group = Treatment)) +
  geom_histogram(binwidth = 5) +
  facet_wrap(~ Treatment + Year, nrow = 2) +
  theme_bw()
TrtNHistograms
## Both treatments are heavily skewed to the right (have heavy right tails)
## Outliers in both treatments in 2020
## Outlier cutoffs: include all data > 0 & < 10
## Apply to both years

outlier_N_upper_cutoff <- 10


```






#### Fitting nonparametric CI on all depths, treatments, and years

```{r}

## Import full data set
data <- readRDS("output/combined_years_CN_data_set.rds")

str(data)

#### Looking at data
with(data, table(Year, Plot))
with(data, table(Year, Treatment))
with(data, table(Year, Depth))


## Exploratory test of the Gaffke CI function
dataTest1 <- data %>% dplyr::filter(Depth == 10 & Year == 2021 & Treatment == "TRT" & !is.na(oc_mg_ha))
with(dataTest1, table(Treatment, Year, Depth)) 

gaffkeCI_depth10Trt <- c(gaffke_CI(dataTest1$oc_mg_ha, alpha = 0.025, B = 20000, side = "lower"),
                         mean(dataTest1$oc_mg_ha),
                         gaffke_CI(dataTest1$oc_mg_ha, alpha = 0.025, B = 20000, side = "upper"))
gaffkeCI_depth10Trt

################################################################################################
#### Estimating confidence intervals using Gaffke's nonparametric method

## Confidence intervals for C
npResultsTableOC <- data %>%
  ## Remove NAs and outliers for C (defined as any observed C >= 60 mg/ha and any negative values)
  dplyr::filter(!is.na(oc_mg_ha) & oc_mg_ha <= outlier_C_upper_cutoff & oc_mg_ha >= 0) %>%
  group_by(Treatment, Year, Depth) %>%
  dplyr::summarise(cil = gaffke_CI(oc_mg_ha, alpha = 0.025, B = 20000, side = "lower"),
                   mean = mean(oc_mg_ha),
                   ciu = gaffke_CI(oc_mg_ha, alpha = 0.025, B = 20000, side = "upper")) %>%
  dplyr::mutate(measured = "C") # Add a variable specifying what was measured (C or N) for combining results
npResultsTableOC

## Confidence intervals for N
npResultsTableON <- data %>%
  ## Remove NAs and outliers (defined as any observed nitrogen >= 10 mg/ha and any negative values)
  dplyr::filter(!is.na(on_mg_ha) & on_mg_ha <= outlier_N_upper_cutoff & on_mg_ha >= 0) %>%
  group_by(Treatment, Year, Depth) %>%
  dplyr::summarise(cil = gaffke_CI(on_mg_ha, alpha = 0.025, B = 20000, side = "lower"),
                   mean = mean(on_mg_ha),
                   ciu = gaffke_CI(on_mg_ha, alpha = 0.025, B = 20000, side = "upper")) %>%
  dplyr::mutate(measured = "N") # Add a variable specifying what was measured (C or N) for combining results
npResultsTableON

## Put data.frames together
npResultsTable <- bind_rows(npResultsTableOC, npResultsTableON)
npResultsTable %>% print.data.frame()

## Sanity check on the results
cildiff <- with(npResultsTable, mean - cil)
all(cildiff > 0)
ciudiff <- with(npResultsTable, ciu - mean)
all(ciudiff > 0)
## All means are between cil and ciu

## Save results
write.csv(npResultsTable, file = "results/nonparametric_Gaffke_CI_results_table_oc_on.csv", row.names = FALSE)

```


#### Create a figure with observations, means, and CI

```{r}

#### Import nonparametric test results
npResultsTable <- read.csv("results/nonparametric_Gaffke_CI_results_table_oc_on.csv", header = TRUE)
## Add the full measurement names
npResultsTable <- npResultsTable %>%
  dplyr::mutate(measured = ifelse(measured == "C", "oc_mg_ha", "on_mg_ha"),
                ## Create a new composite variable to create subpanels in plot
                year_measured = paste(Year, measured, sep = "_"))
npResultsTable


#### Import full data set
data <- readRDS("output/combined_years_CN_data_set.rds")
str(data)

## Pivot data to long format and prep for plotting
dataLong <- data %>%
  pivot_longer(contains("mg_ha"), names_to = "measured", values_to = "observations") %>%
  ## Remove C and N outliers
  dplyr::filter((measured == "oc_mg_ha" & observations <= outlier_C_upper_cutoff & observations >= 0) | 
                  (measured == "on_mg_ha" & observations <= outlier_N_upper_cutoff & observations >= 0)) %>%
  ## Create a new composite variable to create subpanels in plot
  dplyr::mutate(year_measured = paste(Year, measured, sep = "_"))
dataLong

#############################################################################
# #### Checking that filtering out outliers worked correctly
# data %>% dplyr::filter(oc_mg_ha >= 60) ## Select OC outliers
# dataLong %>% dplyr::filter(Treatment == "CTL" & Year == 2020 & Depth == 10 & 
#                              (Plot == 10 | Plot == 12))
# data %>% dplyr::filter(Treatment == "CTL" & Year == 2020 & Depth == 10 & 
#                          (Plot == 10 | Plot == 12))
# dataLong %>% dplyr::filter(Treatment == "CTL" & Year == 2020 & Depth == 10 & 
#                              (Plot == 10 | Plot == 12 | Plot == 11))
# ## ON measurements from the same plots are kept in dataLong...
# ## and OC and ON measurements from other plots are also kept.
# dataLong %>% dplyr::filter(observations >= 20)
# ## OC observations > 20 are included
# dataLong %>% dplyr::filter(observations >= 20) %>% distinct(measured)
# ## and only OC observations > 20
# ## Filtering seems to have worked
######################################################################

#### Plot with data and stats results
soilDataCIPlot <- ggplot(data = dataLong, aes(x = Depth, group = Treatment)) +
  geom_point(aes(y = observations, color = Treatment), 
             alpha = 0.4, size = 2, position = position_dodge(width = 4.5)) +
  facet_wrap(~ year_measured, scales = "free_y", labeller = label_panels) +
  ## To see the year-measurement labels on the panels, comment out above facet_wrap() line and uncomment below:
  #facet_wrap(~ year_measured, scales = "free_y") +
  geom_point(data = npResultsTable, aes(x = Depth, y = mean), 
             size = 3.5, position = position_dodge(width = 4.5), color = "black") +
  geom_point(data = npResultsTable, aes(x = Depth, y = mean, color = Treatment), 
             size = 3, position = position_dodge(width = 4.5)) +
  geom_errorbar(data = npResultsTable, aes(x = Depth, ymax = ciu, ymin = cil), 
                width=0.4, position = position_dodge(width = 4.5)) +
  scale_x_continuous("Soil depth (cm)") +
  scale_y_continuous("Total concentration (mg/ha)") +
  scale_color_manual(values = c("red", "blue")) +
  theme_bw(base_size = 14) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black"),
        panel.background = element_blank(),
        strip.background = element_blank(),
        strip.text = element_text(hjust = -0))
soilDataCIPlot

ggsave(soilDataCIPlot, filename = "results/figures/plot_soil_CN_data_np_stats.jpg",
       units = "in", width = 10, height = 10)


```

# Check results from linear models

```{r}

#### Import full data set
data <- readRDS("output/combined_years_CN_data_set.rds")
str(data)

#### Carbon lm model
data_outliersC <- data %>%
  dplyr::filter(!is.na(oc_mg_ha) & oc_mg_ha <= outlier_C_upper_cutoff & oc_mg_ha >= 0)

clmMod <- lm(oc_mg_ha ~ Year*Depth*Treatment, data = data_outliersC)
plot(clmMod)
summary(clmMod)
## Results for C: marginally significant Treatment main effect and Year-Treatment interaction
## QQ plot confirms skew in distribution

#### Nitrogen lm model
data_outliersN <- data %>%
  dplyr::filter(!is.na(on_mg_ha) & on_mg_ha <= outlier_N_upper_cutoff & on_mg_ha >= 0)

nlmMod <- lm(on_mg_ha ~ Year*Depth*Treatment, data = data_outliersN)
plot(nlmMod)
summary(nlmMod)
## Results for N: significant Treatment main effect and Year-Treatment interaction
## QQ plot confirms skew in distribution


```

