---
title: 'Met_Master Merge with Eddy_Pro_Master: Data from 2019-11-18'
output:
  word_document: default
  html_notebook: default
  html_document:
    df_print: paged
---



```{r}
library(tidyverse)
source("calc_footprint_FFP.R")
library(ggplot2)
library(modelr)
options(na.action = na.warn)
```


# Lists #
```{r}
rm(list=ls())
```

# Defining the data I/O directory for the Eddy Master File #
**
```{r}
path_eddy<-"C:\\Users\\Tommy\\flux\\Data-exploring\\02_Concord\\"
path.in_eddy<-paste(path_eddy,"01_Proccessed_Data",sep="")
path.out_eddy<-paste(path_eddy,"03_combined_data",sep="")
ver<-"Master_Eddy" 
file.name_eddy<-paste("master_eddy_pro_concord",sep="")
```

# read in eddypro full output Master file, parse variable names #
```{r}
data_master_eddy<-read.csv(paste(path.in_eddy,"\\",ver,"\\",file.name_eddy,".csv",sep=""),
                  header=F,
                  skip=3,
                  na.strings=c(-9999),
                  stringsAsFactors = F)
colnames(data_master_eddy)<-colnames(
  read.csv(paste(path.in_eddy,"\\",ver,"\\",file.name_eddy,".csv",sep=""),
           header=T,
           skip=1))


```


# Defining the data I/O directory for the Master met_data #

```{r}
path_met<-"C:\\Users\\Tommy\\flux\\Data-exploring\\02_Concord\\"
path.in_met<-paste(path_met,"01_Proccessed_Data",sep="")
path.out_met<-paste(path_met,"03_combined_data",sep="")
ver<-"met_data" 
file.name<-paste("MET_data_master",sep="")
```




#read in Met_Data Master file, parse variable names and define N/As#


```{r}
met_data_master<-read.csv(paste(path.in_met,"\\",ver,"\\",file.name,".csv",sep=""),
                  header=F,
                  skip=4,
                  na.strings=c("NAN"),
                  stringsAsFactors = F)
colnames(met_data_master)<-colnames(
  read.csv(paste(path.in_met,"\\",ver,"\\",file.name,".csv",sep=""),
           header=T,
           skip= 1))



```




# Parsing the time stamp converting it into a POSIXlt vector#

**interpreting date and time into new timestamp column**

**Then taking that time stamp column and turning each time into a unique number (time.id) so I can join based on that. As it can be really tricky to join/merge based on time stamps alone**

**Or I could make sure both time stamps are characters and match them that way**

**Finally ploting time.id to make sure my times translate linearily**

```{r}
data_master_eddy$TIMESTAMP<-strptime(paste(data_master_eddy$date,data_master_eddy$time,sep=" "),format="%m/%d/%Y %H:%M", tz = "GMT")

data_master_eddy$time.id<-data_master_eddy$TIMESTAMP$year+1900+(data_master_eddy$TIMESTAMP$yday)/366+(data_master_eddy$TIMESTAMP$hour)/366/24+ (data_master_eddy$TIMESTAMP$min)/366/24/60

data_master_eddy$time.id[1:50]
plot(data_master_eddy$time.id)
which(duplicated(data_master_eddy$time.id))
```


#Taking the met_data and turning the time stamp into posixt format#

```{r}
met_data_master$TIMESTAMP<-strptime(met_data_master$TIMESTAMP,
                           format ="%m/%d/%Y %H:%M", tz = "GMT")

met_data_master$TIMESTAMP[1:20]
```

#Making sure timestamp columns line up#

```{r}

met_data_master$TIMESTAMP[1:10]

data_master_eddy$TIMESTAMP[1:10]
```




#creating a time id for the MET Data so I I can join the MET and Eddy Pro Data#

```{r}

met_data_master$time.id <-met_data_master$TIMESTAMP$year+1900+(met_data_master$TIMESTAMP$yday)/366+(met_data_master$TIMESTAMP$hour)/366/24 + (met_data_master$TIMESTAMP$min)/366/24/60 

met_data_master$time.id[1:20]
plot(met_data_master$time.id)
which(duplicated(met_data_master$time.id))


```


#Joining the Met_Data and Eddy Pro Data Sets#

**with merge**

```{r}

combo_master_ed_met<- merge(met_data_master[,-which(colnames(met_data_master)=="TIMESTAMP")], data_master_eddy[,-which(colnames(data_master_eddy)=="TIMESTAMP")], by = "time.id")



colnames(combo_master_ed_met)

```


#Add back time stamp to the combo_master_ed_met#
```{r}
combo_master_ed_met$TIMESTAMP<-strptime(paste(combo_master_ed_met$date,combo_master_ed_met$time,sep=" "),format="%m/%d/%Y %H:%M", tz = "GMT")

combo_master_ed_met$TIMESTAMP[1:10]





```

#Creating a CSV File of my combine Master File!#
```{r}
write.csv(combo_master_ed_met,
          paste(path.out_eddy,ver,"combo_master_ed_met",sep=""),
          quote = T,
          row.names = F)
```

#filtering data for quality control filters#
**filtering latent heat, sensible heat, co2 flux, qc_tau and h20flux by quality controls**

```{r}
combo_master_ed_met$LE.[!is.na(combo_master_ed_met$qc_LE)&combo_master_ed_met$qc_LE==2]<-NA

combo_master_ed_met$qqc_h2o_flux[!is.na(combo_master_ed_met$qc_h2o_flux)&combo_master_ed_met$qc_h2o_flux==2]<-NA

combo_master_ed_met$H[!is.na(combo_master_ed_met$qc_H)&combo_master_ed_met$qc_H==2]<-NA

combo_master_ed_met$u.[!is.na(combo_master_ed_met$qc_Tau)&combo_master_ed_met$qc_Tau==2]<-NA

combo_master_ed_met$co2_flux[!is.na(combo_master_ed_met$co2_flux)&combo_master_ed_met$co2_flux==2]<-NA


```

# latent heat, sensible heat, h20_flux, and relative humidity by day for whole period #


```{r}

plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$LE)
hist(combo_master_ed_met$LE)

plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$h2o_flux)

plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$H)

plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$RH)





```




#Plotting Co2 flux by timstamp on x-axis. 
```{r}

plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$co2_flux, ylim = c(-10,10),cex=0.6)

plot(tapply(combo_master_ed_met$H,round(combo_master_ed_met$DOY),function(x) mean(x,na.rm=T)))



```

#line plot of c02_fluxes#
```{r}
ggplot(data = combo_master_ed_met) + 
  geom_line(mapping = aes(x = time.id , y = co2_flux)) 

```


#latent heat and Sensible heat plotted over eachother

```{r}
plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$LE,pch=1,col="blue",cex=0.6)
points(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$H,col="red",pch=1,cex=0.6)
```

#air temperatue by sensible heat an U* by co2 flux
```{r}
plot(combo_master_ed_met$air_temperature-273.15,combo_master_ed_met$H,xlim=c(10,40),ylim=c(-100,500))



plot(combo_master_ed_met$u. ,combo_master_ed_met$co2_flux, ylim = c(0, 10), xlim = c(0,1))
```


#Adding best fit line to air temperature by sensible heat
```{r}
ggplot(data = combo_master_ed_met) + 
  geom_point(mapping = aes(x = air_temperature-273.15, y = H)) +
  geom_smooth(mapping = aes(x = air_temperature-273.15, y = H))


```

#best fit line to U* bt co2 flux
```{r}
ggplot(data = combo_master_ed_met) + 
  geom_point(mapping = aes(x = u., y = co2_flux)) +
  geom_smooth(mapping = aes(x = u., y = co2_flux))


```


```{r}
library(tidyverse)
hist(combo_master_ed_met$wind_dir, xlim = c(0,370), breaks = 36, main = "Wind Direction")
```

#Comparing MET Temperature data to temperature reading from Licor intruments#
```{r}
plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$PTemp_C_Avg)
points(combo_master_ed_met$TIMESTAMP,combo_master_ed_met$air_temperature-273.15,col="red",pch=2)
```



#Adding coefficient to Net radiation#
```{r}
combo_master_ed_met$Correct_NR = (combo_master_ed_met$NR_Wm2_Avg*10)/14.2
```


```{r}
summary(combo_master_ed_met$Correct_NR[c(1:600,2500:4000)])
plot(combo_master_ed_met$Correct_NR)
```


filtering out bad NR numbers

```{r}

combo_master_ed_met$Correct_NR[!is.na(combo_master_ed_met$Correct_NR)&(combo_master_ed_met$Correct_NR<(-150)|combo_master_ed_met$Correct_NR>800)]<-NA
summary(combo_master_ed_met$Correct_NR)
plot(combo_master_ed_met$Correct_NR)
```





