---
title: "Data Exploration of 2019-10-24 Data Download"
output: html_notebook
---

```{r}
library(tidyverse)
source("calc_footprint_FFP.R")
library(ggplot2)
library(modelr)
options(na.action = na.warn)
```


# Lists #
```{r}
rm(list=ls())
```


# Defining the data I/O directory #
**"C:\Users\Tommy\flux\Data-exploring\02_Concord\01_Proccessed_Data\2019-09-25_All_data_To_Date\eddypro_20190925_Concord_alltodate.csv**
```{r}
path<-"C:\\Users\\Tommy\\flux\\Data-exploring\\02_Concord\\"
path.in<-paste(path,"01_Proccessed_Data",sep="")
path.out<-paste(path,"02_Footprint_Analysis",sep="")
ver<-"2019-10-24_two_wks_prior" 
file.name<-paste("eddypro_Concord20191024_full_output_2019-11-04T170244_exp",sep="")
```

# read in eddypro full output file, parse variable names #
```{r}
data20191024<-read.csv(paste(path.in,"\\",ver,"\\",file.name,".csv",sep=""),
                  header=F,
                  skip=3,
                  na.strings=c(-9999),
                  stringsAsFactors = F)
colnames(data20191024)<-colnames(
  read.csv(paste(path.in,"\\",ver,"\\",file.name,".csv",sep=""),
           header=T,
           skip=1))
```

# Parsing the time stamp converting it into a POSIXlt vector#
**interpreting date and time into new timestamp column**
```{r}
data20191024$TIMESTAMP<-strptime(paste(data20191024$date,data20191024$time,sep=" "),
                            format="%Y-%m-%d %H:%M",tz="UTC")

data20191024$TIMESTAMP[1:10]
```

#Basic Summary of Data

```{r}
summary(data20191024)
```


# filter ustar based on qc_Tau. #
**Filtering out all qc_Tau = 2**
```{r}
data20191024$u.[!is.na(data20191024$qc_Tau)&data20191024$qc_Tau==2]<-NA
```


#Plotting Co2 flux by timstamp on x-axis. 
```{r}

plot(data20191024$TIMESTAMP ,data20191024$co2_flux)

```

# filtering latent heat, sensible heat and h20flux by quality controls#

```{r}
data20191024$LE.[!is.na(data20191024$qc_LE)&data20191024$qc_LE==2]<-NA

data20191024$qqc_h2o_flux[!is.na(data20191024$qc_h2o_flux)&data20191024$qc_h2o_flux==2]<-NA

data20191024$H[!is.na(data20191024$qc_H)&data20191024$qc_H==2]<-NA

```

# latent heat, sensible heat, h20_flux, and relative humidity by day for whole period #


```{r}

plot(data20191024$TIMESTAMP ,data20191024$LE)
hist(data20191024$LE)

plot(data20191024$TIMESTAMP ,data20191024$h2o_flux)

plot(data20191024$TIMESTAMP ,data20191024$H)

plot(data20191024$TIMESTAMP ,data20191024$RH)





```


#h20 flux and co2 flux
```{r}

plot(data20191024$TIMESTAMP ,data20191024$co2_flux, ylim = c(-6,6))
points(data20191024$TIMESTAMP ,data20191024$h2o_flux,col="red",pch=2)

```


#latent heat and Sensible heat plotted over eachother

```{r}
plot(data20191024$TIMESTAMP ,data20191024$LE)
points(data20191024$TIMESTAMP ,data20191024$H,col="red",pch=2)
```

#air temperatue by sensible heat an U* by co2 flux
```{r}
plot(data20191024$air_temperature-273.15,data20191024$H,xlim=c(10,40),ylim=c(-100,500))



plot(data20191024$u. ,data20191024$co2_flux, ylim = c(0, 10), xlim = c(0,1))
```


#Adding best fit line to air temperature by sensible heat
```{r}
ggplot(data = data20191024) + 
  geom_point(mapping = aes(x = air_temperature-273.15, y = H)) +
  geom_smooth(mapping = aes(x = air_temperature-273.15, y = H))

ggplot(data = data20191024) + 
  geom_point(mapping = aes(x = air_temperature-273.15, y = H)) +
    geom_smooth(mapping = aes(x = air_temperature-273.15, y = H, method= 'lm', se = FALSE))
```

#best fit line to U* bt co2 flux
```{r}
ggplot(data = data20191024) + 
  geom_point(mapping = aes(x = u., y = co2_flux)) +
  geom_smooth(mapping = aes(x = u., y = co2_flux))


```


```{r}
library(openair)
library(tidyverse)

hist(data20191024$wind_dir, xlim = c(0,370), breaks = 36, main = "Wind Direction")




```




#ggplot regression
**doing stuff wrong, not sure what**

```{r}
ggplotRegression <- function (fit) {

   

    ggplot(fit$model, aes_string(x = air_temperature-273.15(fit$model)[2], y = H(fit$model)[1])) + 
      geom_point() +
      stat_smooth(method = "lm", col = "red") +
      labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                         "Intercept =",signif(fit$coef[[1]],5 ),
                         " Slope =",signif(fit$coef[[2]], 5),
                         " P =",signif(summary(fit)$coef[2,4], 5)))
}


```

```{r}

 
```


