---
title: "Energy Balance Closure 2019-11-01 Data"
output: html_notebook
---



 

```{r}
library(tidyverse)
source("calc_footprint_FFP.R")
library(ggplot2)
library(modelr)
options(na.action = na.warn)
```


# Lists #
```{r}
rm(list=ls())
```


# Defining the data I/O directory #
**"C:\Users\Tommy\flux\Data-exploring\02_Concord\01_Proccessed_Data\2019-09-25_All_data_To_Date\eddypro_20190925_Concord_alltodate.csv**
```{r}
path1<-"C:\\Users\\Tommy\\flux\\Data-exploring\\02_Concord\\"
path.in1<-paste(path1,"01_Proccessed_Data",sep="")
path.out1<-paste(path1,"03_combined_data",sep="")
ver<-"2019-11-01_one_wk_prior" 
file.name1<-paste("eddypro_Concord20191101_1wk_prior_full_output_2019-11-04T175830_exp",sep="")
```

# read in eddypro full output file, parse variable names #
```{r}
data20191101<-read.csv(paste(path.in1,"\\",ver,"\\",file.name1,".csv",sep=""),
                  header=F,
                  skip=3,
                  na.strings=c(-9999),
                  stringsAsFactors = F)
colnames(data20191101)<-colnames(
  read.csv(paste(path.in1,"\\",ver,"\\",file.name1,".csv",sep=""),
           header=T,
           skip=1))

data20191101
```

# Parsing the time stamp converting it into a POSIXlt vector#

**interpreting date and time into new timestamp column**

**Then taking that time stamp column and turning each time into a unique number (time.id) so I can join based on that. As it can be really tricky to join/merge based on time stamps alone**

**Or I could make sure both time stamps are characters and match them that way**

**Finally ploting time.id to make sure my times translate linearily**

```{r}
data20191101$TIMESTAMP<-strptime(paste(data20191101$date,data20191101$time,sep=" "),
                            format="%m/%d/%Y %H:%M", tz = "GMT")

data20191101$time.id <-data20191101$TIMESTAMP$year+1900+(data20191101$TIMESTAMP$yday)/366+(data20191101$TIMESTAMP$hour)/366/24+ (data20191101$TIMESTAMP$min)/366/24/60

data20191101$time.id[1:50]
plot(data20191101$time.id)
which(duplicated(data20191101$time.id))
```

# Defining the data I/O directory for met_data #
**"C:\Users\Tommy\flux\Data-exploring\02_Concord\01_Proccessed_Data\met_data\CR6Series_Concord_Met_20191101.csv"**
```{r}
path<-"C:\\Users\\Tommy\\flux\\Data-exploring\\02_Concord\\"
path.in<-paste(path,"01_Proccessed_Data",sep="")
path.out3<-paste(path,"03_combined_data",sep="")
ver<-"met_data" 
file.name<-paste("CR6Series_Concord_Met_20191101",sep="")
```




#read in Met_Data file, parse variable names and define N/As#


```{r}
met_data20191101<-read.csv(paste(path.in,"\\",ver,"\\",file.name,".csv",sep=""),
                  header=F,
                  skip=4,
                  na.strings=c("NAN"),
                  stringsAsFactors = F)
colnames(met_data20191101)<-colnames(
  read.csv(paste(path.in,"\\",ver,"\\",file.name,".csv",sep=""),
           header=T,
           skip= 1))

met_data20191101

```

#Taking the met_data and turning the time stamp into posixt format#

```{r}
met_data20191101$TIMESTAMP<-strptime(met_data20191101$TIMESTAMP,
                            format="%Y-%m-%d %H:%M:%S", tz = "GMT")

met_data20191101$TIMESTAMP[1:50]
```

#Making sure timestamp columns line up#

```{r}

met_data20191101$TIMESTAMP[1:10]

data20191101$TIMESTAMP[1:10]
```


```{r}
met_data20191101
```

#creating a time id for the MET Data so I I can join the MET and Eddy Pro Data#

```{r}

met_data20191101$time.id <-met_data20191101$TIMESTAMP$year+1900+(met_data20191101$TIMESTAMP$yday)/366+(met_data20191101$TIMESTAMP$hour)/366/24 + (met_data20191101$TIMESTAMP$min)/366/24/60 

met_data20191101$time.id[1:50]
plot(met_data20191101$time.id)
which(duplicated(met_data20191101$time.id))

met_data20191101
```


#Joining the Met_Data and Eddy Pro Data Sets#

**with merge**

**need to add back timestamp**
```{r}

Combo20191101<- merge(met_data20191101[,-which(colnames(met_data20191101)=="TIMESTAMP")], data20191101[,-which(colnames(data20191101)=="TIMESTAMP")], by = "time.id")

Combo20191101

colnames(Combo20191101)

```


**with left join**
```{r}
Combo20191101<- met_data20191101 %>% 
  left_join(data20191101, by = time.id)
```




#Basic Summary of Eddy Pro Data

```{r}
summary(data20191101)
```


# filter ustar based on qc_Tau. #
**Filtering out all qc_Tau = 2**
```{r}
data20191101$u.[!is.na(data20191101$qc_Tau)&data20191101$qc_Tau==2]<-NA
```


#Plotting Co2 flux by timstamp on x-axis. 
```{r}

plot(data20191101$TIMESTAMP ,data20191101$co2_flux)

```

# filtering latent heat, sensible heat and h20flux by quality controls#

```{r}
data20191101$LE.[!is.na(data20191101$qc_LE)&data20191101$qc_LE==2]<-NA

data20191101$qqc_h2o_flux[!is.na(data20191101$qc_h2o_flux)&data20191101$qc_h2o_flux==2]<-NA

data20191101$H[!is.na(data20191101$qc_H)&data20191101$qc_H==2]<-NA

```

# latent heat, sensible heat, h20_flux, and relative humidity by day for whole period #


```{r}

plot(data20191101$TIMESTAMP ,data20191101$LE)
hist(data20191101$LE)

plot(data20191101$TIMESTAMP ,data20191101$h2o_flux)

plot(data20191101$TIMESTAMP ,data20191101$H)

plot(data20191101$TIMESTAMP ,data20191101$RH)





```


#h20 flux and co2 flux
```{r}

plot(data20191101$TIMESTAMP ,data20191101$co2_flux, ylim = c(-6,6))
points(data20191101$TIMESTAMP ,data20191101$h2o_flux,col="red",pch=2)

```


#latent heat and Sensible heat plotted over eachother

```{r}
plot(data20191101$TIMESTAMP ,data20191101$LE)
points(data20191101$TIMESTAMP ,data20191101$H,col="red",pch=2)
```

#air temperatue by sensible heat an U* by co2 flux
```{r}
plot(data20191101$air_temperature-273.15,data20191101$H,xlim=c(10,40),ylim=c(-100,500))



plot(data20191101$u. ,data20191101$co2_flux, ylim = c(0, 10), xlim = c(0,1))
```


#Adding best fit line to air temperature by sensible heat
```{r}
ggplot(data = data20191101) + 
  geom_point(mapping = aes(x = air_temperature-273.15, y = H)) +
  geom_smooth(mapping = aes(x = air_temperature-273.15, y = H))

ggplot(data = data20191101) + 
  geom_point(mapping = aes(x = air_temperature-273.15, y = H)) +
    geom_smooth(mapping = aes(x = air_temperature-273.15, y = H, method= 'lm', se = FALSE))
```

#best fit line to U* bt co2 flux
```{r}
ggplot(data = data20191101) + 
  geom_point(mapping = aes(x = u., y = co2_flux)) +
  geom_smooth(mapping = aes(x = u., y = co2_flux))


```


**Energy Balance of non-gapfilled data. Slope of line is energy balance closure. Ideally it should be 1:1 Net radiation - soil heat flux= to Latent heat +sensible heat. **

```{r}


Combo20191101$E_ng <- NR_Wm2_Avg- SHF_1_Wm2_Avg


Combo20191101$E_lh <- LE +H 

scatter.smooth(Combo20191101$E_ng, Combo20191101$E_lh)
lm(Combo20191101$E_lh ~ Combo20191101$E_ng)
summary(lm(Combo20191101$E_lh ~ Combo20191101$E_ng))$r.squared
```


```{r}
library(openair)
library(tidyverse)

hist(data20191101$wind_dir, xlim = c(0,370), breaks = 36, main = "Wind Direction")


```