---
title: "Merging CIMIS Data"
output: html_notebook
---



```{r}
rm(list=ls())

require(stringr)
require(zoo)
require(openair)


na.count<-function(x) sum(is.na(x))
na.mean<-function(x) ifelse(is.nan(mean(x,na.rm=T)),NA,mean(x,na.rm=T))

library(REddyProc)

library(car)
library(stringr)

library(tidyverse)
library(ggpubr)
library(rstatix)
library(broom)
library(psych)

library(lme4)
library(dplyr)
```


# Defining the data I/O directory #

```{r}
## change root.path as needed
root.path<-"C:\\Users\\Tommy\\flux\\Data-exploring\\02_Concord\\"
#root.path<-"D:\\Housen\\Flux\\Data-exploring\\02_Concord\\"

combined.path<-paste0(root.path,"03_combined_data\\") ## this is where the combined data lives


path.in_CIMIS<-paste0(root.path,"05_CIMIS_Data\\")
 ver<-"cimis_data" 

# hc: Use this for storing combined file
path.out<-paste(root.path,"06_CIMIS_gap_fill\\",sep="")

```



#defining specific files
```{r}
## use follows to specify the versions of the combined file
# file name of the combined_file
cdata.file_combo<-paste0("2020-08-06_master_eddy_met_concord_postfiltering.csv")



## use follows to specify the version of the
file.name_cimis<-paste("CIMIS_hourly.csv")



```


# Read in Combined fulloutput file
# parse variable names and define N/As

```{r}
## read in full output file
combo_data<-read.csv(paste0(combined.path, cdata.file_combo,sep=""),
              
                header=T,
                na.strings="NA",
                stringsAsFactors=F)
colnames(combo_data)<-colnames(read.csv(paste(combined.path,cdata.file_combo,sep=""),
                                  
                                   header=T,
                                   na.strings="NA"))



head(combo_data)

```


#Read in CIMIS File
```{r}
## read in CIMIS file
cimis_data<-read.csv(paste0(path.in_CIMIS, file.name_cimis,sep=""),
                     header = T,
                     skip = 1)
              
                

colnames(cimis_data)<-colnames(read.csv(paste(path.in_CIMIS,file.name_cimis,sep=""),
                                  
                                   header=T,
                                   na.strings="NA"))



head(cimis_data)
```

# Parsing time stamp of cimis_data 
#first add zero to the front of the am time values so the strptime can read them
<!-- * then converting it into a POSIXlt vector* -->
<!-- * interpreting date and time into new timestamp column* -->
<!-- ** Then taking that time stamp column and turning each time into a unique number (time.id) so I can join based on that. As it can be really tricky to join/merge based on time stamps alone** -->

<!-- ** Finally ploting time.id to make sure my times translate linearily** -->


```{r}




cimis_data$Hour<-str_pad (as.character(cimis_data$Hour), 4, pad = "0") #adding zero to the front of the am numbers



cimis_data$TIMESTAMP<-strptime(paste(cimis_data$Date,cimis_data$Hour,sep=" "),
                          format="%m/%d/%Y %H%M ",
                          tz = "Etc/GMT-8")
head( cimis_data$TIMESTAMP)

plot(cimis_data$Sol.Rad)


cimis_data$time.id<-cimis_data$TIMESTAMP$year+1900+
  (cimis_data$TIMESTAMP$yday)/366+
  (cimis_data$TIMESTAMP$hour)/366/24+
  (cimis_data$TIMESTAMP$min)/366/24/60

cimis_data$time.id[1:50]
plot(cimis_data$TIMESTAMP,cimis_data$time.id)
which(duplicated(cimis_data$time.id))

head(cimis_data)




```

#For cmobined master data switching the timestamp back to a timestamp from being a character vector. 
```{r}
names(combo_data)[names(combo_data) == "TIMESTAMP"] <- "fake_timestamp"

#colnames(combo_data)


combo_data$TIMESTAMP<-strptime(paste(combo_data$fake_timestamp),
                          format="%m/%d/%Y %H:%M",
                         tz = "Etc/GMT-8")
head(combo_data$TIMESTAMP)


plot(combo_data$TIMESTAMP, combo_data$time.id)

which(duplicated(combo_data$time.id))

head(combo_data)

```


#trying to add half hourly timestamp to CIMIS data
```{r}
# # create a full timestamp, 30 mins
# full.time<-data.frame(TIMESTAMP=
#                         seq.POSIXt(min(cimis_data $TIMESTAMP),
#                                    max(cimis_data$TIMESTAMP),
#                                    units = "seconds", by = 1800),
#                       stringsAsFactors=F)
# 
# full.time$TIMESTAMP<-strptime(full.time$TIMESTAMP,
#                               format ="%Y-%m-%d %H:%M:%S",
#                               tz = "Etc/GMT-8")
# 
# full.time$time.id <-full.time$TIMESTAMP$year+1900+
#   (full.time$TIMESTAMP$yday)/366+
#   (full.time$TIMESTAMP$hour)/366/24+
#   (full.time$TIMESTAMP$min)/366/24/60 
# 
# print(paste("Starting timestamp:",full.time$TIMESTAMP[1]))
# print(paste("Ending timestamp:",full.time$TIMESTAMP[nrow(full.time)]))
# 
# head(full.time)
```



#removing fake timestamp
```{r}
combo_data$fake_timestamp <-NULL
# combo_data$TIMESTAMP<-NULL
# cimis_data$TIMESTAMP <- NULL


colnames(combo_data)
colnames(cimis_data)

```



```{r}
# 
# combo_data<- merge.data.frame(full.time,
#                          combo_data[,-which(colnames(cdata)=="TIMESTAMP")],
#                          by = "time.id",
#                          all = TRUE,
#                          sort = TRUE)
#all=true what ever appears in each file
# 

#merges, but keeps bot rows.
cimis_combo_data<- merge.data.frame (combo_data,
                         cimis_data[,-which(colnames(combo_data)=="TIMESTAMP")],
                         by = "time.id",
                         all = TRUE,
                         sort = TRUE)



############
#neither works not work
# cimis_combo_data <- left_join(combo_data, cimis_data, by = "time.id")


# cimis_combo_data<- merge(combo_data[,-which(colnames(combo_data)=="TIMESTAMP")], cimis_data[,-which(colnames(cimis_data)=="TIMESTAMP")], by = "time.id")

head(cimis_combo_data, 50)

```


```{r}
write.csv(cimis_combo_data,
          paste(path.out,Sys.Date(),"_eddy_met_cimis.csv",sep=""),
          quote = T,
          row.names = F)


```

