---
title: "Concord_spec_Tommy.With loops"
output: html_notebook
---



```{r}
rm(list=ls())

require(stringr)
require(zoo)
require(openair)

source("concord_filter.R")
source("cospectra_plot3.R")

na.count<-function(x) sum(is.na(x))
na.mean<-function(x) ifelse(is.nan(mean(x,na.rm=T)),NA,mean(x,na.rm=T))

```

# Defining the data I/O directory #
hc: define all I/O upfront and reuse them for consistency

```{r}
## change root.path as needed
root.path<-"C:\\Users\\Tommy\\flux\\Data-exploring\\02_Concord\\"
#root.path<-"D:\\Housen\\Flux\\Data-exploring\\02_Concord\\"
eddypro.path<-paste0(root.path,"01_Proccessed_Data\\Master_Eddy\\") ## this is where the EddyPro outputs located
plot.path<-paste0(root.path,"01_Proccessed_Data\\spectrum_plot\\") ## this is where the output plots located

#path_met<-"C:\\Users\\Tommy\\flux\\Data-exploring\\02_Concord\\"
path.in_met<-paste(root.path,"01_Proccessed_Data",sep="")
ver<-"met_data" 

# hc: Use this for storing combined file
path.out<-paste(root.path,"03_combined_data\\",sep="")

```

# Define file naming / version used
hc: Keep anything that needs to change regularly here

```{r}
## use follows to specify the versions of EddyPro outputs
# file name of the master EddyPro file
cdata.file2<-paste0("master_eddy_pro_concord.csv")

## Use follows to define binned spectrum file names
cdata.proc.time<-"2020-04-17T161020"
cdata.proc.ext<-"_adv"
#20190614-1700_binned_cospectra_2020-04-17T161020_adv

## use follows to specify the versions of master met file
file.name<-paste("MET_data_master",sep="")

#"C:\Users\Tommy\flux\Data-exploring\02_Concord\01_Proccessed_Data\Master_Eddy"
#"C:\Users\Tommy\flux\Data-exploring\02_Concord\01_Proccessed_Data\Master_Eddy\master_eddy_pro_concord.csv"
#"C:\Users\Tommy\flux\Data-exploring\02_Concord\01_Proccessed_Data\Master_Eddy\eddypro_binned_cospectra"
#"C:\Users\Tommy\flux\Data-exploring\02_Concord\01_Proccessed_Data\Master_Eddy\eddypro_full_cospectra"
#"C:\Users\Tommy\flux\Data-exploring\02_Concord\01_Proccessed_Data\Master_Eddy\spectrum_plot"

```

# Read in EddyPro fulloutput file
* parse variable names and define N/As
* remove time periods that does not have enough record of high frequency data

```{r}
## read in full output file
cdata<-read.csv(paste(eddypro.path,cdata.file2,sep=""),
                skip=3,
                header=F,
                na.strings="-9999",
                stringsAsFactors=F)
colnames(cdata)<-colnames(read.csv(paste(eddypro.path,cdata.file2,sep=""),
                                   skip=1,
                                   header=T,
                                   na.strings="NaN"))

cdata<-cdata[cdata$filename!="not_enough_data"&
               !is.na(cdata$used_records),]

head(cdata)

```

# Read in Met data master file
* parse variable names and define N/As, NAN, -7999

```{r}
met_data_master<-read.csv(paste(path.in_met,"\\",ver,"\\",file.name,".csv",sep=""),
                          header=F,
                          skip=4,
                          na.strings=c("NAN","-7999"),
                          stringsAsFactors = F)
colnames(met_data_master)<-colnames(
  read.csv(paste(path.in_met,"\\",ver,"\\",file.name,".csv",sep=""),
           header=T,
           skip= 1))

head(met_data_master)

```

# Parsing time stamp of cdata (EddyPro file)
* converting it into a POSIXlt vector*
* interpreting date and time into new timestamp column
* Then taking that time stamp column and turning each time into a unique number (time.id) so I can join based on that. As it can be really tricky to join/merge based on time stamps alone**
* Or I could make sure both time stamps are characters and match them that way**
* Finally ploting time.id to make sure my times translate linearily*


```{r}
cdata$TIMESTAMP<-strptime(paste(cdata$date,cdata$time,sep=" "),
                          format="%m/%d/%Y %H:%M", 
                          tz = "Etc/GMT-8")

#cdata$TIMESTAMP=cdata$TIMESTAMP+1800 don't need to add 1800. already in endtime format
#cdata$TIMESTAMP=cdata$TIMESTAMP #just rename it end. so that we know

cdata$time.id<-cdata$TIMESTAMP$year+1900+
  (cdata$TIMESTAMP$yday)/366+
  (cdata$TIMESTAMP$hour)/366/24+ 
  (cdata$TIMESTAMP$min)/366/24/60

cdata$time.id[1:50]
plot(cdata$TIMESTAMP,cdata$time.id)
which(duplicated(cdata$time.id))
```
# Parsing time stamp of cdata (Met file)
* Taking the met_data and turning the time stamp into posixt format#
* creating a time id for the MET Data so I I can join the MET and Eddy Pro Data#

```{r}
met_data_master$TIMESTAMP<-strptime(met_data_master$TIMESTAMP,
                                    format ="%m/%d/%Y %H:%M",
                                    tz = "Etc/GMT-8")

met_data_master$time.id <-met_data_master$TIMESTAMP$year+1900+
  (met_data_master$TIMESTAMP$yday)/366+
  (met_data_master$TIMESTAMP$hour)/366/24+
  (met_data_master$TIMESTAMP$min)/366/24/60 

met_data_master$time.id[1:20]
plot(met_data_master$TIMESTAMP,met_data_master$time.id)
which(duplicated(met_data_master$time.id))

head(met_data_master)
#met_data_master$TIMESTAMP[1:20]

```

# Create a full timestamp without gaps 
* Create a full timestamp based on the earliest and latest timestamps in EddyPro and Met files
* Use this full timestamp later when merging EddyPro and master met files

```{r}
# create a full timestamp, 30 mins
full.time<-data.frame(TIMESTAMP=
                        seq.POSIXt(min(min(met_data_master$TIMESTAMP),min(cdata$TIMESTAMP)),
                                   max(max(met_data_master$TIMESTAMP),max(cdata$TIMESTAMP)),
                                   units = "seconds", by = 1800),
                   stringsAsFactors=F)

full.time$TIMESTAMP<-strptime(full.time$TIMESTAMP,
                              format ="%Y-%m-%d %H:%M:%S",
                              tz = "Etc/GMT-8")

full.time$time.id <-full.time$TIMESTAMP$year+1900+
  (full.time$TIMESTAMP$yday)/366+
  (full.time$TIMESTAMP$hour)/366/24+
  (full.time$TIMESTAMP$min)/366/24/60 

print(paste("Starting timestamp:",full.time$TIMESTAMP[1]))
print(paste("Ending timestamp:",full.time$TIMESTAMP[nrow(full.time)]))

head(full.time)


```

#Joining the Met_Data and Eddy Pro Data Sets 
* using time stamp from the full.time dataframe
* Also create a doy.id, unique for each date, later used in aggregating daily values

```{r}

cdata<- merge.data.frame(full.time,
                         cdata[,-which(colnames(cdata)=="TIMESTAMP")],
                         by = "time.id",
                         all = TRUE,
                         sort = TRUE) 
#all=true what ever appears in each file is show in the file data file. sort tries to sort each data frame by merging. in this case probably doesnot matter. timestamp

cdata<- merge.data.frame(cdata,
                         met_data_master[,-which(colnames(met_data_master)=="TIMESTAMP")],
                         by = "time.id",
                         all = TRUE,
                         sort = TRUE) 

## create a unique DOY id 
cdata$doy.id<-full.time$TIMESTAMP$year+1900+
  (full.time$TIMESTAMP$yday)/366

#colnames(cdata)

```

#Creating a CSV File of my combined Master File!#
hc: modify the filename starting with Date when the file is created

```{r}
write.csv(cdata,
          paste(path.out,Sys.Date(),"_master_eddy_met_concord_prefiltering.csv",sep=""),
          quote = T,
          row.names = F)
```

#Filter data based on predefined criteria
* filtering criteria are defined in concord_filter function
* A few variables also convert Unit 


```{r}

cdata<-concord_filter(data.in=cdata)

colnames(cdata)

```

#Creating a CSV File of combined Master File (post-filtering)
hc: modify the filename starting with Date when the file is created

write.csv(cdata,
   paste(eddypro.path,ver,"cdata",sep=""),
    quote = T,
  row.names = F)

```{r}
write.csv(cdata,
          paste(path.out,Sys.Date(),"_master_eddy_met_concord_postfiltering.csv",sep=""),
          quote = T,
          row.names = F)
```

#Generate simple timeseries plots
* post-filtered time series plot per variable
* LOESS fit and daily average are plotted to show temporal dynamics

```{r}

#summary(cdata)
##############################################################
## Generic time series plot
target.plot.var<-c("co2_flux","LE","H","u.",
                   "co2_mixing_ratio","h2o_mixing_ratio",
                   "air_temperature_adj","RH",
                   "wind_speed","wind_dir","mean_value_RSSI_LI.7500", 
                   "AirT_Avg", "Correct_NR",  "Correct_shf_1" , "Correct_shf_2",
                   "VWC_Avg","Precip_mm_Tot" ,
                   #"PAR_in_uEm2_Avg","PAR_out_uEm2_Avg",
                   "AtmPressure_Avg",
                   "TC_Avg.1.","TC_Avg.2.","TC_Avg.3.","TC_Avg.4.","TC_Avg.5.")
target.plot.var.title<-c(expression(FC~'('~mu~mol~m^{-2}~s^{-1}~')'),
                         expression(LE~'('~W~m^{-2}~')'),
                         expression(H~'('~W~m^{-2}~')'),
                         expression(u['*']~'('~m~s^{-1}~')'),
                         expression(CO[2]~'('~ppm~')'),
                         expression(Water~vapor~'('~ppt~')'),
                         expression(Air~temperature~'('~degree~C~')'),
                         expression(Relative~humidity~'('~percent~')'),
                         expression(Wind~speed~'('~m~s^{-1}~')'),
                         expression(Wind~direction~'('~degree~')'),
                         expression(LI7500~signal~strengh ~'('~'-'~')'),
                         expression(Air~temperature~MET~'('~degree~C~')'),
                         expression(Net~Radiation~'('~W~m^{-2}~')'),
                         expression(Soil~Heatflux1~'('~W~m^{-2}~')'),
                         expression(Soil~Heatflux2~'('~W~m^{-2}~')'),
                         expression(Soil~water~content~'('~m^{3}~m^{-3}~')'),
                         expression(Precipitation~'('~mm~')'),
                         #expression(Incoming~PAR~'('~mu~mol~m^{-2}~s^{-1}~')'),
                         #expression(Outgoing~PAR~'('~mu~mol~m^{-2}~s^{-1}~')'),
                         expression(Atmospheric~pressure~'('~kPa~')'),
                         expression(Soil~temperature~1~'('~degree~C~')'),
                         expression(Soil~temperature~2~'('~degree~C~')'),
                         expression(Soil~temperature~3~'('~degree~C~')'),
                         expression(Soil~temperature~4~'('~degree~C~')'),
                         expression(Soil~temperature~5~'('~degree~C~')'))  

for(k1 in 1:length(target.plot.var)){
  
  ## locate the start of each month
  month.loc<-which(cdata$TIMESTAMP$mday==1&
                     cdata$TIMESTAMP$hour==0&
                     cdata$TIMESTAMP$min==0)
  month.ticks <- seq(cdata$TIMESTAMP[month.loc[1]],
                     cdata$TIMESTAMP[month.loc[length(month.loc)]],by="months")

  png(paste0(plot.path,
             "Concord_",
             cdata$TIMESTAMP$year[1]+1900,"_",
             cdata$TIMESTAMP$yday[1]+1,"_",
             cdata$TIMESTAMP$year[nrow(cdata)]+1900,"_",
             cdata$TIMESTAMP$yday[nrow(cdata)]+1,"_",
             target.plot.var[k1],"_",
             Sys.Date(),".png"),
      width=6,
      height=4,
      units="in",
      res=300,
      pointsize = 11,
      bg = "white")
  
  par(oma=c(0.5,0.5,0.5,0.5),mar=c(4,4.5,0,0))
  plot(cdata$TIMESTAMP,
       cdata[,target.plot.var[k1]],
       xlab="TIMESTAMP",
       ylab=target.plot.var.title[k1],
       cex=0.5,col="grey",bg="lightgrey",
       las=1,pch=21,
       xaxs="i",yaxs="i"
  )
  
  abline(h=0,col="darkgrey")
  
  ## daily averge line
  daily.tmp<-data.frame(date=tapply(cdata$time.id,cdata$doy.id,min),
                        daily=tapply(cdata[,target.plot.var[k1]],cdata$doy.id,na.mean))
  
  lines(cdata$TIMESTAMP[which(cdata$time.id %in% daily.tmp$date)],
        daily.tmp$daily,
        lwd=1.5,col="black")
  
  ## loess fit line
  loess.tmp<-loess(cdata[,target.plot.var[k1]]~c(1:nrow(cdata)),span=0.1)
  
  ## avoid plotting long gaps
  long.gap<-which(loess.tmp$x[-1]-loess.tmp$x[-length(loess.tmp$x)]>48*3)
  if(long.gap[1]>1) long.gap<-c(1,long.gap)
  if(long.gap[length(long.gap)]<length(loess.tmp$x)) long.gap<-c(long.gap,length(loess.tmp$x))
  
  for(k1 in 1:(length(long.gap)-1)){
    lines(cdata$TIMESTAMP[round(loess.tmp$x[c((long.gap[k1]+1):(long.gap[k1+1]-1))])],
          loess.tmp$fitted[c((long.gap[k1]+1):(long.gap[k1+1]-1))],
          lwd=1.5,col="red")
  }
  
  axis(1, at = month.ticks, labels = FALSE, tcl = -0.3)
  dev.off()
}

```


#Generate timeseries plots color-coded by wind direction
* similar plot as previous time series plot
* Color-coded data points based on wind direction, currently 2 groups
** hc: Revise thresholds for WD groups if needed

```{r}

##############################################################
## Generic time series plot
WD.grp<-rep(2,nrow(cdata))
WD.grp[which(!is.na(cdata$wind_dir)&
                  (cdata$wind_dir>120&cdata$wind_dir<=300))]<-1
WD.legend<-c("Southwest wind","Northeast wind")
WD.col<-c(rgb(0,0,1,0.5,maxColorValue=1),rgb(1,0,0,0.5,maxColorValue=1))

target.plot.var<-c("co2_flux","LE","H","u.")
target.plot.var.title<-c(expression(FC~'('~mu~mol~m^{-2}~s^{-1}~')'),
                         expression(LE~'('~W~m^{-2}~')'),
                         expression(H~'('~W~m^{-2}~')'),
                         expression(u['*']~'('~m~s^{-1}~')'))  

for(k1 in 1:length(target.plot.var)){
  
  ## locate the start of each month
  month.loc<-which(cdata$TIMESTAMP$mday==1&
                     cdata$TIMESTAMP$hour==0&
                     cdata$TIMESTAMP$min==0)
  month.ticks <- seq(cdata$TIMESTAMP[month.loc[1]],
                     cdata$TIMESTAMP[month.loc[length(month.loc)]],by="months")

  png(paste0(plot.path,
             "Concord_",
             cdata$TIMESTAMP$year[1]+1900,"_",
             cdata$TIMESTAMP$yday[1]+1,"_",
             cdata$TIMESTAMP$year[nrow(cdata)]+1900,"_",
             cdata$TIMESTAMP$yday[nrow(cdata)]+1,"_",
             target.plot.var[k1],"_color_",
             Sys.Date(),".png"),
      width=8,
      height=4,
      units="in",
      res=300,
      pointsize = 11,
      bg = "white")
  
  par(oma=c(4,4.5,0.5,0.5),mar=c(0,0.5,0,0.5),fig=c(0,0.7,0,1))
  plot(cdata$TIMESTAMP,
       cdata[,target.plot.var[k1]],
       xlab="",
       ylab="",
       cex=0.5,col=WD.col[WD.grp],
       las=1,pch=16,
       xaxs="i",yaxs="i"
  )
  mtext(side=2,target.plot.var.title[k1],line=3)
  mtext(side=1,"TIMESTAMP",line=2.8)
  abline(h=0,col="darkgrey")
  axis(1, at = month.ticks, labels = FALSE, tcl = -0.3)
  
  par(fig=c(0.7,1,0,1),new=T)
  hist0<-hist(cdata[,target.plot.var[k1]],
              plot=F,nclass=50)
  hist1<-hist(cdata[,target.plot.var[k1]][WD.grp==1],
              plot=F,breaks=hist0$breaks)
  hist2<-hist(cdata[,target.plot.var[k1]][WD.grp==2],
              plot=F,breaks=hist0$breaks) 
  
  barplot(hist1$counts,
          axes=F,
          horiz=T,
          ylim=c(0,length(hist1$breaks)+1),
          xlim=c(-5,max(c(hist1$counts,hist2$counts))),
          space=0,col=WD.col[1],border=NA) # barplot
  barplot(hist2$counts,
          axes=F,
          add=T,
          horiz=T,
          ylim=c(0,length(hist1$breaks)+1),
          xlim=c(-5,max(c(hist1$counts,hist2$counts))),
          space=0,col=WD.col[2],border=NA) # barplot
  legend(0,
         length(hist1$breaks)+1,
         fill=WD.col,border=NA,
         legend=WD.legend,bty="n",
         cex=0.9)
  dev.off()
}

```

#Windrose plot 
A simple windrose plot, using openair package

```{r}

png(paste0(plot.path,
           "Concord_",
           cdata$TIMESTAMP$year[1]+1900,"_",
           cdata$TIMESTAMP$yday[1]+1,"_",
           cdata$TIMESTAMP$year[nrow(cdata)]+1900,"_",
           cdata$TIMESTAMP$yday[nrow(cdata)]+1,"_",
           "Windrose_",
           Sys.Date(),".png"),
    width=5,height=5,units="in",res=300,pointsize=10)

openair::windRose(mydata=cdata[,c("wind_speed","wind_dir")],
         ws="wind_speed",
         wd="wind_dir",
         ws.int = 0.5, angle = 15,
         dig.lab=2,
         paddle=F,key.position = "bottom")

dev.off()

```

**Energy Balance of non-gapfilled data. Slope of line is energy balance closure. Ideally it should be 1:1 Net radiation - soil heat flux= to Latent heat +sensible heat. **

#Not looking great. ?????

#Add heat storage in soil!

```{r}


cdata$E_ng = (cdata$Correct_NR-(cdata$Correct_shf_1+cdata$Correct_shf_2)/2)



summary(cdata$E_ng )
plot(cdata$E_ng)

cdata$E_le_and_H =(cdata$LE+cdata$H)
summary(cdata$E_le_and_H  )
plot(cdata$E_le_and_H )

scatter.smooth(cdata$E_ng, cdata$E_le_and_H,
      xlab=expression(Net~Radiation~minus~soil~heat~flux~'('~W~m^{-2}~')'), 
     ylab= expression(Latent~and~Sensible~Heat~'('~W~m^{-2}~')'), 
     main='')
#par(New=TRUE)
#plot(cdata$E_ng, cdata$E_le_and_H,
     # xlab=expression(Net~Radiation~minus~soil~heat~flux~'('~W~m^{-2}~')'), 
     #ylab= expression(Latent~and~Sensible~Heat~'('~W~m^{-2}~')'), 
    # main='')
               
lm(cdata$E_le_and_H  ~ cdata$E_ng)
summary(lm(cdata$E_le_and_H  ~ cdata$E_ng-1))
```

#Work on (co)spectra data
```{r}
head(cdata)
```


```{r}


zL.cut.rng<-c(-5,-0.1,0.1,1) ## setting the 3 Z/L ranges for plotting
cspec.data.pre<-NULL

data.pre<-cdata  

## work on file name of spectrum files
cspec.name.ls.parse<-paste(TIMESTAMP$year+1900,
                           sprintf("%02d",TIMESTAMP$mon+1),
                           sprintf("%02d",TIMESTAMP$mday),
                           "-",
                           sprintf("%02d",TIMESTAMP$hour),
                           sprintf("%02d",TIMESTAMP$min),
                           "_binned_cospectra",
                           sep="")
```


```{r}
## scan if spectrum files exist
cspec.name.ls<-rep(NA,length(cspec.name.ls.parse))
cspec.file.exist<-rep(FALSE,length(cspec.name.ls.parse))
cspec.file.ls<-list.files(paste0(eddypro.path,"eddypro_binned_cospectra\\"))
for(i in 1:length(cspec.file.exist)){
  cspec.name.ls[i]<-cspec.file.ls[which(grepl(cspec.name.ls.parse[i],
                                              cspec.file.ls))[1]]
  cspec.file.exist[i]<-ifelse(!is.na(cspec.name.ls[i]),
                              TRUE,
                              FALSE)
}

cspec.var.name<-c("n.f","f","fh.u","fSu","fSv","fSw","fSt","fSc","fSq","fSm","fSn",
                  "fCwu","fCwv","fCwt","fCwc","fCwq","fCwm","fCwn")
cspec.var.name.select<-c("n.f","f","fh.u","fSu","fSv","fSw","fSt","fSc","fSq",
                         "fCwu","fCwv","fCwt","fCwc","fCwq")

```



```{r}
## which spectrum variables to plot 
target.cspec<-c("fSw","fSt","fSc","fSq",
                "fCwu","fCwt","fCwc","fCwq")
```

#for running just one month comment out 331

```{r}
### loop through the spetrum files, combine them into a single dataframe for plotting
month.id<-paste0(TIMESTAMP$year+1900,"-",sprintf("%02d",TIMESTAMP$mon+1))
month.id.ls<-list(names(table(month.id)),
                  as.vector(table(month.id)))
#can comment out 351 if you want to run just one month
#for(j1 in 1:length(month.id.ls[[1]])){
j1=1 #add just the month heere. comment out if wan to run full loop
cspec.data.pre<-data.frame()
target.mon<-month.id.ls[[1]][j1]
target.mon.loc<-which(month.id==target.mon)

print(paste0("######  ",target.mon,"  ######"))

for(i1 in 1:length(cspec.name.ls[target.mon.loc])){
  if(cspec.file.exist[target.mon.loc][i1]){
    
    ## read in each (co)spectra files
    cspec.data<-read.csv(paste(eddypro.path,
                               "eddypro_binned_cospectra\\",
                               cspec.name.ls[target.mon.loc][i1],sep=""),
                         skip=11,
                         header=T,
                         na.strings=c("-9999","-9999.0"))
    
    colnames(cspec.data)<-cspec.var.name
    
    ## combine spetrum data with basic state variables, e.g., WS, WD
    cspec.data.tmp<-data.frame(date=rep(data.pre$date[target.mon.loc][i1],nrow(cspec.data)),
                               time=rep(data.pre$time[target.mon.loc][i1],nrow(cspec.data)),
                               zL=rep(data.pre$X.z.d..L[target.mon.loc][i1],nrow(cspec.data)),
                               L=rep(data.pre$L[target.mon.loc][i1],nrow(cspec.data)),
                               WS=rep(data.pre$wind_speed[target.mon.loc][i1],nrow(cspec.data)),
                               WD=rep(data.pre$wind_dir[target.mon.loc][i1],nrow(cspec.data)),
                               cspec.data[,cspec.var.name.select])
    
    ### filter spetrum data based on corresponding variance/covariance
    
    if(is.na(data.pre$u.[target.mon.loc][i1])){
      cspec.data.tmp$fSu<-NA
      cspec.data.tmp$fCwu<-NA
      cspec.data.tmp$fSv<-NA
      cspec.data.tmp$fCwv<-NA
      cspec.data.tmp$fSw<-NA
    }
    if(is.na(data.pre$H[target.mon.loc][i1])){
      cspec.data.tmp$fSt<-NA
      cspec.data.tmp$fCwt<-NA
    }
    if(is.na(data.pre$co2_flux[target.mon.loc][i1])){
      cspec.data.tmp$fSc<-NA
      cspec.data.tmp$fCwc<-NA
    }
    if(is.na(data.pre$LE[target.mon.loc][i1])){
      cspec.data.tmp$fSq<-NA
      cspec.data.tmp$fCwq<-NA
    }
    cspec.data.pre<-rbind.data.frame(cspec.data.pre,cspec.data.tmp)
  }else{
    print(paste(cspec.name.ls.parse[target.mon.loc][i1],"has no spectrum files"))  
  }                       
}


### output site-specific (co)spectra file (composite all records)
write.csv(cspec.data.pre,
          paste0(plot.path,
                 target.mon,
                 "_cospectra_compiled_",
                 Sys.Date(),".csv",
                 sep=""),
          row.names=F)

#### loop through the target.var, do spetrum plotting 
for(m2 in 1:length(target.cspec)){
  
  cospectra_plot3(cspec.data.pre=cspec.data.pre,
                  target.var=target.cspec[m2], 
                  case="Concord",
                  year=TIMESTAMP$year[target.mon.loc][1]+1900,
                  doy.i=TIMESTAMP$yday[target.mon.loc][1]+1,
                  doy.f=TIMESTAMP$yday[target.mon.loc][length(target.mon.loc)]+1,
                  output=T,
                  outDir=plot.path,
                  plot.loess=T,
                  postfix=paste0("_",Sys.Date()),
                  log.y.value=T,
                  zL.cut.rng=zL.cut.rng)  
  
}
#} #comment out for just running one month. remove # if you want to run a full loop. 



```






