---
title: "Gap Filling"
output: html_notebook
---

#example from website
```{r}
library(REddyProc)
library(dplyr)

#example from tutorial
# #+++ Load data with 1 header and 1 unit row from (tab-delimited) text file
# fileName <- getExamplePath('Example_DETha98.txt', isTryDownload = TRUE)
# EddyData <- if (length(fileName)) fLoadTXTIntoDataframe(fileName) else
#   # or use example dataset in RData format provided with REddyProc
#   Example_DETha98
# 
# #+++ Replace long runs of equal NEE values by NA
# EddyData <- filterLongRuns(EddyData, "NEE")
# #+++ Add time stamp in POSIX time format
# EddyDataWithPosix <- fConvertTimeToPosix(
#   EddyData, 'YDH',Year = 'Year',Day = 'DoY', Hour = 'Hour') %>% 
#   filterLongRuns("NEE")
# #+++ Initalize R5 reference class sEddyProc for post-processing of eddy data
# #+++ with the variables needed for post-processing later
# EProc <- sEddyProc$new(
#   'DE-Tha', EddyDataWithPosix, c('NEE','Rg','Tair','VPD', 'Ustar'))
# 
# EProc$sPlotFingerprintY('NEE', Year = 1998)
```


#has to begin on first half hour:0:00 and end on last half hour 0:30
#adjust data accordingly
```{r}
fileName<-('C:/Users/Tommy/flux/Data-exploring/02_Concord/04_Reddy_Proc_data/2020-09-11_reddy_proc.txt')

fileName[is.na(fileName)] <- -9999



EddyData.F <- if (length(fileName)) fLoadTXTIntoDataframe(fileName) else Example_DETha98

head(EddyData.F,25)

#converting Pa to hpa
# EddyData.F$VPD = (EddyData.F$VPD/100)

#adding back the timestamp to the radyproc data frame, since when it became a text file the time became its on column.  
EddyData.F$TIMESTAMP<-strptime(paste(EddyData.F$TIMESTAMP,EddyData.F$Hour,sep=" "),
                          format="%m/%d/%Y %H:%M", 
                          tz = "Etc/GMT-8")





EddyData.F$Hour<-NULL

head(EddyData.F)

head(EddyData.F$TIMESTAMP)


# write.csv(EddyData.F, 'C:/Users/Tommy/flux/Data-exploring/02_Concord/04_Reddy_Proc_data/eddydata_timestamp.csv')

# eddyC <- sEddyProc$new( 'mormon', EddyDataWithPosix.F,
#                         c('NEE','Rg','Tair','VPD', 'Ustar'),DTS.n=24)

#Setting the basic info and the columns we are interested in analyzing. 
eddyC <-sEddyProc$new('concord', EddyData.F, c('H','LE', 'NEE', 'rH', 'Ustar', 'Tsoil', 'Tair' , 'Rg'), ColPOSIXTime = "TIMESTAMP", 
    LatDeg = 37.93799591, LongDeg = -121.9761047, TimeZoneHour = -7)

#making sure it looks good
eddyC


```

#fingerprint plots of the gap fill stuff
```{r}
#fingerprint NEE 2019
eddyC$sPlotFingerprintY('NEE', Year = 2019)
#fingerprint NEE 2020
#may data loss from all the bird shit. OMG.....
eddyC$sPlotFingerprintY('NEE', Year = 2020)


#fingerprint Tair 2019
eddyC$sPlotFingerprintY('Tair', Year = 2019)
#fingerprint Tair 2020
eddyC$sPlotFingerprintY('Tair', Year = 2020)

#fingerprint tsoil 2019 (thermocouple 2 5 cm depth)
eddyC$sPlotFingerprintY('Tsoil', Year = 2019)
#fingerprint NEE 2020 (thermocouple 2 5cm depth)
eddyC$sPlotFingerprintY('Tsoil', Year = 2020)

#fingerprint rH 2019
eddyC$sPlotFingerprintY('rH', Year = 2019)
#fingerprint rH 2020
eddyC$sPlotFingerprintY('rH', Year = 2020)

#fingerprint ustar 2019
eddyC$sPlotFingerprintY('Ustar', Year = 2019)
#fingerprint u star 2020
eddyC$sPlotFingerprintY('Ustar', Year = 2020)

#fingerprint H 2019
eddyC$sPlotFingerprintY('H', Year = 2019)
#fingerprint H 2020
eddyC$sPlotFingerprintY('H', Year = 2020)

#fingerprint Le 2019
eddyC$sPlotFingerprintY('LE', Year = 2019)
#fingerprint Le 2020
eddyC$sPlotFingerprintY('LE', Year = 2020)





```

#ustar scenarios and thresholds
```{r}
# uStarTh <- eddyC$sEstUstarThreshold()
# uStarTh <- eddyC$sEstUstarThresholdDistribution( nSample = 100L, probs = c(0.05, 0.5, 0.95))

eddyC$sEstimateUstarScenarios(
    nSample = 100L, probs = c(0.05, 0.5, 0.95))
eddyC$sGetEstimatedUstarThresholdDistribution()

eddyC$sGetUstarScenarios()

```



```{r}
eddyC$sMDSGapFillUStarScens('NEE')
```

#gapfilling Sensible Heat
```{r}
eddyC$sMDSGapFillUStarScens('H')





```


#Gapfilling Latent Heat
```{r}
eddyC$sMDSGapFillUStarScens('LE')
```


#For each of the different u∗ threshold estimates a separate set of output columns of filled NEE and its uncertainty is generated, distinguished by the suffixes given with uStarSuffixes. "_f" denotes the filled value and "_fsd" the estimated standard deviation of its uncertainty.
```{r}
grep("NEE_.*_f$",names(eddyC$sExportResults()), value = TRUE)
grep("NEE_.*_fsd$",names(eddyC$sExportResults()), value = TRUE)
```

#Sensible Heat
```{r}
grep("H_.*_f$",names(eddyC$sExportResults()), value = TRUE)
grep("H_.*_fsd$",names(eddyC$sExportResults()), value = TRUE)
```

#Latent Heat

```{r}
grep("LE_.*_f$",names(eddyC$sExportResults()), value = TRUE)
grep("LE_.*_fsd$",names(eddyC$sExportResults()), value = TRUE)
```


#fingerprint plot of 5% uncertainty NEE

```{r}
eddyC$sPlotFingerprintY('NEE_U50_f', Year = 2019)

eddyC$sPlotFingerprintY('NEE_U50_f', Year = 2020)



```

#Sensible Heat finger print plot
```{r}
eddyC$sPlotFingerprintY('H_U50_f', Year = 2019)

eddyC$sPlotFingerprintY('NEE_U50_f', Year = 2020)
```

#Latent Heat finger print plot
```{r}
eddyC$sPlotFingerprintY('LE_U50_f', Year = 2019)

eddyC$sPlotFingerprintY('LE_U50_f', Year = 2020)
```




#The third post-processing step is partitioning the net flux (NEE) into its gross components GPP and Reco. The partitioning needs to distinguish carefully between night-time and day-time. Therefore it needs a specification of geographical coordinates and time zone to allow computing sunrise and sunset. Further, the missing values in the used meteorological data need to be filled.


#Then we are ready to invoke the partitioning, here by the night-time approach, for each of the several filled NEE columns.
```{r}

eddyC$sMDSGapFill('Tair', FillAll = FALSE,  minNWarnRunLength = NA)     
  
eddyC$sMRFluxPartitionUStarScens()
```

#The results are stored in columns Reco and GPP_f modified by the respective u∗ threshold suffix.

```{r}
grep("GPP.*_f$|Reco",names(eddyC$sExportResults()), value = TRUE)
```


#Visualizations of the results by a fingerprint plot gives a compact overview.

```{r}
eddyC$sPlotFingerprintY('GPP_U50_f', Year = 2019)

eddyC$sPlotFingerprintY('GPP_U50_f', Year = 2020)

eddyC$sPlotFingerprintY('Reco_U50', Year = 2019)

eddyC$sPlotFingerprintY('Reco_U50', Year = 2020)



```

#Estimating the uncertainty of aggregated results
#The results of the different u∗ threshold scenarios can be used for estimating the uncertainty due to not knowing the threshold.

#First, the mean of the GPP across all the year is computed for each u∗-scenario and converted from μmolCO2m−2s−1 to gCm−2yr−1.


```{r}
FilledEddyData <- eddyC$sExportResults()
uStarSuffixes <- colnames(eddyC$sGetUstarScenarios())[-1]
#suffix <- uStarSuffixes[2]
GPPAggCO2 <- sapply( uStarSuffixes, function(suffix) {
    GPPHalfHour <- FilledEddyData[[paste0("GPP_",suffix,"_f")]]
    mean(GPPHalfHour, na.rm = TRUE)
})
molarMass <- 12.011
GPPAgg <- GPPAggCO2 * 1e-6 * molarMass * 3600*24*365.25
print(GPPAgg)


```

#The difference between those aggregated values is a first estimate of uncertainty range in GPP due to uncertainty of the u∗ threshold.
```{r}
(max(GPPAgg) - min(GPPAgg)) / median(GPPAgg) 
```


#For a better but more time consuming uncertainty estimate, specify a larger sample of u∗ threshold values, for each repeat the post-processing, and compute statistics from the larger sample of resulting GPP columns. This can be achieved by specifying a larger sequence of quantiles when calling sEstimateUstarScenarios in place of the command shown above.

```{r}
eddyC$sEstimateUstarScenarios( 
  nSample = 200, probs = seq(0.025,0.975,length.out = 39) )
```

#exporting dat
```{r}
FilledEddyData <- eddyC$sExportResults()
CombinedData <- cbind(EddyData.F, FilledEddyData)

write.csv(CombinedData, 'C:/Users/Tommy/flux/Data-exploring/02_Concord/07_Gap_Filled_Data\\gapfilled_data.csv' )

fWriteDataframeToFile(CombinedData, 'DE-Tha-Results.txt', Dir = tempdir())
```



#gap filing first three lines by Housen. 
```{r}


# # EProc1 <- sEddyProc$new(case, data.work, c(h.ls[1]),DTS.n = d.hr)
# #         EProc1$sFillInit(h.ls[1])
# #         data.work$H_F <- EProc1$sFillMDC(7)$VAR_f
# 
# #+++ Add time stamp in POSIX time format
# EddyDataWithPosix <- fConvertTimeToPosix(
#   eddy.data, 'YDH',Year = 'Year',Day = 'DoY', Hour = 'Hour') %>% 
#   filterLongRuns("NEE")
# 
#  EProc1 <- sEddyProc$new(
#   'Concord', EddyDataWithPosix, c('NEE','Rg','Tair','VPD', 'Ustar'))

```