---
title: 'Met_Master Merge with Eddy_Pro_Master: Data from 2020-01-20'
output:
  word_document: default
  html_notebook: default
  html_document:
    df_print: paged
---



```{r}

source("calc_footprint_FFP.R")
library(ggplot2)
library(modelr)
options(na.action = na.warn)
```


# Lists #
```{r}
rm(list=ls())
```

# Defining the data I/O directory for the Eddy Master File #
**
```{r}
path_eddy<-"C:\\Users\\Tommy\\flux\\Data-exploring\\02_Concord\\"
path.in_eddy<-paste(path_eddy,"01_Proccessed_Data",sep="")
path.out_eddy<-paste(path_eddy,"03_combined_data",sep="")
ver<-"Master_Eddy" 
file.name_eddy<-paste("master_eddy_pro_concord",sep="")
```

# read in eddypro full output Master file, parse variable names #
```{r}
data_master_eddy<-read.csv(paste(path.in_eddy,"\\",ver,"\\",file.name_eddy,".csv",sep=""),
                  header=F,
                  skip=3,
                  na.strings=c(-9999),
                  stringsAsFactors = F)
colnames(data_master_eddy)<-colnames(
  read.csv(paste(path.in_eddy,"\\",ver,"\\",file.name_eddy,".csv",sep=""),
           header=T,
           skip=1))

head(data_master_eddy)
```


# Defining the data I/O directory for the Master met_data #

```{r}
path_met<-"C:\\Users\\Tommy\\flux\\Data-exploring\\02_Concord\\"
path.in_met<-paste(path_met,"01_Proccessed_Data",sep="")
path.out_met<-paste(path_met,"03_combined_data",sep="")
ver<-"met_data" 
file.name<-paste("MET_data_master",sep="")
```




#read in Met_Data Master file, parse variable names and define N/As#


```{r}
met_data_master<-read.csv(paste(path.in_met,"\\",ver,"\\",file.name,".csv",sep=""),
                  header=F,
                  skip=4,
                  na.strings=c("NAN"),
                  stringsAsFactors = F)
colnames(met_data_master)<-colnames(
  read.csv(paste(path.in_met,"\\",ver,"\\",file.name,".csv",sep=""),
           header=T,
           skip= 1))

head(met_data_master)

```




# Parsing the time stamp converting it into a POSIXlt vector#

**interpreting date and time into new timestamp column**

**Then taking that time stamp column and turning each time into a unique number (time.id) so I can join based on that. As it can be really tricky to join/merge based on time stamps alone**

**Or I could make sure both time stamps are characters and match them that way**

**Finally ploting time.id to make sure my times translate linearily**

```{r}
data_master_eddy$TIMESTAMP<-strptime(paste(data_master_eddy$date,data_master_eddy$time,sep=" "),format="%m/%d/%Y %H:%M", tz = "GMT")

data_master_eddy$time.id<-data_master_eddy$TIMESTAMP$year+1900+(data_master_eddy$TIMESTAMP$yday)/366+(data_master_eddy$TIMESTAMP$hour)/366/24+ (data_master_eddy$TIMESTAMP$min)/366/24/60

data_master_eddy$time.id[1:50]
plot(data_master_eddy$time.id)
which(duplicated(data_master_eddy$time.id))
```


#Taking the met_data and turning the time stamp into posixt format#

```{r}
met_data_master$TIMESTAMP<-strptime(met_data_master$TIMESTAMP,
                           format ="%m/%d/%Y %H:%M", tz = "GMT")

met_data_master$TIMESTAMP[1:20]
```

#Making sure timestamp columns line up#

```{r}

met_data_master$TIMESTAMP[1:10]

data_master_eddy$TIMESTAMP[1:10]
```


```{r}
head(met_data_master)
```

#creating a time id for the MET Data so I I can join the MET and Eddy Pro Data#

```{r}

met_data_master$time.id <-met_data_master$TIMESTAMP$year+1900+(met_data_master$TIMESTAMP$yday)/366+(met_data_master$TIMESTAMP$hour)/366/24 + (met_data_master$TIMESTAMP$min)/366/24/60 

met_data_master$time.id[1:20]
plot(met_data_master$time.id)
which(duplicated(met_data_master$time.id))

head(met_data_master)
```


#Joining the Met_Data and Eddy Pro Data Sets#

**with merge**

```{r}

combo_master_ed_met<- merge(met_data_master[,-which(colnames(met_data_master)=="TIMESTAMP")], data_master_eddy[,-which(colnames(data_master_eddy)=="TIMESTAMP")], by = "time.id")

combo_master_ed_met

colnames(combo_master_ed_met)

```


#Add back time stamp to the combo_master_ed_met#
```{r}
combo_master_ed_met$TIMESTAMP<-strptime(paste(combo_master_ed_met$date,combo_master_ed_met$time,sep=" "),format="%m/%d/%Y %H:%M", tz = "GMT")

combo_master_ed_met$TIMESTAMP[1:10]

combo_master_ed_met$TIMESTAMP[10451:10453]

head(combo_master_ed_met)



```

#Creating a CSV File of my combined Master File!#
```{r}
write.csv(cdata,
          paste(path.out_eddy,ver,"cdata",sep=""),
          quote = T,
          row.names = F)
```

#filtering data for quality control filters#
**filtering latent heat, sensible heat, co2 flux, qc_tau and h20flux by quality controls**

```{r}
combo_master_ed_met$LE.[!is.na(combo_master_ed_met$qc_LE)&combo_master_ed_met$qc_LE==2]<-NA

combo_master_ed_met$qqc_h2o_flux[!is.na(combo_master_ed_met$qc_h2o_flux)&combo_master_ed_met$qc_h2o_flux==2]<-NA

combo_master_ed_met$H[!is.na(combo_master_ed_met$qc_H)&combo_master_ed_met$qc_H==2]<-NA

combo_master_ed_met$u.[!is.na(combo_master_ed_met$qc_Tau)&combo_master_ed_met$qc_Tau==2]<-NA

combo_master_ed_met$co2_flux[!is.na(combo_master_ed_met$co2_flux)&combo_master_ed_met$co2_flux==2]<-NA


```

# latent heat, sensible heat, h20_flux, and relative humidity by day for whole period #


```{r}

plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$LE)
hist(combo_master_ed_met$LE)

plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$h2o_flux)

plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$H)

plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$RH)






```



#Half Hour Flux Averages

```{r}
plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$co2_flux,xlab='Time', ylab='Co2 Fluxes', main=' Half Hour Co2 Flux Averages',  ylim = c(-20,20),pch=1,col="blue",cex=0.4)
```

#Daily average of fluxes 
```{r}

plot(tapply(combo_master_ed_met$co2_flux ,round(combo_master_ed_met$DOY),function(x) mean(x,na.rm=T)), xlab='Time', ylab='Co2 Fluxes', main='Daily Co2 Flux Averages',pch=1,col="red",cex=1.5)

```

#Plotting Co2 flux by timstamp on x-axis. First half-hourly data and daily data stacked 

```{r}
layout(matrix(c(1,1,2,2), 2, 2, byrow = TRUE))
plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$co2_flux, xlab='Time', ylab='Co2 Fluxes', main='Half Hour Flux Averages',  ylim = c(-15,15),pch=1,col="blue",cex=0.4)
plot(tapply(combo_master_ed_met$co2_flux ,round(combo_master_ed_met$DOY),function(x) mean(x,na.rm=T)), xlab='Time', ylab='Co2 Fluxes', main='Daily Co2 Flux Averages',pch=1,col="red",cex=1.5)


```


```{r}

plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$co2_flux,
  ylim = c(-10, 10),
               cex=0.6,col="grey",
               xlab= 'Time', 
               ylab="", 
               main='',las=1,
               lpars=list(lwd=3,col="red"))
mtext(side=2,expression(CO[2]~Flux~'('~mu~mol~m^{-2}~s^{-1}~')'),line=2.5)
par(new= TRUE)
plot(tapply(combo_master_ed_met$co2_flux ,round(combo_master_ed_met$DOY),function(x) mean(x,na.rm=T)),
     xaxt='n', 
     xlab='Time', 
     ylab='', 
     main='', las =1,
     ylim = c(-10,10),
     lty=1,col="red",
     lwd=2,type="l")
mtext(side=2,expression(CO[2]~Flux~'('~mu~mol~m^{-2}~s^{-1}~')'),line=2.5)
abline(h=0,col="black")

```


#Plotting daily flux average over half hour fluxes
```{r}


plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$co2_flux, 
     xlab='Time', 
     ylab='Co2 Fluxes', 
     main='',  ylim = c(-10,10),pch=1,col="grey",cex=0.4)
par(new= TRUE)
plot(tapply(combo_master_ed_met$co2_flux ,round(combo_master_ed_met$DOY),function(x) mean(x,na.rm=T)),xaxt='n', xlab='Time', ylab='Co2 Fluxes', main='',ylim = c(-10,10),lty=1,col="red",lwd=2,type="l")
abline(h=0,col="black")
legend(x='bottomright',legend=c('1/2 hour fluxes', 'daily flux averages'),
col=c('grey', 'red'), pch=c(1,19))

```

#Daily average of Sensible Heat  
```{r}
plot(tapply(combo_master_ed_met$H,round(combo_master_ed_met$DOY),function(x) mean(x,na.rm=T)),xlab='Time', ylab='Sensible Heat', main='Daily Average of Sensible Heat')
```


#Daily average of Latent Heat  
```{r}
plot(tapply(combo_master_ed_met$LE ,round(combo_master_ed_met$DOY),function(x) mean(x,na.rm=T)),xlab='Time', ylab='Latent Heat', main='Daily Average of Latent Heat')
```



#line plot of c02_fluxes#
```{r}
ggplot(data = combo_master_ed_met) + 
  geom_line(mapping = aes(x = time.id , y = co2_flux)) 

```


#latent heat and Sensible heat plotted over eachother

```{r}
plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$LE,
     xlab='Time', 
     ylab='Latent and Sensible Heat', 
     main='Latent and Sensible Heat',pch=1,col="blue",cex=0.6)
points(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$H,
       col="red",
       pch=1,
       cex=0.6)
legend(x='bottomright',legend=c('Latent Heat', 'Sensible Heat'),
col=c('blue', 'red'), pch=c(1,19))

```

#air temperatue by sensible heat an U* by co2 flux
```{r}
plot(combo_master_ed_met$air_temperature-273.15,combo_master_ed_met$H,xlim=c(10,40),ylim=c(-100,500))



plot(combo_master_ed_met$u. ,combo_master_ed_met$co2_flux, ylim = c(0, 10), xlim = c(0,1))
```


#Adding best fit line to air temperature by sensible heat
```{r}
ggplot(data = combo_master_ed_met) + 
  geom_point(mapping = aes(x = air_temperature-273.15, y = H)) +
  geom_smooth(mapping = aes(x = air_temperature-273.15, y = H))


```

#best fit line to U* bt co2 flux
```{r}
ggplot(data = combo_master_ed_met) + 
  geom_point(mapping = aes(x = u., y = co2_flux)) +
  geom_smooth(mapping = aes(x = u., y = co2_flux))


```


```{r}

hist(combo_master_ed_met$wind_dir, xlim = c(0,370), breaks = 36, main = "Wind Direction at Concord Tower", xlab = 'Degrees')
```

#Comparing MET Temperature data to temperature reading from Licor intruments#
```{r}
plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$PTemp_C_Avg)
points(combo_master_ed_met$TIMESTAMP,combo_master_ed_met$air_temperature-273.15,col="red",pch=2)
```



#Adding coefficient to Net radiation#
```{r}
combo_master_ed_met$Correct_NR = (combo_master_ed_met$NR_Wm2_Avg*10)/14.2
```

#plotting air temperature from data logger. see where our gaps line up. lines up with net radiation and gaps
```{r}
plot(combo_master_ed_met$AirT_Avg)
```

#plotting Net Radation to see the bad data. 
```{r}
summary(combo_master_ed_met$Correct_NR[c(1:600,2500:4000)])
plot(combo_master_ed_met$Correct_NR)
```


#filtering out bad NR numbers

```{r}

combo_master_ed_met$Correct_NR[!is.na(combo_master_ed_met$Correct_NR)&(combo_master_ed_met$Correct_NR<(-150)|combo_master_ed_met$Correct_NR>800)]<-NA
summary(combo_master_ed_met$Correct_NR)
plot(combo_master_ed_met$Correct_NR)
```

```{r}
summary(combo_master_ed_met$Correct_NR)
```


#Adding coefficient to Soil Heat Flux Data
```{r}
plot(combo_master_ed_met$SHF_1_mV_Avg,ylim=c(-10,10))
combo_master_ed_met$Correct_shf_1 = (combo_master_ed_met$SHF_1_mV_Avg*16.455)
plot(combo_master_ed_met$Correct_shf_1,ylim=c(-50,50))
```

#plotting Soil heat flux to see the bad data. 
```{r}

summary(combo_master_ed_met$Correct_shf_1)

summary(combo_master_ed_met$Correct_shf_1[c(2500:4000)])
plot(combo_master_ed_met$Correct_shf_1)
plot(combo_master_ed_met$Correct_shf_1[c(2500:4000)], ylim = c(-50,50),xlab='8/14/2019 to 02/05/2020', ylab='Soil Heat Flux_1 ', main='Half Hour Averages of Soil Heat Flux of the Concord Site')

```



#filtering out bad soil heat flux numbers

```{r}

combo_master_ed_met$Correct_shf_1[!is.na(combo_master_ed_met$Correct_shf_1)&(combo_master_ed_met$Correct_shf_1<(-20)|combo_master_ed_met$Correct_shf_1>50)]<-NA
summary(combo_master_ed_met$Correct_shf_1)
plot(combo_master_ed_met$Correct_shf_1)
```

**Energy Balance of non-gapfilled data. Slope of line is energy balance closure. Ideally it should be 1:1 Net radiation - soil heat flux= to Latent heat +sensible heat. **

```{r}


combo_master_ed_met$E_ng = (combo_master_ed_met$Correct_NR-combo_master_ed_met$Correct_shf_1)

summary(combo_master_ed_met$E_ng )
plot(combo_master_ed_met$E_ng)

combo_master_ed_met$E_le_and_H =(combo_master_ed_met$LE+combo_master_ed_met$H)
summary(combo_master_ed_met$E_le_and_H  )
plot(combo_master_ed_met$E_le_and_H )

scatter.smooth(combo_master_ed_met$E_ng, combo_master_ed_met$E_le_and_H )
lm(combo_master_ed_met$E_le_and_H  ~ combo_master_ed_met$E_ng)
summary(lm(combo_master_ed_met$E_le_and_H  ~ combo_master_ed_met$E_ng-1))
```



#1/2 hour and daily averages of Latent Heat



```{r}
plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$LE, 
     xlab='Time', 
     ylab= expression(Latent~Heat~'('~W~m^{-2}~')'), 
     main='',  
     ylim = c(-40,300),
     pch=1,
     col="grey",cex=0.4)
par(new= TRUE)
plot(tapply(combo_master_ed_met$LE ,round(combo_master_ed_met$DOY),function(x) mean(x,na.rm=T)),
     xaxt='n', 
     xlab='Time', 
    ylab= expression(Latent~Heat~'('~W~m^{-2}~')'),  
     main='',
     ylim = c(-40,300),lty=1,col="red",lwd=2,type="l")
abline(h=0,col="black")
```


```{r}
plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$LE,
  ylim = c(-40, 300),
               cex=0.4,col="grey",
               xlab= 'Time', 
               ylab="", 
               main='',las=1,
               lpars=list(lwd=3,col="red"))
mtext(side=2,expression(Latent~Heat~'('~W~m^{-2}~')'),line=2.5)
par(new= TRUE)
plot(tapply(combo_master_ed_met$LE ,round(combo_master_ed_met$DOY),function(x) mean(x,na.rm=T)),
     xaxt='n', 
     xlab='Time', 
     ylab='', 
     main='', las =1,
     ylim = c(-40,300),
     col="red",pch=1,cex=1.0)
mtext(side=2,expression(Latent~Heat~'('~W~m^{-2}~')'),line=2.5)
abline(h=0,col="black")
legend(x='topright',legend=c('1/2 hour averages', 'daily averages'),
col=c('grey', 'red'), pch=c(19,1))
```


```{r}
plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$LE, 
     xlab='Time', 
     ylab='Latent Heat', 
     main='Latent Heat: Daily and Half Hour Averages', 
     ylim = c(-40,300),pch=1,col="grey",cex=0.4)
par(new= TRUE)
plot(tapply(combo_master_ed_met$LE ,round(combo_master_ed_met$DOY),function(x) mean(x,na.rm=T)),xaxt='n'
     , xlab='Time',
     ylab='Latent Heat', 
     main='Latent Heat: Daily and Half Hour Averages',
     ylim = c(-40,300),
     col="red",pch=1,cex=1.0)
abline(h=0,col="black")
legend(x='topright',legend=c('1/2 hour averages', 'daily averages'),
col=c('grey', 'red'), pch=c(1,1))
```



#1/2 hour and daily averages of Sensible Heat

```{r}
plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$H, xlab='Time', ylab='Sensible Heat', main='Sensible Heat: Daily and Half Hour Averages',  ylim = c(-40,300),pch=1,col="grey",cex=0.4)
par(new= TRUE)
plot(tapply(combo_master_ed_met$H ,round(combo_master_ed_met$DOY),function(x) mean(x,na.rm=T)),xaxt='n', xlab='Time', ylab='Sensible Heat', main='Sensible Heat: Daily and Half Hour Averages',ylim = c(-40,300),lty=1,col="red",lwd=2,type="l")
abline(h=0,col="black")
```


```{r}
plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$H, xlab='Time', ylab='Sensible Heat', main='Sensible Heat: Daily and Half Hour Averages',  ylim = c(-40,300),pch=1,col="grey",cex=0.4)
par(new= TRUE)
plot(tapply(combo_master_ed_met$H ,round(combo_master_ed_met$DOY),function(x) mean(x,na.rm=T)),xaxt='n', xlab='Time', ylab='Sensible Heat', main='Sensible Heat: Daily and Half Hour Averages',ylim = c(-40,300),col="red",pch=1,cex=1.0)
abline(h=0,col="black")
```


```{r}
plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$H,
  ylim = c(-40, 300),
               cex=0.4,col="grey",
               xlab= 'Time', 
               ylab="", 
               main='',las=1,
               lpars=list(lwd=3,col="red"))
mtext(side=2,expression(Sensible~Heat~'('~W~m^{-2}~')'),line=2.5)
par(new= TRUE)
plot(tapply(combo_master_ed_met$H ,round(combo_master_ed_met$DOY),function(x) mean(x,na.rm=T)),
     xaxt='n', 
     xlab='Time', 
     ylab='', 
     main='', las =1,
     ylim = c(-40,300),
     col="red",pch=1,cex=1.0)
mtext(side=2,expression(Sensible~Heat~'('~W~m^{-2}~')'),line=2.5)
abline(h=0,col="black")
```

#Net Radiation Daily and 1/2 hour averages

```{r}
plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$Correct_NR, xlab='Time', ylab='Net Radiation', main='Net Radiation: Daily and Half Hour Averages',  ylim = c(-80,800),pch=1,col="grey",cex=0.4)
par(new= TRUE)
plot(tapply(combo_master_ed_met$Correct_NR ,round(combo_master_ed_met$DOY),function(x) mean(x,na.rm=T)),xaxt='n', xlab='Time', ylab='Net Radiation', main='Net Radiation: Daily and Half Hour Averages',ylim = c(-80,800),lty=1,col="red",lwd=2,type="l")
abline(h=0,col="black")
```

```{r}

plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$Correct_NR, xlab='Time', ylab='Net Radiation', main='Net Radiation: Daily and Half Hour Averages',  ylim = c(-80,800),pch=1,col="grey",cex=0.4)
par(new= TRUE)
plot(tapply(combo_master_ed_met$Correct_NR ,round(combo_master_ed_met$DOY),function(x) mean(x,na.rm=T)),xaxt='n', xlab='Time', ylab='Net Radiation', main='Net Radiation: Daily and Half Hour Averages',ylim = c(-80,800),col="red",pch=1,cex=1.0)
abline(h=0,col="black")

```


#soil heat flux
```{r}
plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$Correct_shf_1, xlab='Time', ylab='Soil Heat Flux 1', main='Soil Heat Flux 1: Daily and Half Hour Averages',  ylim = c(-20,40),pch=1,col="grey",cex=0.4)
par(new= TRUE)
plot(tapply(combo_master_ed_met$Correct_shf_1,round(combo_master_ed_met$DOY),function(x) mean(x,na.rm=T)),xaxt='n', xlab='Time', ylab='Soil Heat Flux 1', main='Soil Heat Flux 1: Daily and Half Hour Averages',ylim = c(-20,40),lty=1,col="red",lwd=2,type="l")
abline(h=0,col="black")
```



```{r}
plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$Correct_shf_1, xlab='Time', ylab='Soil Heat Flux', main='Soil Heat Flux 1: Daily and Half Hour Averages',  ylim = c(-20,40),pch=1,col="grey",cex=0.4)
par(new= TRUE)
plot(tapply(combo_master_ed_met$Correct_shf_1,round(combo_master_ed_met$DOY),function(x) mean(x,na.rm=T)),xaxt='n', xlab='Time', ylab='Soil Heat Flux 1', main='Soil Heat Flux 1: Daily and Half Hour Averages',ylim = c(-20,40),col="red",pch=1,cex=1.0)
abline(h=0,col="black")
```

#air temperature daily and 1/2 hour averages
```{r}
plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$air_temperature-273.15, xlab='Time', ylab='Air Temperature C: Daily and 1/2 Hour Averages', main=' ',  ylim = c(5,40),pch=1,col="grey",cex=0.4)
par(new= TRUE)
plot(tapply(combo_master_ed_met$air_temperature-273.15,round(combo_master_ed_met$DOY),function(x) mean(x,na.rm=T)),xaxt='n', xlab='Time', ylab='Air Temperature C: Daily and 1/2 Hour Averages', main='',ylim = c(5,40),lty=1,col="red",lwd=2,type="l")
abline(h=0,col="black")
```


#Water Fluxes daily and 1/2 hour averages. cumulative water and co2
```{r}
plot(combo_master_ed_met$TIMESTAMP ,combo_master_ed_met$h2o_flux, xlab='Time', ylab='H2O Fluxes', main='H2O Fluxes: Daily and Half Hour Averages',  ylim = c(-2,5),pch=1,col="grey",cex=0.4)
par(new= TRUE)

plot(tapply(combo_master_ed_met$h2o_flux,
            round(combo_master_ed_met$DOY),
            function(x) mean(x,na.rm=T)),
     xaxt='n',
     xlab='Time',
     ylab='H2O Fluxes',
     main='H2O Fluxes: Daily and Half Hour Averages',
     ylim = c(-2,5),
     lty=1,
     col="red",
     lwd=2,
     type="l")
abline(h=0,col="black")

plot(cumsum(tapply(combo_master_ed_met$h2o_flux,
            round(combo_master_ed_met$DOY),
            function(x) mean(x,na.rm=T)))*18.02/1000000*1800*48,
     xaxt='n',
     xlab='Days since June 25',
     ylab=expression(Cumulative~Evapotranspiration~'('~mm~')'),
     main='',
     ylim = c(0,270),
     lty=1,
     col="red",
     lwd=2,
     type="l")
axis(side=1,at=seq(0,270,by=30))

plot(cumsum(tapply(combo_master_ed_met$co2_flux,
            round(combo_master_ed_met$DOY),
            function(x) mean(x,na.rm=T)))*12/1000000*1800*48,
     xaxt='n',
     xlab='Days since June 25 2019',
     ylab=expression(Cumulative~NEE~'('~g~C~m^{-2}~')'),
     main='',
     ylim = c(-100,100),
     lty=1,
     col="red",
     lwd=2,
     type="l")
axis(side=1,at=seq(0,360,by=30))

```

#Co2 fluxes v.s u star, temperature, and VPD

```{r}

plot(combo_master_ed_met$u. ,combo_master_ed_met$co2_flux, ylim = c(-5, 10), xlim = c(0,1), xlab='U*', ylab='Co2 Fluxes', main='Co2 Fluxes v.s U*')

plot(combo_master_ed_met$VPD ,combo_master_ed_met$co2_flux, ylim = c(-5, 10), xlab='VPD', ylab='Co2 Fluxes', main='Co2 Fluxes v.s VPD*')

plot(combo_master_ed_met$air_temperature-273.15 ,combo_master_ed_met$co2_flux, ylim = c(-5, 10), xlab='Air Temperature (C)', ylab='Co2 Fluxes', main='Co2 Fluxes v.s Air temperature*')

plot(combo_master_ed_met$Correct_NR[combo_master_ed_met$daytime==1] ,combo_master_ed_met$co2_flux[combo_master_ed_met$daytime==1], ylim = c(-10, 10), xlab='Net Radiation', ylab='Co2 Fluxes', main='Co2 Fluxes v.s Net Radiation')

summary(combo_master_ed_met$VPD)
scatter.smooth(combo_master_ed_met$Correct_NR[combo_master_ed_met$daytime==1],
               combo_master_ed_met$co2_flux[combo_master_ed_met$daytime==1],
               ylim = c(-10, 10),
               cex=0.6,col="grey",
               xlab=expression(Daytime~Net~Radiation~'('~W~m^{-2}~')'), 
               ylab="", 
               main='',las=1,
               lpars=list(lwd=3,col="red"))
mtext(side=2,expression(CO[2]~Flux~'('~mu~mol~m^{-2}~s^{-1}~')'),line=2.5)

scatter.smooth(combo_master_ed_met$air_temperature[combo_master_ed_met$daytime==0&
                                                     combo_master_ed_met$u.>=0.15]-273.15,
               combo_master_ed_met$co2_flux[combo_master_ed_met$daytime==0&
                                                     combo_master_ed_met$u.>=0.15],
               ylim = c(-5, 10),
               cex=0.6,col="grey",
               xlab=expression(Air~Temperature~'('~degree~C~')'), 
               ylab="", 
               main='',las=1,
               lpars=list(lwd=3,col="red"))
mtext(side=2,expression(CO[2]~Flux~'('~mu~mol~m^{-2}~s^{-1}~')'),line=2.5)

```

#cumulative 
