---
title: "Getting Data Ready for Kljun Footprint Model"
author: "Thomas_Fenster"
date: "October, 2019"
output:
  html_notebook: default
  word_document: default
---

# Read in EddyPro full output file, reformat and select #

**needed variables for online Kljun footprint model**

# Lists #
```{r}
rm(list=ls())

library(dplyr)
```


# Defining the data I/O directory #
**"C:\Users\Tommy\flux\Data-exploring\02_Concord\01_Proccessed_Data\Master_Eddy\master_eddy_pro_concord.csv"**
```{r}
path<-"C:\\Users\\Tommy\\flux\\Data-exploring\\02_Concord\\"
path.in<-paste(path,"01_Proccessed_Data",sep="")
path.out<-paste(path,"02_Footprint_Analysis",sep="")
ver<-"Master_Eddy" 
file.name<-paste("master_eddy_pro_concord",sep="")
```

# read in eddypro full output file, parse variable names #
```{r}
data.in<-read.csv(paste(path.in,"\\",ver,"\\",file.name,".csv",sep=""),
                  header=F,
                  skip=3,
                  na.strings=c("-9999.0"),
                  stringsAsFactors = F)
colnames(data.in)<-colnames(
  read.csv(paste(path.in,"\\",ver,"\\",file.name,".csv",sep=""),
           header=T,
           skip=1))
data.in
```

# Parsing the time stamp #
```{r}
data.in$TIMESTAMP<-strptime(paste(data.in$date,data.in$time,sep=" "),format="%m/%d/%Y %H:%M", tz = "GMT")

data.in$TIMESTAMP[1:10]
```

# filter ustar based on qc_Tau. #
**Filtering out all qc_Tau = 2**
```{r}
data.in$u.[!is.na(data.in$qc_Tau)&data.in$qc_Tau==2]<-NA
```

# prepare file format for Kljun Online footprint model 
#If you just need to create an overall footprint, not seperated by night or day time or wind direction you can stop here. 
```{r}
data.fpt<-data.frame(yyyy=data.in$TIMESTAMP$year+1900,
                     mm=data.in$TIMESTAMP$mon+1,
                     day=data.in$TIMESTAMP$mday,
                     HH=floor(data.in$TIMESTAMP$hour),
                     MM=data.in$TIMESTAMP$min,
                     zm=3.67,  ## measurement height (m)
                     d=0,      ## displacement height (m)
                     z0=0.05,  ## roughness length (m)
                     u_mean=data.in$wind_speed,  ## wind speed
                     L=data.in$L,    ## Monin-Obukov length (m)
                     sigma_v=sqrt(data.in$v_var),  ## cross-wind standard deviation (m/s)
                     u_star=data.in$u.,  ## frisction velocity (m/s)
                     wind_dir=data.in$wind_dir)  ## wind direction

data.fpt<-na.omit(data.fpt)

write.csv(data.fpt,
          paste(path.out,ver,"_fpt_short.csv",sep=""),
          quote = T,
          row.names = F)
```

#created a csv spreadsheet for a klujn footprint model that has a column for night time and day time
#Before uploading to the online model be sure to delete the daytime column! Will not run if you keep it. 
```{r}
data.fpt.time_of_day<-data.frame(yyyy=data.in$TIMESTAMP$year+1900,
                     mm=data.in$TIMESTAMP$mon+1,
                     day=data.in$TIMESTAMP$mday,
                     HH=floor(data.in$TIMESTAMP$hour),
                     MM=data.in$TIMESTAMP$min,
                     daytime=data.in$daytime,
                     zm=3.67,  ## measurement height (m)
                     d=0,      ## displacement height (m)
                     z0=0.05,  ## roughness length (m)
                     u_mean=data.in$wind_speed,  ## wind speed
                     L=data.in$L,    ## Monin-Obukov length (m)
                     sigma_v=sqrt(data.in$v_var),  ## cross-wind standard deviation (m/s)
                     u_star=data.in$u.,  ## frisction velocity (m/s)
                     wind_dir=data.in$wind_dir)  ## wind direction

data.fpt.time_of_day<-na.omit(data.fpt.time_of_day)

write.csv(data.fpt.time_of_day,
          paste(path.out,ver,"_time_of_day_fpt_1_short.csv",sep=""),
          quote = T,
          row.names = F)
```


#CSV of of day and night treatment and control areas
#tried increasing control to 235 but lose 1/6 of data. Reduced Treatment to 215. 
#Don't lose too much data and get a nicer seperation. 
```{r}
control_overall.fpt <- data.fpt %>%  filter(wind_dir >= 230 &
                              wind_dir <= 300)

treatment_overall.fpt <- data.fpt%>% filter( wind_dir >= 150 & wind_dir <= 215)


########creating CSVs#############################################
write.csv(control_overall.fpt ,
          paste(path.out,ver,"control_overall_fpt.csv",sep=""),
          quote = T,
          row.names = F)

write.csv(treatment_overall.fpt ,
          paste(path.out,ver,"treatment_215_overall_fpt.csv",sep=""),
          quote = T,
          row.names = F)

```



# filter and created a nighttime only csv for the footprint model#
```{r}



##########################creating just the night time######################### 

night_footprint<-data.fpt.time_of_day %>% filter(daytime == "0")

#night_time_footprint control
night_footprint_control <- night_footprint %>% filter(wind_dir >= 230 &
                              wind_dir <= 300)


#nigh_time_footprint treatment
night_footprint_treatment <- night_footprint %>% filter( wind_dir >= 150 & wind_dir <= 215)


######################creating CSV of nighttime overall, treatment,  and control footprints#######


# #overall footrpint night time
# write.csv(night_footprint, #
#           paste(path.out,ver,"night_fpt_overall.csv",sep=""),
#           quote = T,
#           row.names = F)


#control night
write.csv(night_footprint_control, #
          paste(path.out,ver,"night_fpt_control.csv",sep=""),
          quote = T,
          row.names = F)
#treatment night
write.csv(night_footprint_treatment,
          paste(path.out,ver,"night_fpt_treatment.csv",sep=""),
          quote = T,
          row.names = F)



```



# filter by daytime and night time. and created a daytime only csv for the footprint model#

```{r}




######################################################
#daytime overall footprint
day_footprint<-data.fpt.time_of_day %>% filter(daytime == "1")

#day_time_footprint control
day_footprint_control <- day_footprint %>% 
  filter(wind_dir >= 230 &
                              wind_dir <= 300)


#day_time_footprint treatment
day_footprint_treatment <- day_footprint %>% 
  filter( wind_dir >= 150 &
                            wind_dir <= 215)

##############################################creating CSV's######################

# #overall day foot print
# write.csv(day_footprint,
#           paste(path.out,ver,"day_fpt_overall.csv",sep=""),
#           quote = T,
#           row.names = F)



#control day
write.csv(day_footprint_control, #
          paste(path.out,ver,"day_fpt_control.csv",sep=""),
          quote = T,
          row.names = F)

#treatment day
write.csv(day_footprint_treatment,
          paste(path.out,ver,"day_fpt_treatment.csv",sep=""),
          quote = T,
          row.names = F)




```


